### 2015-07-21 ms.tex
paper edits

%% This is emulateapj reformatting of the AASTEX sample document
%%
\documentclass[preprint2]{aastex}
%\documentclass[iop]{emulateapj}

\usepackage{natbib}
\usepackage{acronym}
\bibliographystyle{apj}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tdm@astro.princeton.edu}

\newcommand{\ntotal}{5500}
\newcommand{\nfail}{1000}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\kepler}{\textit{Kepler}}
\newcommand{\vespa}{\texttt{vespa}}
\newcommand{\isochrones}{\texttt{isochrones}}

\defcitealias{Morton:2012}{M12}

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}

%% You can insert a short comment on the title page using the command below.

\slugcomment{}

\shorttitle{False Positive Probabilities for KOIs}
\shortauthors{Morton et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{False Positive Probabilities for all Kepler Objects of Interest: \\
        \nvalnew\ newly validated planets and \nfpnew\ likely false positives}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{Timothy D. Morton}
\affil{Department of Astrophysical Sciences, Princeton University}

%\altaffiltext{1}{Department of Astrophysics, Princeton University}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI) from the Q1-Q16 catalog release.
Out of \ntotal\ KOIs, we determine that \nval\ have probabilities
$<$1\% to be astrophysical false positives, and thus may be considered
validated planets.  \nvalnew\ of these have not yet been validated or
confirmed by other methods.  In addition, we identify \nfp\ KOIs
likely to be false positives ($>$90\% probability), \nfpnew\ of which
have not yet been identified as such. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple.  These calculations
use \vespa, a publicly available Python package able to be easily
applied to any transiting exoplanet candidate.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so in the
%% subject header.  Objects should be in the appropriate "individual"
%% headers (e.g. quasars: individual, stars: individual, etc.) with the
%% additional provision that the total number of headers, including each
%% individual object, not exceed six.  The \objectname{} macro, and its
%% alias \object{}, is used to mark each object.  The macro takes the object
%% name as its primary argument.  This name will appear in the paper
%% and serve as the link's anchor in the electronic edition if the name
%% is recognized by the data centers.  The macro also takes an optional
%% argument in parentheses in cases where the data center identification
%% differs from what is to be printed in the paper.

\keywords{}

\section{Introduction}

The \kepler\ mission has revolutionized our understanding of
exoplanets.  Among many other important discoveries, \kepler\ has
identified several previously unsuspected features of planetary
systems, such as the prevalence of planets between the size of Earth
and Neptune, and a population of very compact multiple-planet
systems. And perhaps most notably, it has enabled for the first time
estimates of the occurrence rates of small planets ($\gtrsim$1
$R_\oplus$) out to orbits of about one year.  It is important to
remember, however, that these revolutionary discoveries depend
intimately on another revolution---how to interpret transiting planet
\textit{candidate} signals in the absence of unambiguous positive
confirmation of their veracity.

Before \kepler, every survey searching for transiting exoplanets had a

\ac{fpp} and then \ac{fpp}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methods}
\label{sec:methods}

In this work, we apply the fully automated \ac{fpp}-computing
procedure described in \citet{Morton:2012}
\citepalias[][hereafter]{Morton:2012} to all \acp{koi} listed in the
``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
Archive.  While we refer the reader to \citetalias{Morton:2012} for a
detailed description of the method, we outline it briefly here, noting
especially the differences between the current implementation and
\citetalias{Morton:2012}.  The procedure as implemented in this work
is now publicly available in the Python module
\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}.

The basic goal of \vespa\ is to assign probabilities to different
astrophysical hypotheses that might describe a transiting planet
candidate signal.  If $\{H_i\}$ is the set of all considered
hypotheses, the probability for any given model $i$ is
\begin{equation}
  \label{eq:prob}
  \mathrm{Pr}(H_i) = \frac{\mathcal L_i \pi_i}{\displaystyle \sum_j \mathcal L_j \pi_j}
\end{equation}
where $\mathcal L_i$ and $\pi_i$ are the ``likelihood'' and ``prior''
factors for each hypothesis.

eclipse signals as simple
trapezoidal

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Stellar Properties}
\label{sec:methods:stellar}

The first step in calculating the \ac{fpp} of a transit signal is to
determine the physical properties of the signal host star.  To
accomplish this, we use the Python module \isochrones
\citep{isochrones}, which fits a stellar model grid of choice to a set
of observed properties of a given star.

In \citetalias{Morton:2012},

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{False Positive Probabilities}
\label{sec:methods:fpp}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}
\label{sec:results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Stellar Properties}
\label{sec:results:stars}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{False Positive Probabilities}
\label{sec:results:fpp}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conclusions}

\acknowledgments
It is a pleasure to thank
\ldots\

\clearpage
\bibliography{ms}
\clearpage

\end{document}

%%
%% End of file `sample.tex'.

### 2015-07-22 ms.tex
more writing

@@
 \usepackage{acronym}
+\usepackage{amssymb,amsmath}
+
 \bibliographystyle{apj}
@@
 \newcommand{\isochrones}{\texttt{isochrones}}
+\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
 
@@
 \acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
+\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
+\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
 
@@
 In this work, we apply the fully automated \ac{fpp}-computing
-procedure described in \citet{Morton:2012}
-\citepalias[][hereafter]{Morton:2012} to all \acp{koi} listed in the
-``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
+procedure described in \citet[][hereafter
+  \citetalias{Morton:2012}]{Morton:2012} to all \acp{koi} listed in
+the ``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
 Archive.  While we refer the reader to \citetalias{Morton:2012} for a
-detailed description of the method, we outline it briefly here, noting
-especially the differences between the current implementation and
-\citetalias{Morton:2012}.  The procedure as implemented in this work
-is now publicly available in the Python module
+detailed description of the method, we outline it briefly in this
+section.  The procedure as implemented here is now publicly available
+in the Python module
 \vespa\footnote{\url{https://github.com/timothydmorton/vespa}}.
 
-The basic goal of \vespa\ is to assign probabilities to different
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{False Positive Probabilities}
+\label{sec:methods:fpp}
+
+The basic idea of \vespa\ is to assign probabilities to different
 astrophysical hypotheses that might describe a transiting planet
@@
   \label{eq:prob}
-  \mathrm{Pr}(H_i) = \frac{\mathcal L_i \pi_i}{\displaystyle \sum_j \mathcal L_j \pi_j}
+  \mathrm{Pr}\left(H_i\right) = \frac{\pi_i \mathcal
+    L_i}{\displaystyle \sum_j \pi_j \mathcal L_j},
 \end{equation}
-where $\mathcal L_i$ and $\pi_i$ are the ``likelihood'' and ``prior''
-factors for each hypothesis.
+where $\pi_i$ is the ``hypothesis prior'' and $\mathcal L_i$ is the
+``hypothesis likelihood'' (also known as ``evidence'' or
+``marginalized likelihood'').  The prior represents how intrinsically
+probable the hypothesized scenario is to exist, and the likelihood
+represents how closely the shape of the observed transit signal
+matches with the expected shape of a signal produced by the
+hypothesis.
 
-eclipse signals as simple
-trapezoidal
+\vespa\ models an eclipse signal as a simple trapezoid, parametrized
+by depth $\delta$, total duration $T$, and shape parameter $T / \tau$,
+where $\tau$ is the ``ingress/egress'' duration (such that a
+completely V-shaped transit has $T/\tau = 2$).  For the transit signal
+being evaluated, the joint posterior probability density function
+(PDF) of these shape parameters is sampled with \ac{mcmc}, using the
+\texttt{emcee} sampler \citep{emcee}.  This allows the likelihood for
+each hypothesis to be determined by simulating a physically realistic
+population of the hypothesized astrophysical scenario and using this
+population to define the PDF for the trapezoidal parameters under the
+hypothesis.  The likelihood is then
+\begin{equation}
+  \label{eq:lhood}
+  \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
+                                    p_i\left(\bvec{\theta}\right)\,d\bvec{\theta},
+\end{equation}
+where $\bvec{\theta}$ is the vector of trapezoidal shape parameters,
+$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
+PDF for the parameters under hypothesis $i$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Observational constraints are incorporated in two different ways.
+First, photometric (or spectroscopic/asteroseismic) measurements of
+the target star are folded into the population simulations of each
+hypothesis (see \S\ref{sec:methods:stellar}).  All other constraints are
+applied to narrow down which simulated instances of each scenario may
+be counted in the final prior and likelihood evalulations; for example,
+only blended eclipsing binaries with secondary eclipse depths
+shallower than the observed limits are allowed.
+
+The steps \vespa\ takes to calculate the \ac{fpp} of a transit signal
+are thus as follows:
+\begin{enumerate}
+\item Fit trapezoid model to observed transit signal using \ac{mcmc}.
+\item Generate population simulations for each hypothesis scenario
+  being considered (conditioned on available observations of the
+  target star; see \S\ref{sec:methods:stellar}).
+\item Fit each simulated eclipse in each scenario with a trapezoid
+  model (using least-squares optimization).
+\item Evaluate priors and likelihoods for each hypothesis, taking into
+  account all available observational constraints, in order to
+  calculate the \ac{fpp}.
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The first step in calculating the \ac{fpp} of a transit signal is to
-determine the physical properties of the signal host star.  To
-accomplish this, we use the Python module \isochrones
-\citep{isochrones}, which fits a stellar model grid of choice to a set
-of observed properties of a given star.
+The most substantial difference between the current implementation of
+\vespa\ and the procedure documented in \citetalias{Morton:2012} is
+how stellar properties are treated.  Previously, either the target
+star's mass and radius were explicitly provided, or they were randomly
+generated according to the stellar population expected along the line
+of sight by \ac{trilegal}, but constrained to agree with some observed
+color(s) of the star (e.g. $J-K$), to within some specified tolerance.
+This strategy was used both to generate the host stars for the
+transiting planet model and the binary and triple stars for the EB and
+HEB false positive models.
 
-In \citetalias{Morton:2012},
+The new method now used by \vespa\ to fold in observational
+constraints on the host star debuted in \citet{Montet:2015} (and is
+explained there in more detail).  Instead of randomly generating stars
+(or binary or triple systems of stars) from a predefined distribution and
+culling them to agree with observed colors, \emph{all} available
+constraints on the target star are used to condition a direct fit of
+either a single-, binary-, or triple-star model to the Dartmouth grid
+of stellar models.  This fit is done using \texttt{MultiNest}, via the
+\isochrones\footnote{\url{https://github.com/timothydmorton/isochrones}}
+Python module.  Monte Carlo samples of stellar properties for the
+population simulations are then drawn directly from these posterior
+samples.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+As a result, a by-product of the \vespa\ \ac{fpp} calculation is full
+posterior samples of the physical properties of the star, modeled as a
+single, binary, or triple system.  Parameters directly fitted for in
+this process are stellar mass, age, [Fe/H], $A_V$ extinction, and
+distance.  For binary and triple fits, secondary and/or tertiary mass
+parameters are added, with all other parameters assumed to be the same
+among all components.  Photometric observations upon which these fits
+are conditioned are assumed to be the sum of all components.  If
+spectroscopic and/or asteroseismic measurements are used (e.g.,
+constraints on effective temperature or stellar surface gravity), they
+are assumed to relate to only the primary star.  Priors used in these
+fits are listed in Table \ref{table:priors}.  Posterior chains of all
+other stellar parameters of interest (e.g., temperature, surface
+gravity, radius, etc.) are derived from the chains of fitting
+parameters by evaluting the stellar models.
 
-\subsection{False Positive Probabilities}
-\label{sec:methods:fpp}
+\begin{deluxetable}{cc}
+\tablewidth{0pt}
+\tabletypesize{\scriptsize}
+\tablecaption{Priors used in stellar fits}
+\tablehead{
+\colhead{Parameter} &
+\colhead{Prior}}
+\startdata
+Primary mass $M$ & $\propto M^{-2.35}$ \\
+Age {[}Gyr{]} & $\mathcal U(1,15) $\\
+{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$ \\
+$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$ \\
+Distance d & $\propto d^2$ 
+\enddata
+\label{table:priors}
+\end{deluxetable}
 

### 2015-07-22 ms.tex

@@
 \usepackage{natbib}
+\usepackage{amssymb,amsmath}
+\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage[all]{hypcap}
+\renewcommand*{\backref}[1]{[#1]}
+
 \usepackage{acronym}
-\usepackage{amssymb,amsmath}
 
@@
 
-\newcommand{\ntotal}{5500}
-\newcommand{\nfail}{1000}
+\newcommand{\ntotal}{8826}
+\newcommand{\nfail}{1584}
+\newcommand{\ncalc}{7242}
 \newcommand{\nval}{1500}
@@
 \kepler\ Object of Interest (KOI) from the Q1-Q16 catalog release.
-Out of \ntotal\ KOIs, we determine that \nval\ have probabilities
+Out of \ncalc\ KOIs, we determine that \nval\ have probabilities
 $<$1\% to be astrophysical false positives, and thus may be considered
@@
 procedure described in \citet[][hereafter
-  \citetalias{Morton:2012}]{Morton:2012} to all \acp{koi} listed in
-the ``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
-Archive.  While we refer the reader to \citetalias{Morton:2012} for a
-detailed description of the method, we outline it briefly in this
-section.  The procedure as implemented here is now publicly available
-in the Python module
-\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}.
+  \citetalias{Morton:2012}]{Morton:2012} to \ncalc\ \acp{koi} (see
+\autoref{sec:data} for details).  While we refer the reader to
+\citetalias{Morton:2012} for a detailed description of the method, we
+outline it briefly in this section.  The procedure as implemented here
+is now publicly available in the Python module
+\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
+\citep{vespa}.
 
@@
 where $\pi_i$ is the ``hypothesis prior'' and $\mathcal L_i$ is the
-``hypothesis likelihood'' (also known as ``evidence'' or
-``marginalized likelihood'').  The prior represents how intrinsically
-probable the hypothesized scenario is to exist, and the likelihood
-represents how closely the shape of the observed transit signal
-matches with the expected shape of a signal produced by the
-hypothesis.
+``hypothesis likelihood''\footnote{This factor is more widely known as
+  the ``Bayesian evidence'' or ``marginalized likelihood'';
+  \citet{Morton:2014b} argues for the term ``hypothesis likelihood,''
+  as it can be clarifying to think of it that way.}
+The prior represents how intrinsically probable the hypothesized
+scenario is to exist, and the likelihood represents how closely the
+shape of the observed transit signal matches with the expected shape
+of a signal produced by the hypothesis.
 
@@
 $p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
-PDF for the parameters under hypothesis $i$.
+PDF for the parameters under hypothesis $i$.\footnote{$\mathcal L_i$
+  may be seen to be the ``evidence'' or ``marginalized likelihood'' of
+  the trapezoidal model under hypothesis $i$, with $p_\mathrm{sig}$
+  being the likelihood and $p_i$ being the prior, integrated over the
+  $\bvec{\theta}$ parameter space.  But for clarity, and for
+  continuity with previous publication, we continue to call $\mathcal
+  L_i$ the ``likelihood'' for hypothesis $i$.}
 
@@
 the target star are folded into the population simulations of each
-hypothesis (see \S\ref{sec:methods:stellar}).  All other constraints are
+hypothesis (see \autoref{sec:methods:stellar}).  All other constraints are
 applied to narrow down which simulated instances of each scenario may
@@
 only blended eclipsing binaries with secondary eclipse depths
-shallower than the observed limits are allowed.
+shallower than the observed limits contribute to the construction of
+the $p_i$ trapezoidal shape parameter PDF.
 
@@
   being considered (conditioned on available observations of the
-  target star; see \S\ref{sec:methods:stellar}).
+  target star; see \autoref{sec:methods:stellar}).
 \item Fit each simulated eclipse in each scenario with a trapezoid
@@
 generated according to the stellar population expected along the line
-of sight by \ac{trilegal}, but constrained to agree with some observed
-color(s) of the star (e.g. $J-K$), to within some specified tolerance.
-This strategy was used both to generate the host stars for the
-transiting planet model and the binary and triple stars for the EB and
-HEB false positive models.
+of sight by the \ac{trilegal} Galactic stellar popultion synthesis
+tool, but constrained to agree with some observed color(s) of the star
+(e.g. $J-K$), to within some specified tolerance.  This strategy was
+used both to generate the host stars for the transiting planet model
+and the binary and triple stars for the EB and HEB false positive
+models.
 
-The new method now used by \vespa\ to fold in observational
-constraints on the host star debuted in \citet{Montet:2015} (and is
-explained there in more detail).  Instead of randomly generating stars
-(or binary or triple systems of stars) from a predefined distribution and
-culling them to agree with observed colors, \emph{all} available
-constraints on the target star are used to condition a direct fit of
-either a single-, binary-, or triple-star model to the Dartmouth grid
-of stellar models.  This fit is done using \texttt{MultiNest}, via the
-\isochrones\footnote{\url{https://github.com/timothydmorton/isochrones}}
-Python module.  Monte Carlo samples of stellar properties for the
-population simulations are then drawn directly from these posterior
-samples.
+The new method now used by \vespa\ uses the \isochrones\ Python module
+\citep{isochrones} to fold in observational constraints on the host
+star.  At its core, \isochrones\ performs 3-D linear interpolation in
+mass--[Fe/H]--age parameter space for a given stellar model grid.
+This method of stellar modeling for FPP calculation debuted in
+\citet{Montet:2015} and is explained there in more detail.  Instead of
+randomly generating stars (or binary or triple systems of stars) from
+a predefined distribution and culling them to agree with observed
+colors, \emph{all} available constraints on the target star are used
+to condition a direct fit of either a single--, binary--, or
+triple--star model to the Dartmouth grid of stellar models.  This fit
+is done using \texttt{MultiNest} \citep{Feroz:2009, Feroz:2011,
+  Feroz:2013}, via the \texttt{PyMultiNest} wrapper
+\citep{Buchner:2014}.  Monte Carlo samples of stellar properties for
+the population simulations are then drawn directly from these
+posterior samples.
 
-As a result, a by-product of the \vespa\ \ac{fpp} calculation is full
-posterior samples of the physical properties of the star, modeled as a
-single, binary, or triple system.  Parameters directly fitted for in
-this process are stellar mass, age, [Fe/H], $A_V$ extinction, and
-distance.  For binary and triple fits, secondary and/or tertiary mass
-parameters are added, with all other parameters assumed to be the same
-among all components.  Photometric observations upon which these fits
-are conditioned are assumed to be the sum of all components.  If
-spectroscopic and/or asteroseismic measurements are used (e.g.,
-constraints on effective temperature or stellar surface gravity), they
-are assumed to relate to only the primary star.  Priors used in these
-fits are listed in Table \ref{table:priors}.  Posterior chains of all
-other stellar parameters of interest (e.g., temperature, surface
-gravity, radius, etc.) are derived from the chains of fitting
-parameters by evaluting the stellar models.
+As a result, \vespa\ creates full posterior samplings of the physical
+properties of the host star, modeled as a single, binary, and triple
+star system, as a by-product of the \ac{fpp} calculation.  Parameters
+directly fitted for in this process are stellar mass, age, [Fe/H],
+$A_V$ extinction, and distance.  For binary and triple fits, secondary
+and/or tertiary mass parameters are added, with all other parameters
+assumed to be the same among all components.  Photometric observations
+upon which these fits are conditioned are assumed to be the sum of all
+components.  If spectroscopic and/or asteroseismic measurements are
+used (e.g., constraints on effective temperature or stellar surface
+gravity), they are assumed to relate to only the primary star.  Priors
+used in these fits are listed in \autoref{table:priors}.  Posterior
+chains of all other stellar parameters of interest (e.g., temperature,
+surface gravity, radius, etc.) are derived from the chains of fitting
+parameters by evaluting the stellar models using \isochrones.
 
+\capstartfalse
 \begin{deluxetable}{cc}
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Priors used in stellar fits}
+\tablecaption{Priors used in stellar property fits}
 \tablehead{
@@
 \startdata
-Primary mass $M$ & $\propto M^{-2.35}$ \\
-Age {[}Gyr{]} & $\mathcal U(1,15) $\\
-{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$ \\
-$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$ \\
-Distance d & $\propto d^2$ 
+Primary mass $M_A$ & $\propto M_A^{-2.35},~M_A > 0.1$ \\
+Secondary mass $M_B$ & $\propto (M_B/M_A)^{0.3},~0.1 <= M_B < M_A$ \\
+Tertiary mass $M_C$ & $\propto (M_C/M_A)^{0.3},~0.1 <= M_C < M_B$ \\
+Age {[}Gyr{]} & $\mathcal U(1,15)$ \tablenotemark{a}\\
+{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) +
+\frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$  \tablenotemark{b}\\
+$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$
+\tablenotemark{c} \\
+Distance $d$ & $\propto d^2$ 
 \enddata
+\tablenotetext{a}{The age range for the Dartmouth stellar model grids
+  used.}
+\tablenotetext{b}{Double-Gaussian fit to measured local stellar metallicity
+  distribution \citep{Hayden:2015, Casagrande:2011}.}
+\tablenotetext{3}{Maximum allowed value is the Galactic extinction at
+  infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
 \label{table:priors}
 \end{deluxetable}
+\capstarttrue
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data and Constraints}
+\label{sec:data}
+
+The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
+regardless of classification as CONFIRMED, CANDIDATE, or
+FALSE POSITIVE.  As such, we begin with a list of
+\ntotal\ \acp{koi} from the cumulative table at the \ac{nexsci}
+Exoplanet Archive.  However, for various reasons, the ancillary data
+and constraints that we describe below are not available for every
+\ac{koi}, and so in the end we present \ac{fpp} results for
+\ncalc\ \acp{koi}.
 

### 2015-07-22 ms.tex
more writing

@@
 %%
-\documentclass[preprint2]{aastex}
-%\documentclass[iop]{emulateapj}
+%\documentclass[preprint2]{aastex}
+\documentclass{emulateapj}
 
@@
 \defcitealias{Morton:2012}{M12}
-
-\acrodef{fpp}[FPP]{false positive probability}
-\acrodef{koi}[KOI]{\kepler\ Object of Interest}
-\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
-\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
-\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
-\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
 
@@
 We present the results of applying a fully automated transit signal
-false positive probability calculating procedure to every
-\kepler\ Object of Interest (KOI) from the Q1-Q16 catalog release.
-Out of \ncalc\ KOIs, we determine that \nval\ have probabilities
+false positive probability calculating procedure to every \ac{koi}.
+Out of \ncalc\ \acp{koi}, we determine that \nval\ have probabilities
 $<$1\% to be astrophysical false positives, and thus may be considered
@@
 \section{Introduction}
+\acresetall
 
@@
 to condition a direct fit of either a single--, binary--, or
-triple--star model to the Dartmouth grid of stellar models.  This fit
-is done using \texttt{MultiNest} \citep{Feroz:2009, Feroz:2011,
-  Feroz:2013}, via the \texttt{PyMultiNest} wrapper
-\citep{Buchner:2014}.  Monte Carlo samples of stellar properties for
-the population simulations are then drawn directly from these
-posterior samples.
+triple--star model to the Dartmouth grid of stellar models
+\citep{Dotter:2008, Feiden:2011}.  This fit is done using
+\texttt{MultiNest} \citep{Feroz:2009, Feroz:2011, Feroz:2013}, via the
+\texttt{PyMultiNest} wrapper \citep{Buchner:2014}.  Monte Carlo
+samples of stellar properties for the population simulations are then
+drawn directly from these posterior samples.
 
@@
 The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
-regardless of classification as CONFIRMED, CANDIDATE, or
-FALSE POSITIVE.  As such, we begin with a list of
-\ntotal\ \acp{koi} from the cumulative table at the \ac{nexsci}
-Exoplanet Archive.  However, for various reasons, the ancillary data
-and constraints that we describe below are not available for every
-\ac{koi}, and so in the end we present \ac{fpp} results for
-\ncalc\ \acp{koi}.
+regardless of classification as CONFIRMED, CANDIDATE, or FALSE
+POSITIVE.  As such, we begin with a list of \ntotal\ \acp{koi} from
+the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
+gather ancillary data and constraints from various sources (described
+below) in order to enable the \vespa\ calculation. For various
+reasons, the data are not available for every \ac{koi}, and so in the
+end we present \ac{fpp} results for \ncalc\ \acp{koi}.
+
+For each \ac{koi} we obtain the following data:
+\begin{enumerate}
+\item The RA/Dec coordinates of each star from the \ac{kic}.
+\item $grizJHK$ photometry from the \ac{kic}, with $griz$ bands
+  corrected to the \ac{sdss} photometric scale according to
+  \citet{Pinsonneault:2012}.
+\item Stellar $T_\mathrm{eff}$, [Fe/H], and $\log g$ values and
+  uncertainties from the \citet{Huber:2014} stellar properties
+  catalog, if the provenance of these values is from spectroscopy or
+  asteroseismology.
+\item Detrended \kepler\ photometry used for the \ac{mcmc} modeling of
+  \citet{Rowe:2015}, along with information about individually fitted
+  transit times, where available.
+\item Best-fit $R_p/R_\star$ from the \citet{Rowe:2015} MCMC analysis.
+\item Centroid uncertainty information from the \ac{nexsci} Exoplanet
+  Archive: we assume that the allowed ``exclusion'' radius for a blend
+  scenario is 3$\times$ the uncertainty in the fitted centroid
+  position (the \verb|koi_dicco_msky_err| column in the Archive
+  table).  We floor this value at 0\farcs5, to prevent unrealistically
+  small exclusion radii.
+\item The maximum secondary eclipse depth allowed by the
+  \kepler\ photometry.  This quantity is obtained from vetting
+  metrics produced internally by the \kepler\ Science Office.  When
+  these metrics are not available for a particular \ac{koi}, we
+  default to 10$\times$ the uncertainty in the \kepler\ pipeline
+  measured transit depth (\verb|koi_depth_err1|).
+
+\end{enumerate}
 
@@
 
+\acrodef{fpp}[FPP]{false positive probability}
+\acrodef{koi}[KOI]{\kepler\ Object of Interest}
+\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
+\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
+\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
+\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
+\acrodef{kic}[KIC]{Kepler Input Catalog}
+\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
+
 \acknowledgments

### 2015-07-23 ms.tex
more work

@@
 \usepackage{amssymb,amsmath}
+\usepackage{color}
 \usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
@@
 \newcommand{\nfpnew}{200}
+\newcommand{\nbadphot}{1009} %EmptyPhotometry or MissingKOI
+\newcommand{\nbadphotFP}{897}
+\newcommand{\nbadphotCAND}{111}
+\newcommand{\nbadrowemcmc}{210}
+\newcommand{\nbadstellar}{80} %MissingStellar
+\newcommand{\nbadsec}{82} %NoWeakSecondary
 \newcommand{\kepler}{\textit{Kepler}}
@@
 \newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
+
+%% TODO commands
+\newcommand{\todo}[3]{{\color{#2} \emph{#1} TODO: #3}}
+\newcommand{\tdmtodo}[1]{\todo{TDM}{red}{#1}}
 
@@
 the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
-gather ancillary data and constraints from various sources (described
-below) in order to enable the \vespa\ calculation. For various
-reasons, the data are not available for every \ac{koi}, and so in the
-end we present \ac{fpp} results for \ncalc\ \acp{koi}.
+gather ancillary data and constraints from various sources in order to
+enable the \vespa\ calculation:
 
-For each \ac{koi} we obtain the following data:
 \begin{enumerate}
@@
   default to 10$\times$ the uncertainty in the \kepler\ pipeline
-  measured transit depth (\verb|koi_depth_err1|).
+  measured transit depth (\verb|koi_depth_err1|).  While these
+  secondary metrics are not yet available on the Archive, they should
+  become available with the final data release.
 
 \end{enumerate}
+
+Of the \ntotal\ total \acp{koi}, \nbadphot\ did not receive \ac{mcmc}
+modeling.  Most of these (\nbadphotFP) are already designated FALSE
+POSITIVE at the archive, though \nbadphotCAND\ have CANDIDATE
+disposition.  One, K00245.04, is a confirmed planet.  \tdmtodo{Find
+  out why??}  An additional \nbadrowemcmc\ did receive \ac{mcmc}
+modeling but had unphysical fit results; e.g., negative $R_p/R_\star$
+or best-fit impact parameter greater than $(1 + R_p/R_\star)$.  Of the
+\acp{koi} that did have usable \ac{mcmc} fits, \nbadsec\ had no
+\verb|koi_depth_err1| on the archive, and thus had no weak secondary
+constraint and were left out of the calculations.  After all these
 
@@
 \acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
+\acrodef{ttv}[TTV]{transit timing variations}
 

### 2015-07-29 ms.tex
further work
more work (latex tables done?)

@@
 \newcommand{\nbadsec}{82} %NoWeakSecondary
+\newcommand{\nattempted}{7317}
+\newcommand{\ntryfail}{75}
 \newcommand{\kepler}{\textit{Kepler}}
@@
 \defcitealias{Morton:2012}{M12}
+\defcitealias{Huber:2014}{H14}
 
@@
 calculations is full stellar property posterior samplings for every
-host star, modeled as single, binary, and triple.  These calculations
-use \vespa, a publicly available Python package able to be easily
-applied to any transiting exoplanet candidate.
+host star, modeled as single, binary, and triple systems.  These
+calculations use \vespa, a publicly available Python package able to
+be easily applied to any transiting exoplanet candidate.
 \end{abstract}
@@
 triple--star model to the Dartmouth grid of stellar models
-\citep{Dotter:2008, Feiden:2011}.  This fit is done using
-\texttt{MultiNest} \citep{Feroz:2009, Feroz:2011, Feroz:2013}, via the
+\citep{Dotter:2008, Feiden:2011}.  This fit is done using multi-modal
+nested sampling, implemented with \texttt{MultiNest}
+\citep{Feroz:2009, Feroz:2011, Feroz:2013}, via the
 \texttt{PyMultiNest} wrapper \citep{Buchner:2014}.  Monte Carlo
@@
 gravity), they are assumed to relate to only the primary star.  Priors
-used in these fits are listed in \autoref{table:priors}.  Posterior
+used in these fits are listed in \autoref{table:priors}---notably, we
+use a prior on [Fe/H] based on a double-Gaussian fit to the local
+metallicity distribution \citep{Hayden:2015, Casagrande:2011}.  Posterior
 chains of all other stellar parameters of interest (e.g., temperature,
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Priors used in stellar property fits}
+\tablecaption{Priors used in stellar property fits
+\label{table:priors}}
 \tablehead{
@@
   infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
-\label{table:priors}
 \end{deluxetable}
@@
   table).  We floor this value at 0\farcs5, to prevent unrealistically
-  small exclusion radii.
+  small exclusion radii.  If this quantity is not available from the
+  Archive we set a default exclusion radius of 4\arcsec.
 \item The maximum secondary eclipse depth allowed by the
@@
 
+%This leaves \nattempted\ \acp{koi} upon which we run \vespa.
+%\ntryfail of these encounter runtime errors during the
+%\vespa\ calculation; these are further explained below in
+%\autoref{sec:failures}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+\label{sec:results}
+
+The results of the \vespa\ calculations are presented in
+\autoref{table:stars} and \autoref{table:fpp}, and are discussed in
+the following subsections.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Stellar Properties}
+\label{sec:results:stars}
+
+As discussed in \autoref{sec:methods:stellar}, \vespa\ fits for stellar
+properties as part of its \ac{fpp}--calculating procedure, using the
+\isochrones\ package.  Thus, we obtain posterior samplings of the
+physical properties of each \ac{koi} as a side effect of this batch
+calculation, a result of general interest independent of \acp{fpp}.
+\autoref{table:stars} presents summarized results of the single--star
+fits.  While \vespa\ also fits double-- and triple--star models for
+each \ac{koi}, these are of less general interest and so we do not
+present them separately.
+
+\autoref{fig:starsteff} and \autoref{fig:starsfehradius} compare the
+estimated effective temperatures, metallicities, and radii, derived
+here to those independently determined for the official
+\kepler\ stellar properties catalog \citep[][hereafter
+  \citetalias{Huber:2014}]{Huber:2014}.  While there is largely
+general agreement, there are also discrepancies, highlighting the
+difficulty of estimating physical stellar properties.  In particular,
+we note that for stars which \citetalias{Huber:2014} list as $T_{\rm eff}
+< 4000$\,K, \isochrones\ predicts systematically hotter temperatures.
+Most of the \citetalias{Huber:2014} properties for these stars are
+taken from \citet{dressing:2013}.
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/hubercompare_teff.pdf}
+\end{center}
+\caption{Comparison between effective temperatures estimated from the
+  \isochrones\ analysis in this work and those from the
+  \kepler\ stellar parameters catalog \citep[][hereafter
+    \citetalias{Huber:2014}]{Huber:2014}.  Bottom panel shows stars
+  for which \citetalias{Huber:2014} predicts $T_{\rm eff} < 4500$\,K,
+  middle spans $4500\,{\rm K} < T_{\rm eff} < 6500\,{\rm K}$, and top
+  has $T_{\rm eff} > 6500$\,K. Blue horizontal bold lines are the
+  \citetalias{Huber:2014} values in sorted order; blue shading
+  represents the error bars from \citetalias{Huber:2014}.  Vertical
+  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
+  these lines are grey if they overlap with the
+  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
+  marked by a point) if they are inconsistent.  This comparison shows
+  that the stellar parameters estimated in this work are broadly
+  consistent with \citetalias{Huber:2014}, though less so for the
+  coolest and hottest stars.
+\label{fig:starsteff}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/hubercompare_fehradius.pdf}
+\end{center}
+\caption{Comparison between metallicities and radii estimated from the
+  \isochrones\ analysis in this work and those from the
+  \kepler\ stellar parameters catalog \citep[][hereafter
+    \citetalias{Huber:2014}]{Huber:2014}.  Top panel shows metallicity
+  for all stars in the sample.  The middle panel shows stars for which
+  \citetalias{Huber:2014} estimates $R_\star < 2\,R_\odot$, and the
+  bottom shows $R_\star > 2\,R_\odot$. Blue horizontal bold lines are
+  the \citetalias{Huber:2014} values in sorted order; blue shading
+  represents the error bars from \citetalias{Huber:2014}.  Vertical
+  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
+  these lines are grey if they overlap with the
+  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
+  marked by a point) if they are inconsistent.  This comparison shows
+  that the stellar parameters estimated in this work are broadly
+  consistent with \citetalias{Huber:2014}, though less so for the more
+  evolved stars.  The metallicity estimates of the
+  \isochrones\ calculations are driven by the use of the local
+  metallicity prior \citep[][\autoref{table:priors}]{Hayden:2015,
+    Casagrande:2011}.
+\label{fig:starsfehradius}}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{False Positive Probabilities}
+\label{sec:results:fpp}
+
+Of the \ntotal\ \acp{koi} in the cumulative
+table at the \ac{nexsci} Exoplanet Archive, \vespa\ successfully
+calculated the \ac{fpp} for \ncalc.  Most of the \nfail\ failures are a
+result of a \ac{koi} no longer being ``of interest,'' despite still
+being listed in the cumulative table.  \autoref{sec:failures} contains
+detailed explanations of the different failure modes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Failure Modes}
+\label{sec:failures}
+
 Of the \ntotal\ total \acp{koi}, \nbadphot\ did not receive \ac{mcmc}
@@
 \acp{koi} that did have usable \ac{mcmc} fits, \nbadsec\ had no
-\verb|koi_depth_err1| on the archive, and thus had no weak secondary
-constraint and were left out of the calculations.  After all these
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:results}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Stellar Properties}
-\label{sec:results:stars}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{False Positive Probabilities}
-\label{sec:results:fpp}
+\verb|koi_depth_err1| value on the archive, and thus had no weak
+secondary constraint and were left out of the calculations.
 
@@
 
+\capstartfalse
+\input{table_stars}
+\capstarttrue
+
+\capstartfalse
+\input{table_fpp}
+\capstarttrue
+
 \end{document}

### 2015-07-29 ms.tex
more stellar parameter discussion re: D13

@@
 \defcitealias{Huber:2014}{H14}
+\defcitealias{Dressing:2013}{D13}
 
@@
 general agreement, there are also discrepancies, highlighting the
-difficulty of estimating physical stellar properties.  In particular,
-we note that for stars which \citetalias{Huber:2014} list as $T_{\rm eff}
-< 4000$\,K, \isochrones\ predicts systematically hotter temperatures.
-Most of the \citetalias{Huber:2014} properties for these stars are
-taken from \citet{dressing:2013}.
+difficulty of estimating physical stellar properties.
+
+In particular, we note that for stars which \citetalias{Huber:2014}
+list as $T_{\rm eff} < 4000$\,K, \isochrones\ predicts systematically
+hotter temperatures.  Most of the \citetalias{Huber:2014} properties
+for these stars are taken from
+\citet[][\citetalias{dressing:2013}]{dressing:2013}.  Those properties
+were determined by trying to match the colors of each star to the colors
+of a grid of model stars from the Dartmouth models, supplemented by
+some interpolation.  \citetalias{dressing:2013} also imposed priors
+on [Fe/H] and the height of stars above the plane of the Galaxy.  To
+validate their methodology, \citetalias{dressing:2013} compare their
+predictions of 26 nearby stars (with parallax)
 

### 2015-08-17 ms.tex

@@
 for these stars are taken from
-\citet[][\citetalias{dressing:2013}]{dressing:2013}.  Those properties
+\citet[][\citetalias{Dressing:2013}]{Dressing:2013}.  Those properties
 were determined by trying to match the colors of each star to the colors
 of a grid of model stars from the Dartmouth models, supplemented by
-some interpolation.  \citetalias{dressing:2013} also imposed priors
+some interpolation.  \citetalias{Dressing:2013} also imposed priors
 on [Fe/H] and the height of stars above the plane of the Galaxy.  To
-validate their methodology, \citetalias{dressing:2013} compare their
-predictions of 26 nearby stars (with parallax)
+validate their methodology, \citetalias{Dressing:2013} compare their
+results for 26 nearby stars to the masses predicted for those stars by
+combining parallax measurements with the \citet{Delfosse:2000}
+relation between mass and absolute $K$-band magnitude.  While they
+find general good agreement, the \citetalias{Dressing:2013} masses are
+noted to be on average about 5\% lower than the Delfosse-predicted masses.
 

### 2015-08-19 ms.tex
removed acronym package

@@
 \usepackage{amssymb,amsmath}
-\usepackage{color}
+\usepackage{color}%,hyperref}
+%\definecolor{linkcolor}{rgb}{0,0,0.5}
+%\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
+%            filecolor=linkcolor,urlcolor=linkcolor}
+%\usepackage{url}
+
 \usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
@@
 
-\capstartfalse
+%\capstartfalse
 \begin{deluxetable}{cc}
@@
 Age {[}Gyr{]} & $\mathcal U(1,15)$ \tablenotemark{a}\\
-{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) +
-\frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$  \tablenotemark{b}\\
-$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$
-\tablenotemark{c} \\
+{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$  \tablenotemark{b}\\
+$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$ \tablenotemark{c} \\
 Distance $d$ & $\propto d^2$ 
 \enddata
-\tablenotetext{a}{The age range for the Dartmouth stellar model grids
-  used.}
-\tablenotetext{b}{Double-Gaussian fit to measured local stellar metallicity
-  distribution \citep{Hayden:2015, Casagrande:2011}.}
+\tablenotetext{a}{The age range for the Dartmouth stellar model grids used.}
+\tablenotetext{b}{Double-Gaussian fit to measured local stellar
+  metallicity distribution \citep{Hayden:2015, Casagrande:2011}.}
 \tablenotetext{3}{Maximum allowed value is the Galactic extinction at
@@
 \end{deluxetable}
-\capstarttrue
+%\capstarttrue
 
@@
 
-\capstartfalse
+%\capstartfalse
 \input{table_stars}
-\capstarttrue
+%\capstarttrue
 
-\capstartfalse
+%\capstartfalse
 \input{table_fpp}
-\capstarttrue
+%\capstarttrue
 

### 2015-08-19 ms.tex
put back capstarts

@@
 
-%\capstartfalse
+\capstartfalse
 \begin{deluxetable}{cc}
@@
 Age {[}Gyr{]} & $\mathcal U(1,15)$ \tablenotemark{a}\\
-{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$  \tablenotemark{b}\\
+{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$  \tablenotemark{b} \\
 $A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$ \tablenotemark{c} \\
@@
 \end{deluxetable}
-%\capstarttrue
+\capstarttrue
 
@@
 
-%\capstartfalse
+\capstartfalse
 \input{table_stars}
-%\capstarttrue
+\capstarttrue
 
-%\capstartfalse
+\capstartfalse
 \input{table_fpp}
-%\capstarttrue
+\capstarttrue
 

### 2015-08-19 ms.tex
remove acronym usage

@@
 \usepackage{amssymb,amsmath}
-\usepackage{color}%,hyperref}
-%\definecolor{linkcolor}{rgb}{0,0,0.5}
-%\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
-%            filecolor=linkcolor,urlcolor=linkcolor}
-%\usepackage{url}
+\usepackage{color,hyperref}
+\definecolor{linkcolor}{rgb}{0,0,0.5}
+\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
+            filecolor=linkcolor,urlcolor=linkcolor}
+\usepackage{url}
 
-\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
-\usepackage[all]{hypcap}
-\renewcommand*{\backref}[1]{[#1]}
+%\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
+%\usepackage[all]{hypcap}
+%\renewcommand*{\backref}[1]{[#1]}
 
-\usepackage{acronym}
+%\usepackage{acronym}
 
@@
 We present the results of applying a fully automated transit signal
-false positive probability calculating procedure to every \ac{koi}.
-Out of \ncalc\ \acp{koi}, we determine that \nval\ have probabilities
+false positive probability calculating procedure to every Kepler
+Object of Interest (KOI).
+Out of \ncalc\ KOIs, we determine that \nval\ have probabilities
 $<$1\% to be astrophysical false positives, and thus may be considered
@@
 \section{Introduction}
-\acresetall
 
@@
 
-\ac{fpp} and then \ac{fpp}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this work, we apply the fully automated \ac{fpp}-computing
+In this work, we apply the fully automated FPP-computing
 procedure described in \citet[][hereafter
-  \citetalias{Morton:2012}]{Morton:2012} to \ncalc\ \acp{koi} (see
+  \citetalias{Morton:2012}]{Morton:2012} to \ncalc\ KOIs (see
 \autoref{sec:data} for details).  While we refer the reader to
@@
 being evaluated, the joint posterior probability density function
-(PDF) of these shape parameters is sampled with \ac{mcmc}, using the
+(PDF) of these shape parameters is sampled with Markov Chain Monte
+Carlo (MCMC), using the
 \texttt{emcee} sampler \citep{emcee}.  This allows the likelihood for
@@
 
-The steps \vespa\ takes to calculate the \ac{fpp} of a transit signal
+The steps \vespa\ takes to calculate the FPP of a transit signal
 are thus as follows:
 \begin{enumerate}
-\item Fit trapezoid model to observed transit signal using \ac{mcmc}.
+\item Fit trapezoid model to observed transit signal using MCMC.
 \item Generate population simulations for each hypothesis scenario
@@
   account all available observational constraints, in order to
-  calculate the \ac{fpp}.
+  calculate the FPP.
 \end{enumerate}
@@
 generated according to the stellar population expected along the line
-of sight by the \ac{trilegal} Galactic stellar popultion synthesis
-tool, but constrained to agree with some observed color(s) of the star
-(e.g. $J-K$), to within some specified tolerance.  This strategy was
-used both to generate the host stars for the transiting planet model
-and the binary and triple stars for the EB and HEB false positive
-models.
+of sight by the TRIdimensional modeL of thE GALaxy (TRILEGAL) Galactic
+stellar popultion synthesis tool, but constrained to agree with some
+observed color(s) of the star (e.g. $J-K$), to within some specified
+tolerance.  This strategy was used both to generate the host stars for
+the transiting planet model and the binary and triple stars for the EB
+and HEB false positive models.
 
@@
 properties of the host star, modeled as a single, binary, and triple
-star system, as a by-product of the \ac{fpp} calculation.  Parameters
+star system, as a by-product of the FPP calculation.  Parameters
 directly fitted for in this process are stellar mass, age, [Fe/H],
@@
 \enddata
-\tablenotetext{a}{The age range for the Dartmouth stellar model grids used.}
-\tablenotetext{b}{Double-Gaussian fit to measured local stellar
-  metallicity distribution \citep{Hayden:2015, Casagrande:2011}.}
-\tablenotetext{3}{Maximum allowed value is the Galactic extinction at
-  infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
+%\tablenotetext{a}{The age range for the Dartmouth stellar model grids used.}
+%\tablenotetext{b}{Double-Gaussian fit to measured local stellar
+%  metallicity distribution \citep{Hayden:2015, Casagrande:2011}.}
+%\tablenotetext{3}{Maximum allowed value is the Galactic extinction at
+%  infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
 \end{deluxetable}
-\capstarttrue
+%\capstarttrue
 
@@
 
-The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
+The goal of this work is to calculate the FPP for every KOI,
 regardless of classification as CONFIRMED, CANDIDATE, or FALSE
-POSITIVE.  As such, we begin with a list of \ntotal\ \acp{koi} from
-the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
-gather ancillary data and constraints from various sources in order to
-enable the \vespa\ calculation:
+POSITIVE.  As such, we begin with a list of \ntotal\ KOIs from the
+cumulative table at the NASA Exoplanet Science Institute (NExScI)
+Exoplanet Archive.  We then gather ancillary data and constraints from
+various sources in order to enable the \vespa\ calculation:
 
 \begin{enumerate}
-\item The RA/Dec coordinates of each star from the \ac{kic}.
-\item $grizJHK$ photometry from the \ac{kic}, with $griz$ bands
-  corrected to the \ac{sdss} photometric scale according to
-  \citet{Pinsonneault:2012}.
+\item The RA/Dec coordinates of each star from the Kepler Input
+  Catalog (KIC).
+\item $grizJHK$ photometry from the KIC, with $griz$ bands corrected
+  to the Sloan Digital Sky Survey (SDSS) photometric scale according
+  to \citet{Pinsonneault:2012}.
 \item Stellar $T_\mathrm{eff}$, [Fe/H], and $\log g$ values and
@@
   asteroseismology.
-\item Detrended \kepler\ photometry used for the \ac{mcmc} modeling of
+\item Detrended \kepler\ photometry used for the MCMC modeling of
   \citet{Rowe:2015}, along with information about individually fitted
@@
 \item Best-fit $R_p/R_\star$ from the \citet{Rowe:2015} MCMC analysis.
-\item Centroid uncertainty information from the \ac{nexsci} Exoplanet
+\item Centroid uncertainty information from the NExScI Exoplanet
   Archive: we assume that the allowed ``exclusion'' radius for a blend
@@
   metrics produced internally by the \kepler\ Science Office.  When
-  these metrics are not available for a particular \ac{koi}, we
+  these metrics are not available for a particular KOI, we
   default to 10$\times$ the uncertainty in the \kepler\ pipeline
@@
 As discussed in \autoref{sec:methods:stellar}, \vespa\ fits for stellar
-properties as part of its \ac{fpp}--calculating procedure, using the
+properties as part of its FPP--calculating procedure, using the
 \isochrones\ package.  Thus, we obtain posterior samplings of the
-physical properties of each \ac{koi} as a side effect of this batch
-calculation, a result of general interest independent of \acp{fpp}.
+physical properties of each KOI as a side effect of this batch
+calculation, a result of general interest independent of FPP.
 \autoref{table:stars} presents summarized results of the single--star
 fits.  While \vespa\ also fits double-- and triple--star models for
-each \ac{koi}, these are of less general interest and so we do not
+each KOI, these are of less general interest and so we do not
 present them separately.
@@
 
-Of the \ntotal\ \acp{koi} in the cumulative
-table at the \ac{nexsci} Exoplanet Archive, \vespa\ successfully
-calculated the \ac{fpp} for \ncalc.  Most of the \nfail\ failures are a
-result of a \ac{koi} no longer being ``of interest,'' despite still
+Of the \ntotal\ KOIs in the cumulative
+table at the NExScI Exoplanet Archive, \vespa\ successfully
+calculated the FPP for \ncalc.  Most of the \nfail\ failures are a
+result of a KOI no longer being ``of interest,'' despite still
 being listed in the cumulative table.  \autoref{sec:failures} contains
@@
 
-Of the \ntotal\ total \acp{koi}, \nbadphot\ did not receive \ac{mcmc}
+Of the \ntotal\ total KOIs, \nbadphot\ did not receive MCMC
 modeling.  Most of these (\nbadphotFP) are already designated FALSE
@@
 disposition.  One, K00245.04, is a confirmed planet.  \tdmtodo{Find
-  out why??}  An additional \nbadrowemcmc\ did receive \ac{mcmc}
+  out why??}  An additional \nbadrowemcmc\ did receive MCMC
 modeling but had unphysical fit results; e.g., negative $R_p/R_\star$
 or best-fit impact parameter greater than $(1 + R_p/R_\star)$.  Of the
-\acp{koi} that did have usable \ac{mcmc} fits, \nbadsec\ had no
+KOIs that did have usable MCMC fits, \nbadsec\ had no
 \verb|koi_depth_err1| value on the archive, and thus had no weak
@@
 
-\acrodef{fpp}[FPP]{false positive probability}
-\acrodef{koi}[KOI]{\kepler\ Object of Interest}
-\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
-\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
-\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
-\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
-\acrodef{kic}[KIC]{Kepler Input Catalog}
-\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
-\acrodef{ttv}[TTV]{transit timing variations}
+%\acrodef{fpp}[FPP]{false positive probability}
+%\acrodef{koi}[KOI]{\kepler\ Object of Interest}
+%\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
+%\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
+%\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
+%\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
+%\acrodef{kic}[KIC]{Kepler Input Catalog}
+%\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
+%\acrodef{ttv}[TTV]{transit timing variations}
 

### 2015-08-19 ms.tex
stellar properties text

@@
 \bibliographystyle{apj}
+
+\newcommand{\figref}[1]{\ref{fig:#1}}
+\newcommand{\Fig}[1]{\figurename~\figref{#1}}
+\newcommand{\fig}[1]{\Fig{#1}}
+\newcommand{\figlabel}[1]{\label{fig:#1}}
+\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
+\newcommand{\tab}[1]{\Tab{#1}}
+\newcommand{\tablabel}[1]{\label{tab:#1}}
+\newcommand{\Eq}[1]{Equation~(\ref{eq:#1})}
+\newcommand{\eq}[1]{\Eq{#1}}
+\newcommand{\eqalt}[1]{Equation~\ref{eq:#1}}
+\newcommand{\eqlabel}[1]{\label{eq:#1}}
+\newcommand{\sectionname}{Section}
+\newcommand{\Sect}[1]{\sectionname~\ref{sect:#1}}
+\newcommand{\sect}[1]{\Sect{#1}}
+\newcommand{\sectalt}[1]{\ref{sect:#1}}
+\newcommand{\App}[1]{Appendix~\ref{sect:#1}}
+\newcommand{\app}[1]{\App{#1}}
+\newcommand{\sectlabel}[1]{\label{sect:#1}}
 
@@
 \section{Methods}
-\label{sec:methods}
+\sectlabel{methods}
 
@@
   \citetalias{Morton:2012}]{Morton:2012} to \ncalc\ KOIs (see
-\autoref{sec:data} for details).  While we refer the reader to
+\sect{data} for details).  While we refer the reader to
 \citetalias{Morton:2012} for a detailed description of the method, we
@@
 \subsection{False Positive Probabilities}
-\label{sec:methods:fpp}
+\sectlabel{methods:fpp}
 
@@
 \begin{equation}
-  \label{eq:prob}
+  \eqlabel{prob}
   \mathrm{Pr}\left(H_i\right) = \frac{\pi_i \mathcal
@@
 \begin{equation}
-  \label{eq:lhood}
+  \eqlabel{lhood}
   \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
@@
 the target star are folded into the population simulations of each
-hypothesis (see \autoref{sec:methods:stellar}).  All other constraints are
+hypothesis (see \sect{methods:stellar}).  All other constraints are
 applied to narrow down which simulated instances of each scenario may
@@
   being considered (conditioned on available observations of the
-  target star; see \autoref{sec:methods:stellar}).
+  target star; see \sect{methods:stellar}).
 \item Fit each simulated eclipse in each scenario with a trapezoid
@@
 \subsection{Stellar Properties}
-\label{sec:methods:stellar}
+\sectlabel{methods:stellar}
 
@@
 gravity), they are assumed to relate to only the primary star.  Priors
-used in these fits are listed in \autoref{table:priors}---notably, we
+used in these fits are listed in \tab{priors}---notably, we
 use a prior on [Fe/H] based on a double-Gaussian fit to the local
@@
 \tablecaption{Priors used in stellar property fits
-\label{table:priors}}
+\tablabel{priors}}
 \tablehead{
@@
 \section{Data and Constraints}
-\label{sec:data}
+\sectlabel{data}
 
@@
 \section{Results}
-\label{sec:results}
+\sectlabel{results}
 
 The results of the \vespa\ calculations are presented in
-\autoref{table:stars} and \autoref{table:fpp}, and are discussed in
+\tab{stars} and \tab{fpp}, and are discussed in
 the following subsections.
@@
 \subsection{Stellar Properties}
-\label{sec:results:stars}
+\sectlabel{results:stars}
 
-As discussed in \autoref{sec:methods:stellar}, \vespa\ fits for stellar
+As discussed in \sect{methods:stellar}, \vespa\ fits for stellar
 properties as part of its FPP--calculating procedure, using the
@@
 calculation, a result of general interest independent of FPP.
-\autoref{table:stars} presents summarized results of the single--star
+\tab{stars} presents summarized results of the single--star
 fits.  While \vespa\ also fits double-- and triple--star models for
@@
 
-\autoref{fig:starsteff} and \autoref{fig:starsfehradius} compare the
-estimated effective temperatures, metallicities, and radii, derived
-here to those independently determined for the official
-\kepler\ stellar properties catalog \citep[][hereafter
+\fig{starsteff} and \fig{starsfehradius} compare the estimated
+effective temperatures, metallicities, and radii, derived here to
+those independently determined for the official \kepler\ stellar
+properties catalog \citep[][hereafter
   \citetalias{Huber:2014}]{Huber:2014}.  While there is largely
-general agreement, there are also discrepancies, highlighting the
+general agreement, there are also some discrepancies, highlighting the
 difficulty of estimating physical stellar properties.
@@
 list as $T_{\rm eff} < 4000$\,K, \isochrones\ predicts systematically
-hotter temperatures.  Most of the \citetalias{Huber:2014} properties
+hotter temperatures.  Many of the \citetalias{Huber:2014} properties
 for these stars are taken from
 \citet[][\citetalias{Dressing:2013}]{Dressing:2013}.  Those properties
-were determined by trying to match the colors of each star to the colors
+were determined by trying to match the $grizJHK$ photometry
 of a grid of model stars from the Dartmouth models, supplemented by
@@
 relation between mass and absolute $K$-band magnitude.  While they
-find general good agreement, the \citetalias{Dressing:2013} masses are
-noted to be on average about 5\% lower than the Delfosse-predicted masses.
+find general good agreement, \citetalias{Dressing:2013} does note that
+their masses are on average about 5\% lower than the Delfosse-predicted
+masses.  Our estimated masses for these stars are typically
+$\sim$10-15\% higher than those estimated by \citetalias{Dressing:2013}.
+
+The same data ($grizJHK$ photometry) and the same stellar models
+(Dartmouth) were used for both this work and
+\citetalias{Dressing:2013}, raising the question of the origin of the
+systematic differences between these methods.  The primary origin of
+this discrepancy appears to be the fact that \isochrones\ is doing a
+full multi-modal posterior exploration of the stellar parameter space,
+marginalizing over the unknown $A_V$ extinction in the process, while
+\citetalias{Dressing:2013} uses rather a fixed 1\,mag of $V$-band
+extinction per 1000\,pc extinction and selects the maximum-likelihood
+match to the grid of models.  As we allow for a maximum extinction up
+to the measured $A_V$ extinction at infinity, not explicitly dependent
+on distance, this typically allows for slightly hotter stars with
+slightly more extinction than was permitted by \citet{Dressing:2013}.
+
+The other significant discrepancy between the \isochrones\ results and
+\citetalias{Huber:2014} is among evolved stars, as seen in the lower
+panel of \fig{starsfehradius}.  Many of these stars have densities
+measured via asteroseismology, and \isochrones\ does not unambiguously
+identify all of them as evolved.  However, it should be noted that we
+do in fact identify over half of them as probably significantly
+evolved---this is made possible by the multi-modal posterior sampling
+of \texttt{MultiNest} used by \isochrones.  In addition, as the middle
+panel of \fig{starsfehradius} shows, even for stars not positively
+identified as evolved by \citetalias{Huber:2014}, isochrones often
+allows for a significant range of stellar radius---also desirable
+behavior, as \citetalias{Huber:2014} estimates the properties for many
+of these using only broad-band photometry as well, which means their
+true nature is not securely known.  The need for caution when
+estimating the radii of KOI host stars has also been emphasized by
+\citetalias{Bastien:2014}, who find from photometric ``flicker''
+measurements that a significant number of FGK KOI hosts may be
+slightly evolved.
+
+We emphasize that stellar parameter estimation is not the central goal
+of this work, nor are the FPP results very sensitive to the exact
+estimated stellar properties.  The exception to this would be if the
+stellar density estimate is significantly mis-estimated, which would
+the case if a star is not properly identified as evolved.  However, we
+note that of the 743 KOIs with host stars $>$2\,$\R_\odot$ at the
+NExScI Archive, 515 of them already have FALSE POSITIVE designations.
+Additionally, \citet{Sliski:2014} find a large false positive rate for
+KOIs with evolved host stars.  Given all of these considerations, we
+believe that potential systematic issues with stellar property
+determinations in various corners of parameter space do not affect the
+main results, which are the false positive probabilities.
 
@@
   coolest and hottest stars.
-\label{fig:starsteff}}
+\figlabel{starsteff}}
 \end{figure*}
@@
   \isochrones\ calculations are driven by the use of the local
-  metallicity prior \citep[][\autoref{table:priors}]{Hayden:2015,
+  metallicity prior \citep[][\tab{priors}]{Hayden:2015,
     Casagrande:2011}.
-\label{fig:starsfehradius}}
+\figlabel{starsfehradius}}
 \end{figure*}
@@
 \subsection{False Positive Probabilities}
-\label{sec:results:fpp}
+\sectlabel{results:fpp}
 
@@
 result of a KOI no longer being ``of interest,'' despite still
-being listed in the cumulative table.  \autoref{sec:failures} contains
+being listed in the cumulative table.  \sect{failures} contains
 detailed explanations of the different failure modes.
@@
 \subsection{Failure Modes}
-\label{sec:failures}
+\sectlabel{failures}
 
@@
 \section{Conclusions}
-\label{sec:conclusions}
+\sectlabel{conclusions}
 

### 2015-08-21 ms.tex
typo
paper-writing

@@
 \newcommand{\ntotal}{8826}
-\newcommand{\nfail}{1584}
-\newcommand{\ncalc}{7242}
+\newcommand{\nfail}{787}
+\newcommand{\ncalc}{8039}
 \newcommand{\nval}{1500}
@@
 \newcommand{\nfpnew}{200}
-\newcommand{\nbadphot}{1009} %EmptyPhotometry or MissingKOI
-\newcommand{\nbadphotFP}{897}
-\newcommand{\nbadphotCAND}{111}
-\newcommand{\nbadrowemcmc}{210}
-\newcommand{\nbadstellar}{80} %MissingStellar
-\newcommand{\nbadsec}{82} %NoWeakSecondary
-\newcommand{\nattempted}{7317}
-\newcommand{\ntryfail}{75}
+\newcommand{\nbadphot}{47} %EmptyPhotometry or MissingKOI
+\newcommand{\nbadphotFP}{34}
+\newcommand{\nbadphotCAND}{13}
+\newcommand{\nbadrowemcmc}{216}
+\newcommand{\nbadstellar}{98} %MissingStellar
+\newcommand{\nbadsec}{162} %NoWeakSecondary
+\newcommand{\nattempted}{8141}
+\newcommand{\ntryfail}{112}
+\newcommand{\nbadtrapfit}{32}
+\newcommand{\nbadroche}{52}
+\newcommand{\nbadother}{28}
+\newcommand{\nbadotherFP}{22}
+\newcommand{\nbadotherCAND}{5}
+\newcommand{\nbadotherCONF}{1}
+
 \newcommand{\kepler}{\textit{Kepler}}
@@
 \enddata
-%\tablenotetext{a}{The age range for the Dartmouth stellar model grids used.}
-%\tablenotetext{b}{Double-Gaussian fit to measured local stellar
-%  metallicity distribution \citep{Hayden:2015, Casagrande:2011}.}
-%\tablenotetext{3}{Maximum allowed value is the Galactic extinction at
-%  infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
+\tablenotetext{a}{The age range for the Dartmouth stellar model grids used.}
+\tablenotetext{b}{Double-Gaussian fit to measured local stellar
+  metallicity distribution \citep{Hayden:2015, Casagrande:2011}.}
+\tablenotetext{c}{Maximum allowed value is the Galactic extinction at
+  infinity calculated along the star's line of sight, according to \citet{Schlegel:1998}.}
 \end{deluxetable}
@@
 calculation, a result of general interest independent of FPP.
-\tab{stars} presents summarized results of the single--star
+\tab{stars} presents summarized results of these single--star
 fits.  While \vespa\ also fits double-- and triple--star models for
@@
 \fig{starsteff} and \fig{starsfehradius} compare the estimated
-effective temperatures, metallicities, and radii, derived here to
-those independently determined for the official \kepler\ stellar
-properties catalog \citep[][hereafter
+effective temperatures, metallicities, and radii derived in this work
+to those independently determined for (or compiled by) the official
+\kepler\ stellar properties catalog \citep[][hereafter
   \citetalias{Huber:2014}]{Huber:2014}.  While there is largely
-general agreement, there are also some discrepancies, highlighting the
-difficulty of estimating physical stellar properties.
+general agreement, there are also some discrepancies, highlighting some
+difficulties of estimating physical stellar properties.
 
@@
 systematic differences between these methods.  The primary origin of
-this discrepancy appears to be the fact that \isochrones\ is doing a
+this discrepancy appears to be the fact that \isochrones\ performs a
 full multi-modal posterior exploration of the stellar parameter space,
@@
 \citetalias{Dressing:2013} uses rather a fixed 1\,mag of $V$-band
-extinction per 1000\,pc extinction and selects the maximum-likelihood
+extinction per 1000\,pc and selects the maximum-likelihood
 match to the grid of models.  As we allow for a maximum extinction up
@@
 stellar density estimate is significantly mis-estimated, which would
-the case if a star is not properly identified as evolved.  However, we
-note that of the 743 KOIs with host stars $>$2\,$\R_\odot$ at the
-NExScI Archive, 515 of them already have FALSE POSITIVE designations.
-Additionally, \citet{Sliski:2014} find a large false positive rate for
+be the case if a star is not properly identified as evolved.  However, we
+note that of the 743 KOIs with host stars $>$2\,$R_{\odot}$ at the 
+NExScI Archive, 515 of them already have FALSE POSITIVE designations;
+additionally, \citet{Sliski:2014} find a large false positive rate for
 KOIs with evolved host stars.  Given all of these considerations, we
@@
 table at the NExScI Exoplanet Archive, \vespa\ successfully
-calculated the FPP for \ncalc.  Most of the \nfail\ failures are a
+calculated the FPP for \ncalc.  Many of the \nfail\ failures are a
 result of a KOI no longer being ``of interest,'' despite still
@@
 
-Of the \ntotal\ total KOIs, \nbadphot\ did not receive MCMC
-modeling.  Most of these (\nbadphotFP) are already designated FALSE
-POSITIVE at the archive, though \nbadphotCAND\ have CANDIDATE
-disposition.  One, K00245.04, is a confirmed planet.  \tdmtodo{Find
-  out why??}  An additional \nbadrowemcmc\ did receive MCMC
-modeling but had unphysical fit results; e.g., negative $R_p/R_\star$
-or best-fit impact parameter greater than $(1 + R_p/R_\star)$.  Of the
-KOIs that did have usable MCMC fits, \nbadsec\ had no
-\verb|koi_depth_err1| value on the archive, and thus had no weak
-secondary constraint and were left out of the calculations.
+We were not able to successfully run \vespa\ on \nfail\ of the
+\ntotal\ total KOIs. The various reasons for these failures are
+detailed below.  
+\begin{enumerate}
+\item \nbadphot\ KOIs did not receive MCMC modeling.  Most of these
+  (\nbadphotFP) are already designated FALSE POSITIVE at the archive,
+  though \nbadphotCAND\ have CANDIDATE disposition.
+\item \nbadrowemcmc\ KOIs did receive MCMC modeling but had unphysical fit
+  results; e.g., negative $R_p/R_\star$ or best-fit impact parameter
+  greater than $(1 + R_p/R_\star)$.
+\item The host stars of \nbadstellar\ KOIs are not included in the
+  \citetalias{Huber:2014} stellar property catalog, and thus were not
+  included in this analysis.
+\item \nbadsec\ KOIs have no \verb|koi_depth_err1| value on the archive,
+  and thus had no weak secondary constraint and were left out of the
+  calculations.
+\item For \nbadtrapfit\ KOIs, the trapezoid MCMC fit did not converge.  The
+  convergence criterion was for the autocorrelation time of the chain
+  for each parameter to be shorter than 10\% of the total chain
+  length.
+\item For \nbadroche\ KOIs, the period of the planet was such that its
+  orbit was implied to be within its host star's Roche limit.  This
+  usually happens when the host star is estimated to be a giant, and
+  these situations are nearly always false positives. 
+\item Finally, \nbadother\ KOIs failed for as-yet undetermined
+  reasons.  \nbadotherFP\ of these are already designated FALSE
+  POSITIVE, \nbadotherCAND\ are CANDIDATE, and \nbadotherCONF\ is
+  dispositioned as a confirmed planet.
+\end{enumerate}
+The numbers in this list correspond to the numbers listed in
+the ``failure'' column in \tab{fpp} for those KOIs without values in
+the ``FPP'' column.
 

### 2015-08-24 ms.tex
edits

@@
 \newcommand{\ncalc}{8039}
-\newcommand{\nval}{1500}
+
 \newcommand{\nvalnew}{1000}
@@
 \newcommand{\nbadotherCONF}{1}
+
+\newcommand{\nreliable}{2854}
+\newcommand{\nval}{2136}
+\newcommand{\nreliableFP}{298}
 
@@
 
-Of the \ntotal\ KOIs in the cumulative
-table at the NExScI Exoplanet Archive, \vespa\ successfully
-calculated the FPP for \ncalc.  Many of the \nfail\ failures are a
-result of a KOI no longer being ``of interest,'' despite still
-being listed in the cumulative table.  \sect{failures} contains
-detailed explanations of the different failure modes.
+Of the \ntotal\ KOIs in the cumulative table at the NExScI Exoplanet
+Archive, \vespa\ successfully calculated the FPP for \ncalc.  These
+results are listed in \tab{fpp};  \sect{failures} contains detailed
+explanations of the different failure modes.
+
+The first thing to note about these results is that they should not
+all be taken at face value.  For example, many KOIs have already been
+identified as false positives, and designated
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
+\end{center}
+\caption{False positive probabilities of all KOIs for which we
+  consider the \vespa\ calculations to be reliable.  This includes
+  KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
+  archive, are considered to be reliably located on the target star ($
+  {\rm Pr} > 0.99$) according to pixel-level analysis
+  \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
+  indicating that the hypotheses tested by \vespa\ are not all poor
+  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
+  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
+  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
+  \citet{Fressin:2013} \emph{a priori} estimates of the overall
+  \kepler\ candidate false positive rate.
+
+\figlabel{fppall}}
+\end{figure*}
 

### 2015-08-24 ms.tex
FP section edits

@@
 
+In order to properly interpret these results, it is necessary to
+understand the range of applicability of the \vespa\ calculation.
+First of all, this method selects between different \emph{eclipse
+  configuration} explanations for the transit-like signal, and cannot
+comment on whether the signal might be caused by stellar variability
+or an instrumental false alarm.  Thus, \vespa\ results on low
+signal-to-noise candidates where it is not clear whether the
+identified signal is truly transit-like or not must be viewed with
+caution.
+
+Another important constraint used in the FPP calculation is the
+allowed sky area inside which a blended false positive may live.  As
+described in \sect{data}, this value is taken to be three times the
+uncertainty on the fitted centroid position from the pixel-level data.
+However, many KOIs have already been identified to be blended binaries
+displaced from the target star.  Some of these are found by detecting
+significant centroid offsets---in these cases, treating the confusion
+radius simply as the uncertainty in the centroid position will clearly
+give a misleading result.  Other displaced false positives have been
+identified as originating from displaced stars by finding KOIs with
+matching ephemerides \citep{Coughlin:2014}, and often the ``parents''
+of these signals are outside the pixel masks, and so unable to be
+detected via the normal centroid-measuring methods.
+
+Thus there are many KOIs that have
+already been identified as false alarms (and thus dispositioned FALSE
+POSITIVE at the NExScI archive) for which \vespa\ gives a low false
+positive probability---all this means is that the planet scenario for
+those KOIs is \emph{more} probable than the other scenarios being
+considered, but
+
+from several pixels or more away, often the result of
+the point spread function (PSF) of a bright eclipsing binary star
+leaking into the aperture of a nearby target star
+\citep{Coughlin:2014}.  Most of these have been
+
+the limits of the \vespa\ method.
+
 The first thing to note about these results is that they should not
@@
 \caption{False positive probabilities of all KOIs for which we
-  consider the \vespa\ calculations to be reliable.  This includes
+  consider the \vespa\ calculations to be reliable (floored at
+  $10^{-4}$ for visualization purposes).  This includes
   KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
@@
   \kepler\ candidate false positive rate.
-
 \figlabel{fppall}}

### 2015-08-25 ms.tex
fpp section text

@@
 or an instrumental false alarm.  Thus, \vespa\ results on low
-signal-to-noise candidates where it is not clear whether the
-identified signal is truly transit-like or not must be viewed with
-caution.
+signal-to-noise ratio (SNR) candidates that are not clearly
+transit-like must be viewed with caution.
 
@@
 of these signals are outside the pixel masks, and so unable to be
-detected via the normal centroid-measuring methods.
+detected via centroid-measuring methods.  In these cases as well, the
+\vespa\ assumptions break down, and the FPP calculations will not be
+valid.
 
-Thus there are many KOIs that have
-already been identified as false alarms (and thus dispositioned FALSE
-POSITIVE at the NExScI archive) for which \vespa\ gives a low false
-positive probability---all this means is that the planet scenario for
-those KOIs is \emph{more} probable than the other scenarios being
-considered, but
+To summarize, the results presented in \tab{fpp} are
+strictly reliable only for KOIs \emph{that have already strongly
+  passed the other Kepler vetting tests.}  The first cut for this is
+the KOI disposition: FALSE POSITIVE indicates failure of one or more
+of these tests (and thus probable invalidity of the
+\vespa\ calculation).  However, because of the generally permissive
+philosophy of the \kepler\ dispositioning, not all CANDIDATE KOIs
+receive the same level of vetting.  That is, something is not
+identified as a FALSE POSITIVE \emph{unless there is positive
+  confirmation of false positive status}.  In particular, when
+pixel-level analysis fails to determine whether the signal is indeed
+coming from the target star because of low SNR, such a KOI will still
+receive CANDIDATE disposition.  Therefore, the \vespa-calculated FPP
+may be considered reliable only when a KOI is designated a CANDIDATE
+(or CONFIRMED) and has large enough SNR to enable secure positional
+determination.
 
-from several pixels or more away, often the result of
-the point spread function (PSF) of a bright eclipsing binary star
-leaking into the aperture of a nearby target star
-\citep{Coughlin:2014}.  Most of these have been
-
-the limits of the \vespa\ method.
-
-The first thing to note about these results is that they should not
-all be taken at face value.  For example, many KOIs have already been
-identified as false positives, and designated
+To enable convenience of interpretation, \tab{fpp} thus contains both
+the current KOI disposition and the results of the positional
+probability calculations of \citet{Bryson:2015}.  \fig{fppall} shows
+the calculated FPPs for all KOIs not dispositioned FALSE POSITIVE that
+have $>$99\% probability to be located on the target star (and for
+which the positional calculations are reliable; that is, having a
+``reliability score'' > 0.4).
 
@@
   consider the \vespa\ calculations to be reliable (floored at
-  $10^{-4}$ for visualization purposes).  This includes
-  KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
-  archive, are considered to be reliably located on the target star ($
-  {\rm Pr} > 0.99$) according to pixel-level analysis
+  $10^{-4}$ for visualization purposes).  This includes KOIs that are
+  not dispositioned as FALSE POSITIVE on the NExScI archive, are
+  considered to be reliably located on the target star ($ {\rm Pr} >
+  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
   \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
@@
   \citet{Fressin:2013} \emph{a priori} estimates of the overall
-  \kepler\ candidate false positive rate.
-\figlabel{fppall}}
+  \kepler\ candidate false positive rate.  \figlabel{fppall}}
 \end{figure*}

### 2015-08-25 ms.tex
kepler

@@
 We present the results of applying a fully automated transit signal
-false positive probability calculating procedure to every Kepler
+false positive probability calculating procedure to every \kepler\
 Object of Interest (KOI).

### 2015-08-27 ms.tex
paper edits and pie chart exploration

@@
 
-\newcommand{\nvalnew}{1000}
 \newcommand{\nfp}{500}
@@
 
-\newcommand{\nreliable}{2854}
-\newcommand{\nval}{2136}
-\newcommand{\nreliableFP}{298}
+\newcommand{\nreliable}{2752}
+\newcommand{\nval}{2069}
+\newcommand{\nreliableFP}{292}
+\newcommand{\nvalnew}{1368}
+\newcommand{\ncurval}{1001}
 
@@
   continuity with previous publication, we continue to call $\mathcal
-  L_i$ the ``likelihood'' for hypothesis $i$.}
+  L_i$ the ``likelihood'' for hypothesis $i$.}  The hypotheses
+currently supported by \vespa are the following: unblended eclipsing
+binary (EB), hierarchical-triple eclipsing binary (HEB),
+chance-aligned background/foreground eclipsing binary (BEB), and
+transiting planet (Pl).
 
@@
 stellar density estimate is significantly mis-estimated, which would
-be the case if a star is not properly identified as evolved.  However, we
-note that of the 743 KOIs with host stars $>$2\,$R_{\odot}$ at the 
+be the case if a star is not properly identified as evolved.  However,
+we note that of the 743 KOIs with host stars $>$2\,$R_{\odot}$ at the
 NExScI Archive, 515 of them already have FALSE POSITIVE designations;
@@
 believe that potential systematic issues with stellar property
-determinations in various corners of parameter space do not affect the
-main results, which are the false positive probabilities.
-
-\begin{figure*}[p]
-\begin{center}
-\includegraphics[width=7in]{figures/hubercompare_teff.pdf}
-\end{center}
-\caption{Comparison between effective temperatures estimated from the
-  \isochrones\ analysis in this work and those from the
-  \kepler\ stellar parameters catalog \citep[][hereafter
-    \citetalias{Huber:2014}]{Huber:2014}.  Bottom panel shows stars
-  for which \citetalias{Huber:2014} predicts $T_{\rm eff} < 4500$\,K,
-  middle spans $4500\,{\rm K} < T_{\rm eff} < 6500\,{\rm K}$, and top
-  has $T_{\rm eff} > 6500$\,K. Blue horizontal bold lines are the
-  \citetalias{Huber:2014} values in sorted order; blue shading
-  represents the error bars from \citetalias{Huber:2014}.  Vertical
-  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
-  these lines are grey if they overlap with the
-  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
-  marked by a point) if they are inconsistent.  This comparison shows
-  that the stellar parameters estimated in this work are broadly
-  consistent with \citetalias{Huber:2014}, though less so for the
-  coolest and hottest stars.
-\figlabel{starsteff}}
-\end{figure*}
-
-\begin{figure*}[p]
-\begin{center}
-\includegraphics[width=7in]{figures/hubercompare_fehradius.pdf}
-\end{center}
-\caption{Comparison between metallicities and radii estimated from the
-  \isochrones\ analysis in this work and those from the
-  \kepler\ stellar parameters catalog \citep[][hereafter
-    \citetalias{Huber:2014}]{Huber:2014}.  Top panel shows metallicity
-  for all stars in the sample.  The middle panel shows stars for which
-  \citetalias{Huber:2014} estimates $R_\star < 2\,R_\odot$, and the
-  bottom shows $R_\star > 2\,R_\odot$. Blue horizontal bold lines are
-  the \citetalias{Huber:2014} values in sorted order; blue shading
-  represents the error bars from \citetalias{Huber:2014}.  Vertical
-  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
-  these lines are grey if they overlap with the
-  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
-  marked by a point) if they are inconsistent.  This comparison shows
-  that the stellar parameters estimated in this work are broadly
-  consistent with \citetalias{Huber:2014}, though less so for the more
-  evolved stars.  The metallicity estimates of the
-  \isochrones\ calculations are driven by the use of the local
-  metallicity prior \citep[][\tab{priors}]{Hayden:2015,
-    Casagrande:2011}.
-\figlabel{starsfehradius}}
-\end{figure*}
+determinations in various corners of parameter space do not strongly
+affect the main results, which are the astrophysical false positive
+probabilities of thousands of KOIs.
 
@@
 Of the \ntotal\ KOIs in the cumulative table at the NExScI Exoplanet
-Archive, \vespa\ successfully calculated the FPP for \ncalc.  These
+Archive, \vespa\ successfully calculates the FPP for \ncalc.  These
 results are listed in \tab{fpp};  \sect{failures} contains detailed
-explanations of the different failure modes.
+explanations of the failure reasons for the other \nfail\ KOIs.
 
@@
 
+However, while the FPP value does only give the \emph{relative}
+probability between the false positive and planet scenarios, there is
+a way to get a sense of whether \emph{all} of the models might be bad
+fits to the data (and thus get a hint that perhaps the signal is due
+to stellar variability or a false alarm).  Recall that FPP is
+calculated as
+\begin{equation}
+\eqlabel{fpp}
+{\rm FPP} = \frac{\displaystyle\sum_{i \neq {\rm Pl}}
+  L_i}{\displaystyle \sum_i L_i}
+\end{equation}
+where $L_i$ = $\mathcal L_i \pi_i$ and $i$ runs over all the models,
+with ``Pl'' representing the planet scenario.  If, for example, the
+shape of the transit is such that \emph{none} of the models gives any
+kind of decent fit to its trapezoidal shape, then $L_{\rm tot} =
+\sum_i L_i$ will be very small.  It appears that a value of $10^{-3}$
+is a reasonable threshold below which to consider a particular
+calculation unreliable.  To set this threshold we inspected the
+handful of systems that have low FPPs and $L_{\rm tot} < 10^{-3}$
+(some go as low as $10^{-10}$ or lower), and find that these very
+often have unrealistically long durations for a transit signal.  Such
+a case could easily give the planet hypothesis the \emph{largest}
+likelihood (resulting in a low FPP), not because it is intrinsically
+likely, but because everything else is just much worse.
+
 Another important constraint used in the FPP calculation is the
@@
 uncertainty on the fitted centroid position from the pixel-level data.
-However, many KOIs have already been identified to be blended binaries
-displaced from the target star.  Some of these are found by detecting
-significant centroid offsets---in these cases, treating the confusion
-radius simply as the uncertainty in the centroid position will clearly
-give a misleading result.  Other displaced false positives have been
+However, many KOIs have already been identified to be blended binary
+false positives displaced from the target star.  Some of these are
+found by detecting significant centroid offsets in the pixel-level
+data---in these cases, \vespa\ treating the confusion radius simply as
+the uncertainty in the centroid position will clearly give a
+misleading result.  Other displaced false positives have been
 identified as originating from displaced stars by finding KOIs with
@@
 
-To summarize, the results presented in \tab{fpp} are
-strictly reliable only for KOIs \emph{that have already strongly
-  passed the other Kepler vetting tests.}  The first cut for this is
-the KOI disposition: FALSE POSITIVE indicates failure of one or more
-of these tests (and thus probable invalidity of the
-\vespa\ calculation).  However, because of the generally permissive
-philosophy of the \kepler\ dispositioning, not all CANDIDATE KOIs
-receive the same level of vetting.  That is, something is not
-identified as a FALSE POSITIVE \emph{unless there is positive
-  confirmation of false positive status}.  In particular, when
-pixel-level analysis fails to determine whether the signal is indeed
-coming from the target star because of low SNR, such a KOI will still
-receive CANDIDATE disposition.  Therefore, the \vespa-calculated FPP
-may be considered reliable only when a KOI is designated a CANDIDATE
-(or CONFIRMED) and has large enough SNR to enable secure positional
-determination.
+To summarize, the results presented in \tab{fpp} are strictly reliable
+only for KOIs \emph{that have already strongly passed the other Kepler
+  vetting tests, and that are not indicated to be clearly poor fits to
+  all the proposed hypotheses}.  The first cut for this is the KOI
+disposition: FALSE POSITIVE indicates failure of one or more of these
+tests (and thus probable invalidity of the \vespa\ calculation).
+However, because of the generally permissive philosophy of the
+\kepler\ dispositioning, not all CANDIDATE KOIs receive the same level
+of vetting.  That is, something is not identified as a FALSE POSITIVE
+\emph{unless there is positive confirmation of false positive status}.
+In particular, when pixel-level analysis fails to determine whether
+the signal is indeed coming from the target star because of low SNR,
+such a KOI will still receive CANDIDATE disposition.  Therefore, the
+\vespa-calculated FPP may be considered most reliable only when a KOI
+is designated a CANDIDATE (or CONFIRMED) and has large enough SNR to
+enable secure positional determination.
 
-To enable convenience of interpretation, \tab{fpp} thus contains both
-the current KOI disposition and the results of the positional
-probability calculations of \citet{Bryson:2015}.  \fig{fppall} shows
-the calculated FPPs for all KOIs not dispositioned FALSE POSITIVE that
-have $>$99\% probability to be located on the target star (and for
-which the positional calculations are reliable; that is, having a
-``reliability score'' > 0.4).
+To enable interpretation, \tab{fpp} thus contains both the current KOI
+disposition and the results of the positional probability calculations
+of \citet{Bryson:2015}.  \Fig{fppall} shows FPPs for all KOIs passing
+the following criteria:
+\begin{itemize}
+\item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive
+\item $> 0.99$ probability to be on the target star, according
+  to \citet{Bryson:2015}, along with a positional probability
+  ``score'' $> 0.4$ (indicating a reliable result).
+\item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
+  poor fits to the transit signal.
+\end{itemize}
 
-\begin{figure*}[p]
-\begin{center}
-\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
-\end{center}
-\caption{False positive probabilities of all KOIs for which we
-  consider the \vespa\ calculations to be reliable (floored at
-  $10^{-4}$ for visualization purposes).  This includes KOIs that are
-  not dispositioned as FALSE POSITIVE on the NExScI archive, are
-  considered to be reliably located on the target star ($ {\rm Pr} >
-  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
-  \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
-  indicating that the hypotheses tested by \vespa\ are not all poor
-  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
-  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
-  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
-  \citet{Fressin:2013} \emph{a priori} estimates of the overall
-  \kepler\ candidate false positive rate.  \figlabel{fppall}}
-\end{figure*}
+These selections leave \nreliable\ KOIs for which the \vespa\ results
+can be considered most reliable.  Of these, \nval\ have ${\rm FPP} <
+0.01$, and are thus validated at the 99\% level.
 
@@
 
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/hubercompare_teff.pdf}
+\end{center}
+\caption{Comparison between effective temperatures estimated from the
+  \isochrones\ analysis in this work and those from the
+  \kepler\ stellar parameters catalog \citep[][hereafter
+    \citetalias{Huber:2014}]{Huber:2014}.  Bottom panel shows stars
+  for which \citetalias{Huber:2014} predicts $T_{\rm eff} < 4500$\,K,
+  middle spans $4500\,{\rm K} < T_{\rm eff} < 6500\,{\rm K}$, and top
+  has $T_{\rm eff} > 6500$\,K. Blue horizontal bold lines are the
+  \citetalias{Huber:2014} values in sorted order; blue shading
+  represents the error bars from \citetalias{Huber:2014}.  Vertical
+  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
+  these lines are grey if they overlap with the
+  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
+  marked by a point) if they are inconsistent.  This comparison shows
+  that the stellar parameters estimated in this work are broadly
+  consistent with \citetalias{Huber:2014}, though less so for the
+  coolest and hottest stars.
+\figlabel{starsteff}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/hubercompare_fehradius.pdf}
+\end{center}
+\caption{Comparison between metallicities and radii estimated from the
+  \isochrones\ analysis in this work and those from the
+  \kepler\ stellar parameters catalog \citep[][hereafter
+    \citetalias{Huber:2014}]{Huber:2014}.  Top panel shows metallicity
+  for all stars in the sample.  The middle panel shows stars for which
+  \citetalias{Huber:2014} estimates $R_\star < 2\,R_\odot$, and the
+  bottom shows $R_\star > 2\,R_\odot$. Blue horizontal bold lines are
+  the \citetalias{Huber:2014} values in sorted order; blue shading
+  represents the error bars from \citetalias{Huber:2014}.  Vertical
+  lines span the 1$\sigma$ credible region of the \isochrones\ fits;
+  these lines are grey if they overlap with the
+  \citetalias{Huber:2014} 1$\sigma$ region and red (with the median
+  marked by a point) if they are inconsistent.  This comparison shows
+  that the stellar parameters estimated in this work are broadly
+  consistent with \citetalias{Huber:2014}, though less so for the more
+  evolved stars.  The metallicity estimates of the
+  \isochrones\ calculations are driven by the use of the local
+  metallicity prior \citep[][\tab{priors}]{Hayden:2015,
+    Casagrande:2011}.
+\figlabel{starsfehradius}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
+\end{center}
+\caption{False positive probabilities of all KOIs for which we
+  consider the \vespa\ calculations to be reliable (floored at
+  $10^{-4}$ for visualization purposes).  This includes KOIs that are
+  not dispositioned as FALSE POSITIVE on the NExScI archive, are
+  considered to be reliably located on the target star ($ {\rm Pr} >
+  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
+  \citep{Bryson:2015}, and for which $L_{\rm tot} > 10^{-3}$,
+  indicating that the hypotheses tested by \vespa\ are not all poor
+  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
+  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
+  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
+  \citet{Fressin:2013} \emph{a priori} estimates of the overall
+  \kepler\ candidate false positive rate.  \figlabel{fppall}}
+\end{figure*}
+
 %\capstartfalse

### 2015-08-27 ms.tex
added pie chart; more text edits

@@
 \newcommand{\nfp}{500}
-\newcommand{\nfpnew}{200}
+
 \newcommand{\nbadphot}{47} %EmptyPhotometry or MissingKOI
@@
 \newcommand{\nreliableFP}{292}
-\newcommand{\nvalnew}{1368}
+\newcommand{\nvalnew}{1396}
+\newcommand{\nfpnew}{192}
 \newcommand{\ncurval}{1001}
@@
 We present the results of applying a fully automated transit signal
-false positive probability calculating procedure to every \kepler\
-Object of Interest (KOI).
-Out of \ncalc\ KOIs, we determine that \nval\ have probabilities
-$<$1\% to be astrophysical false positives, and thus may be considered
-validated planets.  \nvalnew\ of these have not yet been validated or
-confirmed by other methods.  In addition, we identify \nfp\ KOIs
-likely to be false positives ($>$90\% probability), \nfpnew\ of which
-have not yet been identified as such. A side product of these
-calculations is full stellar property posterior samplings for every
-host star, modeled as single, binary, and triple systems.  These
-calculations use \vespa, a publicly available Python package able to
-be easily applied to any transiting exoplanet candidate.
+false positive probability calculating procedure to every
+\kepler\ Object of Interest (KOI).  Out of \ncalc\ KOIs, we determine
+that \nval\ have probabilities $<$1\% to be astrophysical false
+positives, and thus may be considered validated planets.  \nvalnew\ of
+these have not yet been validated or confirmed by other methods.  In
+addition, we identify \nfpnew\ KOIs likely to be false positives
+($>$90\% \nfpnew) that have not yet been identified as such. A side
+product of these calculations is full stellar property posterior
+samplings for every host star, modeled as single, binary, and triple
+systems.  These calculations use \vespa, a publicly available Python
+package able to be easily applied to any transiting exoplanet
+candidate.
 \end{abstract}
@@
 
-In this work, we apply the fully automated FPP-computing
-procedure described in \citet[][hereafter
-  \citetalias{Morton:2012}]{Morton:2012} to \ncalc\ KOIs (see
-\sect{data} for details).  While we refer the reader to
-\citetalias{Morton:2012} for a detailed description of the method, we
-outline it briefly in this section.  The procedure as implemented here
-is now publicly available in the Python module
+In this work, we apply the fully automated FPP-computing procedure
+described in \citet[][hereafter \citetalias{Morton:2012}]{Morton:2012}
+to \ncalc\ KOIs (see \sect{data} for details).  While we refer the
+reader to \citetalias{Morton:2012} for a detailed description of the
+method, we outline it briefly in this section.  The procedure as
+implemented here is publicly available in the Python module
 \vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
@@
 
-\vespa\ models an eclipse signal as a simple trapezoid, parametrized
-by depth $\delta$, total duration $T$, and shape parameter $T / \tau$,
-where $\tau$ is the ``ingress/egress'' duration (such that a
-completely V-shaped transit has $T/\tau = 2$).  For the transit signal
-being evaluated, the joint posterior probability density function
-(PDF) of these shape parameters is sampled with Markov Chain Monte
-Carlo (MCMC), using the
-\texttt{emcee} sampler \citep{emcee}.  This allows the likelihood for
-each hypothesis to be determined by simulating a physically realistic
-population of the hypothesized astrophysical scenario and using this
-population to define the PDF for the trapezoidal parameters under the
-hypothesis.  The likelihood is then
+The \vespa\ procedure models an eclipse signal as a simple trapezoid,
+parametrized by depth $\delta$, total duration $T$, and shape
+parameter $T / \tau$, where $\tau$ is the ``ingress/egress'' duration
+(such that a completely V-shaped transit has $T/\tau = 2$).  For the
+transit signal being evaluated, the joint posterior probability
+density function (PDF) of these shape parameters is sampled with
+Markov Chain Monte Carlo (MCMC), using the \texttt{emcee} sampler
+\citep{emcee}.  This allows the likelihood for each hypothesis to be
+determined by simulating a physically realistic population of the
+hypothesized astrophysical scenario and using this population to
+define the PDF for the trapezoidal parameters under the hypothesis.
+The likelihood is then
 \begin{equation}
@@
   $\bvec{\theta}$ parameter space.  But for clarity, and for
-  continuity with previous publication, we continue to call $\mathcal
+  continuity with previous publications, we continue to call $\mathcal
   L_i$ the ``likelihood'' for hypothesis $i$.}  The hypotheses
-currently supported by \vespa are the following: unblended eclipsing
+currently supported by \vespa\ are the following: unblended eclipsing
 binary (EB), hierarchical-triple eclipsing binary (HEB),
@@
 \begin{enumerate}
-\item Fit trapezoid model to observed transit signal using MCMC.
+\item Generate posterior samples for the transit signal under the
+  trapezoid model, using MCMC.
 \item Generate population simulations for each hypothesis scenario
@@
 \item Evaluate priors and likelihoods for each hypothesis, taking into
-  account all available observational constraints, in order to
-  calculate the FPP.
+  account all available observational constraints.
+\item Use \eq{prob} to calculate the posterior probability for each scenario.
 \end{enumerate}
@@
 randomly generating stars (or binary or triple systems of stars) from
-a predefined distribution and culling them to agree with observed
-colors, \emph{all} available constraints on the target star are used
-to condition a direct fit of either a single--, binary--, or
+a predefined distribution and culling them to approximately agree with
+observed colors, \emph{all} available constraints on the target star
+are used to condition a direct fit of either a single--, binary--, or
 triple--star model to the Dartmouth grid of stellar models
@@
 \end{enumerate}
+As explained in the \vespa\ documentation, we first specify this
+ancillary data in a \verb|star.ini| and \verb|fpp.ini| file for each
+KOI, and then for each we run the command-line script \verb|calcfpp|.
+This end-to-end calculation (which includes the \isochrones\ fits for
+single-, double-, and triple-star models) takes approximately 30
+minutes per KOI on a single core, allowing the entire set to be
+calculated in approximately one day on the Princeton Univeristy
+``Tigress'' computing cluster, using 200 cores.
 
@@
 match to the grid of models.  As we allow for a maximum extinction up
-to the measured $A_V$ extinction at infinity, not explicitly dependent
-on distance, this typically allows for slightly hotter stars with
+to the measured $A_V$ extinction at infinity, not explicitly tied to
+distance, this typically allows for slightly hotter stars with
 slightly more extinction than was permitted by \citet{Dressing:2013}.
@@
 likelihood (resulting in a low FPP), not because it is intrinsically
-likely, but because everything else is just much worse.
+likely, but because all the other scenarios are even less likely.
 
@@
 identified as originating from displaced stars by finding KOIs with
-matching ephemerides \citep{Coughlin:2014}, and often the ``parents''
-of these signals are outside the pixel masks, and so unable to be
-detected via centroid-measuring methods.  In these cases as well, the
-\vespa\ assumptions break down, and the FPP calculations will not be
-valid.
+matching periods and epochs \citep{Coughlin:2014}, and often the
+``parents'' of these signals are outside the pixel masks, and so
+unable to be detected via centroid-measuring methods.  In these cases
+as well, the \vespa\ assumptions break down, and the FPP calculations
+will not be valid.
 
@@
 \begin{itemize}
-\item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive
+\item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive,
 \item $> 0.99$ probability to be on the target star, according
   to \citet{Bryson:2015}, along with a positional probability
-  ``score'' $> 0.4$ (indicating a reliable result).
+  ``score'' $> 0.4$ (indicating a reliable result), and   
 \item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
@@
 can be considered most reliable.  Of these, \nval\ have ${\rm FPP} <
-0.01$, and are thus validated at the 99\% level.
+0.01$, and are thus validated at the 99\% level.  These are not all
+new validations, however, since a number of these are already
+CONFIRMED.  \Fig{fpppie} shows a different kind of summary, setting
+aside those with CONFIRMED and FALSE POSITIVE dispositions and
+splitting up the CANDIDATES according to the \vespa\ results, showing
+that \nvalnew\ KOIs are newly validated at the 99\% level.
 
@@
 \end{enumerate}
-The numbers in this list correspond to the numbers listed in
-the ``failure'' column in \tab{fpp} for those KOIs without values in
-the ``FPP'' column.
+The numbers in this list correspond to the numbers in
+the ``failure'' column in \tab{fpp}.
 
@@
 \end{center}
-\caption{False positive probabilities of all KOIs for which we
-  consider the \vespa\ calculations to be reliable (floored at
-  $10^{-4}$ for visualization purposes).  This includes KOIs that are
-  not dispositioned as FALSE POSITIVE on the NExScI archive, are
+\caption{False positive probabilities of all CANDIDATE or CONFIRMED
+  KOIs for which we consider the \vespa\ calculations to be reliable
+  (floored at $10^{-4}$ for visualization purposes), meaning they are
   considered to be reliably located on the target star ($ {\rm Pr} >
   0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
-  \citep{Bryson:2015}, and for which $L_{\rm tot} > 10^{-3}$,
-  indicating that the hypotheses tested by \vespa\ are not all poor
-  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
-  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
-  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
-  \citet{Fressin:2013} \emph{a priori} estimates of the overall
-  \kepler\ candidate false positive rate.  \figlabel{fppall}}
+  \citep{Bryson:2015}, and have $L_{\rm tot} > 10^{-3}$, indicating
+  that the hypotheses tested by \vespa\ are not all poor explanations
+  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
+  \nval\ have FPPs less than 1\%.  Noteably, \nreliableFP\ are likely
+  false positives (FPP $> 0.5$), consistent with the
+  \citet{Morton:2011} and \citet{Fressin:2013} \emph{a priori}
+  estimates of the overall \kepler\ candidate false positive rate.
+  \figlabel{fppall}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/fpp_pie.pdf}
+\end{center}
+\caption{A summary of how the the calculations presented in this paper
+  advance our understanding of the true nature of KOIs.  More than
+  half of all KOIs to date have already been dispositioned FALSE
+  POSITIVE or CONFIRMED.  Those dispositioned CANDIDATE we further
+  categorize according to their reliability.  The ``no reliable
+  calculation'' category means that either the \vespa\ calculation was
+  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
+  probability uncertain'' indicates that the positional probability
+  calculations of \citet{Bryson:2015} are not reliable (score $<
+  0.4$).  ``On-target probability $<$ 0.99'' means that the positional
+  probability calculations indicate that there is a non-negligible
+  chance that the source of the transit signal is not at the position
+  of the KOI.  The remaining three categories are all CANDIDATE KOIs
+  with reliable calculations, grouped by false positive probability.
+  \nvalnew\ of these are new planet validations, and \nfpnew\ are new
+  likely false positives.  \figlabel{fpppie}}
 \end{figure*}

### 2015-08-31 ms.tex
work on a new plot
more edits

@@
 new validations, however, since a number of these are already
-CONFIRMED.  \Fig{fpppie} shows a different kind of summary, setting
-aside those with CONFIRMED and FALSE POSITIVE dispositions and
-splitting up the CANDIDATES according to the \vespa\ results, showing
-that \nvalnew\ KOIs are newly validated at the 99\% level.
+CONFIRMED.  \Fig{fpppie} shows a different kind of summary, grouping
+KOIs by disposition and splitting up the CANDIDATES according to the
+\vespa\ results, showing that \nvalnew\ KOIs are newly validated at
+the 99\% level.  \Fig{rpcand} shows the radii and periods of the
+CANDIDATE KOIs, grouped by FPP.
 
@@
 
-%\acrodef{fpp}[FPP]{false positive probability}
-%\acrodef{koi}[KOI]{\kepler\ Object of Interest}
-%\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
-%\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
-%\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
-%\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
-%\acrodef{kic}[KIC]{Kepler Input Catalog}
-%\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
-%\acrodef{ttv}[TTV]{transit timing variations}
+In this work, we have calculated the astrophysical false positive
+probability (FPP) for every \kepler\ object of interest (KOI), using
+the publicly available Python module \vespa.  While the assumptions
+behind this calculation are not necessarily valid for every KOI (see
+\sect{results:fpp}, we have identified \nvalnew\ KOIs that have
+reliable FPPs of $< 0.01$, resulting in validation of their planetary
+nature at the 99\% confidence level.  The reliability of these
+calculations is dependent largely on the results of \citet{Bryson:2015},
+which quantify the probability that the eclipse/transit signal is
+spatially coincident on the sky with the presumed target star.
+
+These batch FPP calculations will
+
+The \kepler\ mission has demonstrated that space-based transiting
+planet surveys can identify viable planet candidates at a rate much
+faster than traditional follow-up techniques can confirm them.  As a
+result, probabilistic validation techniques are now
 
@@
   of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
-  \nval\ have FPPs less than 1\%.  Noteably, \nreliableFP\ are likely
+  \nval\ have FPPs less than 1\% (\nvalnew\ of which have not yet been
+  dispositioned as CONFIRMED).  Noteably, \nreliableFP\ are likely
   false positives (FPP $> 0.5$), consistent with the
@@
   of the KOI.  The remaining three categories are all CANDIDATE KOIs
-  with reliable calculations, grouped by false positive probability.
-  \nvalnew\ of these are new planet validations, and \nfpnew\ are new
-  likely false positives.  \figlabel{fpppie}}
+  reliably confirmed to be located at the presumed target star,
+  grouped by false positive probability.  \nvalnew\ of these are new
+  planet validations, and \nfpnew\ are new likely false positives.
+  \figlabel{fpppie}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/RP_cand.pdf}
+\end{center}
+\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
+  by FPP value.  Green circles are most likely to be planets, red X's
+  are most likely to be false positives, and blue plusses have
+  intermediate FPPs.  Grey dots are KOIs for which the
+  \vespa\ calculation is considered less reliable.  
+  \figlabel{rpcand}}
 \end{figure*}

### 2015-08-31 ms.tex
paper edits

@@
 
-\newcommand{\nreliable}{2752}
-\newcommand{\nval}{2069}
-\newcommand{\nreliableFP}{292}
-\newcommand{\nvalnew}{1396}
-\newcommand{\nfpnew}{192}
+\newcommand{\nreliable}{2854}
+\newcommand{\nval}{2136}
+\newcommand{\nreliableFP}{298}
+\newcommand{\nvalnew}{1456}
+\newcommand{\nfpnew}{195}
 \newcommand{\ncurval}{1001}
+
+\newcommand{\posprobthresh}{0.3}
 
@@
 \newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
+
+\newcommand{\dataurl}{\url{http://tigress-web.princeton.edu/~tmorton/koi-fpp/}}
 
@@
 addition, we identify \nfpnew\ KOIs likely to be false positives
-($>$90\% \nfpnew) that have not yet been identified as such. A side
+($>$90\%) that have not yet been identified as such. A side
 product of these calculations is full stellar property posterior
@@
 chance-aligned background/foreground eclipsing binary (BEB), and
-transiting planet (Pl).
+transiting planet (Pl).  We note that the determination of the diluted
+eclipse depth of these blended scenarios assumes that the blended
+system is \emph{fully contained} within the target's photometric
+aperture.  That is, these scenarios do not account for the possibility
+that only a small fraction of the light from a nearby contaminating
+star might be in the aperture, many of which have already been
+identified via other methods \cite{Bryson:2013,Coughlin:2014}.
 
@@
 disposition and the results of the positional probability calculations
-of \citet{Bryson:2015}.  \Fig{fppall} shows FPPs for all KOIs passing
+of \citet{Bryson:KSCI}.  \Fig{fppall} shows FPPs for all KOIs passing
 the following criteria:
@@
 \item $> 0.99$ probability to be on the target star, according
-  to \citet{Bryson:2015}, along with a positional probability
-  ``score'' $> 0.4$ (indicating a reliable result), and   
+  to \citet{Bryson:KSCI}, along with a positional probability
+  ``score'' $> \posprobthresh$ (indicating a reliable result), and   
 \item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
@@
 CANDIDATE KOIs, grouped by FPP.
+
+One final note about these FPP calculations is that unidentified
+transit timing variations (TTVs) will increase the FPP of a transit
+signal, as the shape of the folded light curve will be distorted,
+typically resulting in a longer signal which a trapezoid model will
+also identify as more V-shaped.  While we have analyzed light curves
+using known TTVs when available, we have also undoubtedly missed many
+systems with as-yet-unspecified TTV signals.  This means that a large
+FPP may be simply an indication of unidentified TTVs rather than
+indicative of an astrophysical false positive, especially in
+multi-planet systems, which should overall have a very low false
+positive rate.  \Tab{fpp} lists whether known TTVs were accounted for
+when constructing the folded transit light curve for each KOI.
 
@@
 behind this calculation are not necessarily valid for every KOI (see
-\sect{results:fpp}, we have identified \nvalnew\ KOIs that have
+\sect{results:fpp}), we have identified \nvalnew\ KOIs that have
 reliable FPPs of $< 0.01$, resulting in validation of their planetary
-nature at the 99\% confidence level.  The reliability of these
-calculations is dependent largely on the results of \citet{Bryson:2015},
-which quantify the probability that the eclipse/transit signal is
-spatially coincident on the sky with the presumed target star.
+nature at the 99\% confidence level, more than doubling the
+number of confirmed \kepler\ exoplanets.
 
-These batch FPP calculations will
+The reliability of these calculations is dependent largely on the
+results of \citet{Bryson:KSCI}, which quantify the probability that
+the eclipse/transit signal is spatially coincident on the sky with the
+presumed target star.  Without confirmation that the transit signal is
+not coming from a significantly displaced source, the sky area used as
+part of the prior for the false positive scenarios would need to be
+significantly larger than the positional uncertainty value assumed in
+this work (described in \sect{methods:fpp}).  Additionally, the
+blended false positive scenarios being considered are assumed to be
+fully contained within the photometric aperture; this assumption would
+also be broken if the source of the eclipse were significantly
+displaced.
+
+While previous \emph{a priori} false positive rate estimates
+\cite{Morton:2011b,Fressin:2013} have made clear that the
+\kepler\ planet candidate catalogs are \emph{generally} low enough to
+ignore for the purposes of planet occurrence rate calculations, any
+more detailed study of any small subset of individual KOIs must
+understand in more detail the FPPs of those specific candidates.  This
+type of small-sample candidate culling using individually calculated
+FPPs has already been done in the literature
+\cite{MortonSwift:2014,MortonWinn:2015}; the publication of this full
+catalog allows the community to do the same.
 
@@
   considered to be reliably located on the target star ($ {\rm Pr} >
-  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
-  \citep{Bryson:2015}, and have $L_{\rm tot} > 10^{-3}$, indicating
+  0.99$, with ``score'' $> \posprobthresh$) according to pixel-level analysis
+  \citep{Bryson:KSCI}, and have $L_{\rm tot} > 10^{-3}$, indicating
   that the hypotheses tested by \vespa\ are not all poor explanations
@@
   false positives (FPP $> 0.5$), consistent with the
-  \citet{Morton:2011} and \citet{Fressin:2013} \emph{a priori}
+  \citet{Morton:2011b} and \citet{Fressin:2013} \emph{a priori}
   estimates of the overall \kepler\ candidate false positive rate.
@@
   probability uncertain'' indicates that the positional probability
-  calculations of \citet{Bryson:2015} are not reliable (score $<
-  0.4$).  ``On-target probability $<$ 0.99'' means that the positional
+  calculations of \citet{Bryson:KSCI} are not reliable (score $<
+  \posprobthresh$).  ``On-target probability $<$ 0.99'' means that the positional
   probability calculations indicate that there is a non-negligible

### 2015-08-31 make_final_fpptable.py
added ttv flag to master table

@@ -24,7 +24,10 @@ positional_table = pd.read_csv(positional_file, index_col=0)
 star_table = pd.read_table(starprop_file, delim_whitespace=True)
 star_table.index = star_table['koi']
 
+ttv_table = pd.read_table('ttvdata.txt', index_col=0, delim_whitespace=True) 
+
 err_table = np.loadtxt('fpp_err.txt', usecols=(0,1), dtype=str)
+
 
 kois = fpp_table.index
 
@@ -42,6 +45,8 @@ fpp_table['ephem_match'] = ku.DATA.ix[kois, 'koi_fpflag_ec'].astype(bool)
 fpp_table['exception'] = None
 fpp_table.ix[err_table[:,0], 'exception'] = err_table[:,1]
 fpp_table['exception'] = fpp_table['exception'].str.replace(':','')
+
+fpp_table['has_ttv'] = ttv_table.ix[kois,'has_ttv']
 
 fpp_table.to_csv('fpp_final_table.csv')
 

### 2015-08-31 ms.tex
conclusion work

@@
 false positive probability calculating procedure to every
-\kepler\ Object of Interest (KOI).  Out of \ncalc\ KOIs, we determine
-that \nval\ have probabilities $<$1\% to be astrophysical false
-positives, and thus may be considered validated planets.  \nvalnew\ of
-these have not yet been validated or confirmed by other methods.  In
-addition, we identify \nfpnew\ KOIs likely to be false positives
-($>$90\%) that have not yet been identified as such. A side
-product of these calculations is full stellar property posterior
-samplings for every host star, modeled as single, binary, and triple
-systems.  These calculations use \vespa, a publicly available Python
-package able to be easily applied to any transiting exoplanet
-candidate.
+\kepler\ Object of Interest (KOI)---the first large-scale
+demonstration of a fully automated transiting planet validation
+procedure.  Out of \ncalc\ KOIs, we determine that \nval\ have
+probabilities $<$1\% to be astrophysical false positives, and thus may
+be considered validated planets.  \nvalnew\ of these have not yet been
+validated or confirmed by other methods.  In addition, we identify
+\nfpnew\ KOIs likely to be false positives that have not yet been
+identified as such, though some of these may be a result of
+unidentified transit timing variations. A side product of these
+calculations is full stellar property posterior samplings for every
+host star, modeled as single, binary, and triple systems.  These
+calculations use \vespa, a publicly available Python package able to
+be easily applied to any transiting exoplanet candidate.
 \end{abstract}
@@
 
-One final note about these FPP calculations is that unidentified
+One final note about these calculations is that unidentified
 transit timing variations (TTVs) will increase the FPP of a transit
@@
 multi-planet systems, which should overall have a very low false
-positive rate.  \Tab{fpp} lists whether known TTVs were accounted for
+positive rate.  \Tab{fpp} lists whether known TTV were accounted for
 when constructing the folded transit light curve for each KOI.
@@
 reliable FPPs of $< 0.01$, resulting in validation of their planetary
-nature at the 99\% confidence level, more than doubling the
-number of confirmed \kepler\ exoplanets.
+nature at the 99\% confidence level, more than doubling the number of
+confirmed \kepler\ exoplanets.  Among this set of reliable \vespa\
+calculations are also \nfpnew\ new likely false positive KOIs,
+although we note that there is a chance that some of these large FPPs
+are due to unidentified or miscorrected transit timing variations.
 
@@
 FPPs has already been done in the literature
-\cite{MortonSwift:2014,MortonWinn:2015}; the publication of this full
+\citep{MortonSwift:2014,MortonWinn:2015}; the publication of this full
 catalog allows the community to do the same.
@@
 The \kepler\ mission has demonstrated that space-based transiting
-planet surveys can identify viable planet candidates at a rate much
-faster than traditional follow-up techniques can confirm them.  As a
-result, probabilistic validation techniques are now
+planet surveys identify planet candidates at a rate much faster than
+traditional follow-up techniques can confirm them.  As a result, false
+positive probability quantification techniques are now an integral
+part of the landscape of exoplanet science.  While the present work is
+the first large-scale demonstration of a fully automated validation
+procedure, there is much progress still to be made.  For example,
+there is currently no support within \vespa\ to calculate the FPP for
+a candidate which has a \emph{specifically identified} but hitherto
+unknown close companion.  Future development plans for the
+\vespa\ package include support for this scenario, as well as other
+improvements.  One of the most important of these will be to allow for
+a contaminating EB to not be fully contained within the target
+photometric aperture; that is, modeling the probability for
+further-away stars to be EBs contributing only a small amount of their
+flux to the target photometry, such as is the case for many of the
+false positives identified via ephemeris matching by
+\citet{Coughlin:2014}.  Full inclusion of this effect will allow for
+even low-SNR candidates to receive confident \vespa\ analysis, which
+is now limited only to KOIs for which confident pixel-level positional
+analysis is possible.
 
@@
 
+\begin{turnpage}
 %\capstartfalse
@@
 %\capstarttrue
+\end{turnpage}
 

### 2015-09-01 ms.tex
added mcmc table; a few edits

@@
 \begin{abstract}
-We present the results of applying a fully automated transit signal
-false positive probability calculating procedure to every
-\kepler\ Object of Interest (KOI)---the first large-scale
+We present transit signal false positive probability calculations for
+every \kepler\ Object of Interest (KOI)---the first large-scale
 demonstration of a fully automated transiting planet validation
@@
 this work (described in \sect{methods:fpp}).  Additionally, the
-blended false positive scenarios being considered are assumed to be
+blended false positive scenarios \vespa\ considers are assumed to be
 fully contained within the photometric aperture; this assumption would
@@
 \cite{Morton:2011b,Fressin:2013} have made clear that the
-\kepler\ planet candidate catalogs are \emph{generally} low enough to
+\kepler\ planet candidate catalogs are generally low enough to
 ignore for the purposes of planet occurrence rate calculations, any
-more detailed study of any small subset of individual KOIs must
+more detailed study of any small subset of individual KOIs should
 understand in more detail the FPPs of those specific candidates.  This

### 2015-09-04 ms.tex
some new nb stuff

@@
 
-Before \kepler, every survey searching for transiting exoplanets had a
+Before \kepler, every survey searching for transiting exoplanets
+demanded that a candidate signal be verified as a true planet via
+radial velocity (RV) measurement of its mass.  This would involve a
+series of follow-up observations in order to weed out astrophysical
+false positive scenarios---typically stellar eclipsing binaries in
+various configurations.
+
+But for \kepler, following this model has been largely impossible
+because of the quantity and character of the flood of planet
+candidates (thousands of mostly small-planet candidates around
+relatively faint stars).  There have been a small number of
+\kepler\ planets with masses measured by RVs
+\citep[][e.g.]{Marcy:2014}, and significantly more that have been
+confirmed as planets by measurement of transit timing variations
+(TTVs) in multi-planet systems \citep[][e.g.]{}, but this still leaves
+the vast majority of candidates unaccessible to dynamical
+confirmation.
+
+This situation has inspired the development of \emph{probabilistic
+  validation} as a new approach to evaluating transit candidates.  The
+principle of probabilistic validation is to demonstrate that all
+conceivable astrophysical false positive scenarios are negligibly
+likely to be the cause of a transit candidate signal compared to the
+explanation of a planet transiting the presumed target star.  The
+``Blender'' method pioneered this approach and has validated many
+\kepler\ candidates, including .  More recently, the PASTIS analysis suite has
+been introduced \citep{Diaz:2014} and applied to both \kepler\ and
+
+Two
+examples of validation procedures that have been used in the
+literature are ``Blender'' that has been used in the validation of
+many \kepler\ planets, and PASTIS, which has also been used
 
@@
 described in \citet[][hereafter \citetalias{Morton:2012}]{Morton:2012}
-to \ncalc\ KOIs (see \sect{data} for details).  While we refer the
-reader to \citetalias{Morton:2012} for a detailed description of the
-method, we outline it briefly in this section.  The procedure as
-implemented here is publicly available in the Python module
+to \ncalc\ Kepler Objects of Interest (KOIs; see \sect{data} for
+details).  While we refer the reader to \citetalias{Morton:2012} for a
+detailed description of the method, we outline it briefly in this
+section.  The procedure as implemented here is publicly available in
+the Python module
 \vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
@@
 \item The maximum secondary eclipse depth allowed by the
-  \kepler\ photometry.  This quantity is obtained from vetting
-  metrics produced internally by the \kepler\ Science Office.  When
-  these metrics are not available for a particular KOI, we
-  default to 10$\times$ the uncertainty in the \kepler\ pipeline
-  measured transit depth (\verb|koi_depth_err1|).  While these
-  secondary metrics are not yet available on the Archive, they should
-  become available with the final data release.
+  \kepler\ photometry.  This quantity is derived by searching the
+  phased-folded KOI light curve for the deepest signal at any other
+  phase other than that of the primary transit.  This ``model-shift
+  uniqueness test'' is described in both Section 3.2.2 of
+  \citet{Rowe:2015} and \citet{Coughlin:KSCI}, and the values of these
+  metrics for the \kepler\ Data Release 24 (DR24) will soon be
+  published (Coughlin et al.~2015, in prep).  The maximum secondary
+  depth we use is
+\begin{equation}
+\eqlabel{secthresh}
+\delta_{\rm max} = \delta_{\rm sec}  + 3 \sigma_{\rm sec},
+\end{equation}
+where $\delta_{\rm sec}$ is the fitted depth and $\sigma_{\rm sec}$ is
+the uncertainty on that depth (including red noise).  As the DR24
+pipeline uses two different detrending methods, we calculate
+$\delta_{\rm max}$ and $\sigma_{\rm max}$ using both methods and take
+the maximum between the two.  When these metrics are not available for
+a particular KOI, we default to 10$\times$ the uncertainty in the
+\kepler\ pipeline measured transit depth (\verb|koi_depth_err1|).
 
@@
   ``score'' $> \posprobthresh$ (indicating a reliable result), and   
-\item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
+\item $L_{\rm tot} > 10^{-3}$, indicating that not all the hypotheses are
   poor fits to the transit signal.
@@
 
-One final note about these calculations is that unidentified
-transit timing variations (TTVs) will increase the FPP of a transit
-signal, as the shape of the folded light curve will be distorted,
-typically resulting in a longer signal which a trapezoid model will
-also identify as more V-shaped.  While we have analyzed light curves
-using known TTVs when available, we have also undoubtedly missed many
-systems with as-yet-unspecified TTV signals.  This means that a large
-FPP may be simply an indication of unidentified TTVs rather than
-indicative of an astrophysical false positive, especially in
+One final note about these calculations is that unidentified transit
+timing variations (TTVs) will increase the FPP of a transit signal, as
+the shape of the folded light curve will be distorted, typically
+resulting in a longer signal which a trapezoid model will also
+identify as more V-shaped.  While we have analyzed light curves
+correcting for known TTVs when available, we have also undoubtedly
+missed many systems with as-yet-unspecified TTV signals.  This means
+that a large FPP may be simply an indication of unidentified TTVs
+rather than an astrophysical false positive, especially in
 multi-planet systems, which should overall have a very low false
-positive rate.  \Tab{fpp} lists whether known TTV were accounted for
-when constructing the folded transit light curve for each KOI.
+positive rate \citep{Lissauer:2014,Rowe:2014}.  \Tab{fpp} lists
+whether known TTV were accounted for when constructing the folded
+transit light curve for each KOI.
 

### 2015-09-04 ms.tex
intro edits

@@
 explanation of a planet transiting the presumed target star.  The
-``Blender'' method pioneered this approach and has validated many
-\kepler\ candidates, including .  More recently, the PASTIS analysis suite has
-been introduced \citep{Diaz:2014} and applied to both \kepler\ and
+\verb|BLENDER| method pioneered this approach and has validated many
+\kepler\ candidates, including .  More recently, the \verb|PASTIS| analysis
+suite has been introduced \citep{Diaz:2014} and used to validate both
+\kepler\ and \textit{CoRoT} candidates.
 
-Two
-examples of validation procedures that have been used in the
-literature are ``Blender'' that has been used in the validation of
-many \kepler\ planets, and PASTIS, which has also been used
+While they have both proven useful for the purposes of validating
+individual candidates of particular interest, neither \verb|BLENDER|
+nor \verb|PASTIS| is designed for fully automated batch processing of
+large numbers of candidates.  \citet{Morton:2012} describe a
+computationally simpler planet validation procedure designed for
+exactly such a purpose, based on the idea of describing eclipse light
+curves as simple trapezoids and simulating realistic populations of
+astrophysical false positives.  This procedure has also been used in
+the literature to validate a number of \kepler\ planets, and has also
+been applied to a number of candidates found by the \textit{K2}
+mission \citep{Montet:2015,Becker:2015}.  The code that implements
+this procedure is now publicly available in the Python module
+\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
+\citep{vespa}.
+
+This work presents results of applying \vespa\ \emph{en masse} to the
+entire \kepler\ catalog. This is both the first time that most
+\kepler\ candidates have been individually analyzed to assess false
+positive probability and the first time that an automated planet
+validation calculation has been applied on such a large scale.  
+\Sect{methods} describes the methods used, \sect{results} presents and
+discusses the results, and \sect{conclusions} contains concluding
+remarks.
 
@@
 detailed description of the method, we outline it briefly in this
-section.  The procedure as implemented here is publicly available in
-the Python module
-\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
-\citep{vespa}.
+section.
 

### 2015-11-03 make_final_fpptable.py
santerne comparison

@@ -41,6 +41,7 @@ fpp_table['not_transitlike'] = ku.DATA.ix[kois, 'koi_fpflag_nt'].astype(bool)
 fpp_table['significant_secondary'] = ku.DATA.ix[kois, 'koi_fpflag_ss'].astype(bool)
 fpp_table['centroid_offset'] = ku.DATA.ix[kois, 'koi_fpflag_co'].astype(bool)
 fpp_table['ephem_match'] = ku.DATA.ix[kois, 'koi_fpflag_ec'].astype(bool)
+fpp_table['MES'] = ku.DATA.ix[kois, 'koi_max_mult_ev']
 
 fpp_table['exception'] = None
 fpp_table.ix[err_table[:,0], 'exception'] = err_table[:,1]

### 2015-11-20 ms.tex
edits
small edits
added text; adding desert comparisons

@@
 
-\newcommand{\ntotal}{8826}
-\newcommand{\nfail}{787}
-\newcommand{\ncalc}{8039}
+\newcommand{\ntotal}{7470}
+\newcommand{\nfail}{422}
+\newcommand{\ncalc}{7048}
 
-\newcommand{\nfp}{500}
+\newcommand{\nfp}{424}
 
@@
 
-\newcommand{\nreliable}{2854}
-\newcommand{\nval}{2136}
-\newcommand{\nreliableFP}{298}
-\newcommand{\nvalnew}{1456}
-\newcommand{\nfpnew}{195}
-\newcommand{\ncurval}{1001}
+\newcommand{\nreliable}{3018}
+\newcommand{\nval}{2818}
+\newcommand{\nreliableFP}{424}
+\newcommand{\nvalnew}{1380}
+\newcommand{\nfpnew}{424}
+\newcommand{\ncurval}{1002}
 
@@
 suite has been introduced \citep{Diaz:2014} and used to validate both
-\kepler\ and \textit{CoRoT} candidates.
+\kepler\ and \textit{CoRoT} candidates \citep{}.
 
@@
 been applied to a number of candidates found by the \textit{K2}
-mission \citep{Montet:2015,Becker:2015}.  The code that implements
-this procedure is now publicly available in the Python module
-\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
+mission \citep{Montet:2015,Becker:2015,Schlieder:2015}.  The code that
+implements this procedure is now publicly available in the Python
+module \vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
 \citep{vespa}.
@@
 define the PDF for the trapezoidal parameters under the hypothesis.
-The likelihood is then
-\begin{equation}
-  \eqlabel{lhood}
-  \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
-                                    p_i\left(\bvec{\theta}\right)\,d\bvec{\theta},
-\end{equation}
-where $\bvec{\theta}$ is the vector of trapezoidal shape parameters,
+The likelihood is then \begin{equation}   \eqlabel{lhood}   \mathcal
+L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
+p_i\left(\bvec{\theta}\right)\,d\bvec{\theta}, \end{equation} where
+$\bvec{\theta}$ is the vector of trapezoidal shape parameters,
 $p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
@@
 being the likelihood and $p_i$ being the prior, integrated over the
-  $\bvec{\theta}$ parameter space.  But for clarity, and for
-  continuity with previous publications, we continue to call $\mathcal
-  L_i$ the ``likelihood'' for hypothesis $i$.}  The hypotheses
-currently supported by \vespa\ are the following: unblended eclipsing
-binary (EB), hierarchical-triple eclipsing binary (HEB),
-chance-aligned background/foreground eclipsing binary (BEB), and
-transiting planet (Pl).  We note that the determination of the diluted
-eclipse depth of these blended scenarios assumes that the blended
-system is \emph{fully contained} within the target's photometric
-aperture.  That is, these scenarios do not account for the possibility
-that only a small fraction of the light from a nearby contaminating
-star might be in the aperture, many of which have already been
-identified via other methods \cite{Bryson:2013,Coughlin:2014}.
+$\bvec{\theta}$ parameter space.  But for clarity, and for continuity
+with previous publications, we continue to call $\mathcal L_i$ the
+``likelihood'' for hypothesis $i$.}  The hypotheses supported by
+\vespa\ are the following: unblended eclipsing binary (EB),
+hierarchical- triple eclipsing binary (HEB), chance-aligned
+background/foreground eclipsing binary (BEB), and transiting planet
+(Pl).  In this work, we also implement ``double-period'' versions of
+each of the stellar false positive scenarios, acknowledging the
+possibility that if an eclipsing binary has similar primary and
+secondar eclipse depths, then it might be mischaracterized as a
+primary-only transiting planet signal at twice the orbital period
+(especially if diluted).  We note that the determination of the
+diluted eclipse depth of all these blended scenarios assumes that the
+light from the blended system is \emph{fully contained} within the
+target's photometric aperture.  That is, these scenarios do not
+account for the possibility that only a small fraction of the light
+from a nearby contaminating star might be in the aperture, many of
+which have already been identified via other methods
+\cite{Bryson:2013,Coughlin:2014}.
 
@@
 applied to narrow down which simulated instances of each scenario may
-be counted in the final prior and likelihood evalulations; for example,
-only blended eclipsing binaries with secondary eclipse depths
+be counted in the final prior and likelihood evalulations; for
+example, only blended eclipsing binaries with secondary eclipse depths
 shallower than the observed limits contribute to the construction of
-the $p_i$ trapezoidal shape parameter PDF.
+the $p_i$ trapezoidal shape parameter PDF.  For the ``double-period''
+scenarios, we require the primary and secondary eclipse signals to
+have depths within 3-$\sigma$ of each other, where $\sigma$ is defined
+as the fitted uncertainty in the trapezoid-model depth of the
+candidate signal.
 
@@
 be the case if a star is not properly identified as evolved.  However,
-we note that of the 743 KOIs with host stars $>$2\,$R_{\odot}$ at the
-NExScI Archive, 515 of them already have FALSE POSITIVE designations;
+we note that of the 730 KOIs with host stars $>$2\,$R_{\odot}$ at the
+NExScI Archive, 502 of them already have FALSE POSITIVE designations;
 additionally, \citet{Sliski:2014} find a large false positive rate for
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Comparison with follow-up observations}
+\sectlabel{comparisons} One of the difficulties with probabilistic
+validation is that, by necessity, it is typically invoked when no
+other method of follow-up confirmation is possible.  It can therefore
+be difficult to find ways to compare the results of a calculation such
+as \vespa\ to any known observational ground-truth, or to ``validate
+the validations.''  However, because so much follow-up observational
+effort has gone into \kepler\ candidates over the last few years,
+there actually are two different datasets that do provide such
+information for relatively small subsets of candidates.  Here, we
+discuss the results of \vespa\ calculations for these candidates and
+the impliciations for the reliability of the \vespa\ framework.
+
+The first of these datasets is from \citet{Desert:2015}, who observe
+the transits of 50 \kepler\ candidates with the Spitzer Space
+Telescope in order to observationally constrain the FP rate.  The idea
+behind these observations is that a blended EB false positive will
+often show a color-dependent transit depth, and so comparing the
+candidate depths measured by \kepler\ to those measured in the
+infrared by Spitzer would give an idea of how likely a signal is to be
+a false positive. The results of their analysis suggest that fewer
+that about 8\% of their observed candidates are likely to be false
+positives.  Of these 50 candidates, \vespa\ on its own calculates FPP
+$\gt$ 0.1 for four.  Two of these (KOI-103.01 and KOI-248.02) are
+systems with known significant TTVs; the other two (KOI-247.01 and
+KOI-555.02) are likely false positives, with FPPs of 0.90 and 0.81,
+respectively.  All but two of the remaining canidates have FPP $\lt$
+0.01.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 analysis is possible.
+
+Beyond \kepler, future transit missions such as TESS and PLATO will
+require automated false positive analysis in order to efficiently sift
+through the large numbers of candidates that they will find.  This
+work demonstrates that \vespa\ will be a valuable tool towards this
+purpose.
 

### 2015-11-23 ms.tex
intro work; references

@@
 \newcommand{\nbadphotCAND}{13}
-\newcommand{\nbadrowemcmc}{216}
-\newcommand{\nbadstellar}{98} %MissingStellar
-\newcommand{\nbadsec}{162} %NoWeakSecondary
+\newcommand{\nbadrowemcmc}{233}
+\newcommand{\nbadstellar}{74} %MissingStellar
+\newcommand{\nbadsec}{8} %NoWeakSecondary
 \newcommand{\nattempted}{8141}
 \newcommand{\ntryfail}{112}
-\newcommand{\nbadtrapfit}{32}
-\newcommand{\nbadroche}{52}
-\newcommand{\nbadother}{28}
-\newcommand{\nbadotherFP}{22}
-\newcommand{\nbadotherCAND}{5}
+\newcommand{\nbadtrapfit}{36}
+\newcommand{\nbadroche}{37}
+\newcommand{\nbadother}{2}
+\newcommand{\nbadotherFP}{1}
+\newcommand{\nbadotherCAND}{1}
 \newcommand{\nbadotherCONF}{1}
@@
 \newcommand{\vespa}{\texttt{vespa}}
+\newcommand{\pastis}{\verb|PASTIS|}
+\newcommand{\blender}{\verb|BLENDER|}
 \newcommand{\isochrones}{\texttt{isochrones}}
@@
 
-But for \kepler, following this model has been largely impossible
-because of the quantity and character of the flood of planet
-candidates (thousands of mostly small-planet candidates around
-relatively faint stars).  There have been a small number of
-\kepler\ planets with masses measured by RVs
-\citep[][e.g.]{Marcy:2014}, and significantly more that have been
-confirmed as planets by measurement of transit timing variations
-(TTVs) in multi-planet systems \citep[][e.g.]{}, but this still leaves
-the vast majority of candidates unaccessible to dynamical
-confirmation.
+However, following this model has been largely impossible for \kepler\
+because of the quantity and character of the planet candidates
+(thousands of mostly small-planet candidates around relatively faint
+stars).  There have been a small number of \kepler\ planets with
+masses measured by RVs \citep[e.g.,][]{Marcy:2014}, and significantly
+more that have been confirmed as planets by measurement of transit
+timing variations (TTVs) in multi-planet systems
+\citep[e.g.,][]{Ford:2012,Steffen:2012,Fabrycky:2012,Steffen:2013},
+but this still leaves the vast majority of candidates unaccessible to
+dynamical confirmation.
 
@@
 explanation of a planet transiting the presumed target star.  The
-\verb|BLENDER| method pioneered this approach and has validated many
-\kepler\ candidates, including .  More recently, the \verb|PASTIS| analysis
-suite has been introduced \citep{Diaz:2014} and used to validate both
-\kepler\ and \textit{CoRoT} candidates \citep{}.
+\blender\ method pioneered this approach and has validated many
+\kepler\ candidates
+\citep[e.g.,][]{Borucki:2012,Kipping:2014,Torres:2015}.   More
+recently, the \pastis\ analysis suite has been introduced
+\citep{Diaz:2014} and used to validate both \kepler\ and
+\textit{CoRoT} candidates \citep[e.g.,][]{Santerne:2014,Moutou:2014}.
 
 While they have both proven useful for the purposes of validating
-individual candidates of particular interest, neither \verb|BLENDER|
-nor \verb|PASTIS| is designed for fully automated batch processing of
-large numbers of candidates.  \citet{Morton:2012} describe a
-computationally simpler planet validation procedure designed for
-exactly such a purpose, based on the idea of describing eclipse light
-curves as simple trapezoids and simulating realistic populations of
-astrophysical false positives.  This procedure has also been used in
-the literature to validate a number of \kepler\ planets, and has also
+individual candidates of particular interest, neither \blender\ nor
+\pastis\ is designed for fully automated batch processing of large
+numbers of candidates.  An alternative validation approach for
+candidates in multiple-planet systems has also been applied to a large
+number of \kepler\ systems based on the general argument that it is
+unlikely to see multiple false-positive signals in the same \kepler\
+light curve \citep{Lissauer:2012}, resulting resulting in validations
+of over 800 planets with 99\% confidence
+\citep{Lissauer:2014,Rowe:2014}. However, this methodology differs
+from the \blender/\pastis\ approach in two important ways: (a) it is
+applicable only to planets in multi-planet systems, and (b) it relies on  
+broad-brush general arguments rather than analyzing candidate signals
+individually.
+
+\citet{Morton:2012} describe a planet validation procedure that does
+analyze individual signals, but is computationally simpler than
+\blender\ or \pastis, designed explicitly for batch processing.  Based
+on the idea of describing eclipse light curves as simple trapezoids
+and simulating realistic populations of astrophysical false positives,
+This procedure has also been used in the literature to validate a
+number of \kepler\ planets
+\citep[e.g.,][]{Muirhead:2012,Dawson:2012,Swift:2013}, and has also
 been applied to a number of candidates found by the \textit{K2}
-mission \citep{Montet:2015,Becker:2015,Schlieder:2015}.  The code that
-implements this procedure is now publicly available in the Python
-module \vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
+mission \citep{Montet:2015,Becker:2015}.  The code that implements
+this procedure is publicly available in the Python module
+\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}
 \citep{vespa}.
@@
 POSITIVE.  As such, we begin with a list of \ntotal\ KOIs from the
-cumulative table at the NASA Exoplanet Science Institute (NExScI)
-Exoplanet Archive.  We then gather ancillary data and constraints from
-various sources in order to enable the \vespa\ calculation:
+Q1-Q17 (DR24) table at the NASA Exoplanet Science Institute (NExScI)
+Exoplanet Archive (the most recent available uniform catalog).  We
+then gather ancillary data and constraints from various sources in
+order to enable the \vespa\ calculation:
 
@@
 
-We were not able to successfully run \vespa\ on \nfail\ of the
-\ntotal\ total KOIs. The various reasons for these failures are
-detailed below.  
+We were not able to successfully run \vespa\ on all of the KOIs. The 
+various reasons for these failures are detailed below.  
 \begin{enumerate}
-\item \nbadphot\ KOIs did not receive MCMC modeling.  Most of these
-  (\nbadphotFP) are already designated FALSE POSITIVE at the archive,
-  though \nbadphotCAND\ have CANDIDATE disposition.
-\item \nbadrowemcmc\ KOIs did receive MCMC modeling but had unphysical fit
+\item Some KOIs did not receive MCMC modeling.  Most of these
+  have been are already designated FALSE POSITIVE at the archive.
+\item A number of KOIs (\nbadrowemcmc) did receive MCMC modeling but had unphysical fit
   results; e.g., negative $R_p/R_\star$ or best-fit impact parameter
-  greater than $(1 + R_p/R_\star)$.
+  greater than $(1 + R_p/R_\star)$.  These KOIs were left out of the \vespa calculations.
 \item The host stars of \nbadstellar\ KOIs are not included in the
@@
 \item Finally, \nbadother\ KOIs failed for as-yet undetermined
-  reasons.  \nbadotherFP\ of these are already designated FALSE
-  POSITIVE, \nbadotherCAND\ are CANDIDATE, and \nbadotherCONF\ is
-  dispositioned as a confirmed planet.
+  reasons, one of which is a FALSE POSITIVE (371.02) and one is a 
+  candidate (2433.06).
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison with follow-up observations}
-\sectlabel{comparisons} One of the difficulties with probabilistic
+\section{Comparison with follow-up surveys}
+\sectlabel{comparisons}
+
+One of the difficulties with probabilistic
 validation is that, by necessity, it is typically invoked when no
@@
 a false positive. The results of their analysis suggest that fewer
-that about 8\% of their observed candidates are likely to be false
+than 8\% of their observed candidates are likely to be false
 positives.  Of these 50 candidates, \vespa\ on its own calculates FPP
-$\gt$ 0.1 for four.  Two of these (KOI-103.01 and KOI-248.02) are
+$>$ 0.1 for four.  Two of these (KOI-103.01 and KOI-248.02) are
 systems with known significant TTVs; the other two (KOI-247.01 and
 KOI-555.02) are likely false positives, with FPPs of 0.90 and 0.81,
-respectively.  All but two of the remaining canidates have FPP $\lt$
-0.01.
+respectively.  For all but two of the remaining candidates, \vespa\
+gives FPP $< 0.01$.  The false positive rates calculated in
+\citet{Desert:2015} are also based on probabilistic arguments very
+similar to \citet{Morton:2011b} and thus are not quite candidates for
+``ground-truth'' comparison, but the lack of transit chromaticity and
+the agreements between these two independent studies are certainly
+supportive of the \vespa\ results.
+
+A much more independent and powerful test data set has recently become
+available in the work of \citet{Santerne:2015}, which presented the
+results of a long-term RV-monitoring campaign targeting 129 \kepler\
+giant-planet candidates.  Of these, they confirm 45 to be planets and
+identify 48 as eclipsing binaries, 15 as contaminating EBs (CEBs), and
+3 as brown dwarfs.  They are unable to determine the nature of the
+remaining 18.  These results imply a relatively high FP rate among
+giant-planet candidates, possibly near 50\%, which sounds potentially
+concerning.  However, when we look at our results on this sample, we
+see very good agreement between the \vespa\ predictions and the RV-
+detected ``ground truth'' (\Tab{santerne}).  Notably, confirmed
+planets show a mean FPP of about 9\% and a median of only 0.02\%,
+while confirmed EBs (CEBs) show a mean FPP of 78\% (83\%) and a median
+of 95\% (99.5\%).  The three brown dwarfs also show low FPPs, which is
+understandable because \vespa\ doesn't pretend to predict anything
+about the mass of the companion, and BDs are essentially the same size
+as giant planets.  It is also instructive to investigate the four
+cases where \vespa\ computes high FPPs ($>$0.3) for confirmed planets.
+Three of these (KOI-377.01, KOI-1426.02 and KOI-1474.01) have
+significant TTVs, and one is a grazing eclipse (KOI-614.01).
+KOI-1474.01 is also on a highly eccentric orbit \citep{Dawson:2012},
+in addition to its TTVs, which also contributes to its high FPP.
+Overall, this comparison powerfully demonstrates the reliability of
+the \vespa\ calculation, showing that even in a population of
+candidates that include many false positives, it is able to
+effectively identify which are true planets and which are not.
+
+\begin{deluxetable}{ccc}
+\tabletypesize{\scriptsize}
+\tablecaption{\vespa--calculated FPPs of the \\Santerne (2015) RV sample
+  \tablabel{santerne}}
+\tablehead{\colhead{nature} & \colhead{mean FPP} & \colhead{median FPP}}
+\startdata
+planet & 0.0892 & 0.0002 \\
+BD & 0.0035 & 0.0038 \\
+EB & 0.7764 & 0.9450 \\
+CEB & 0.8326 & 0.9950 \\
+? & 0.2393 & 0.0032
+\enddata
+\end{deluxetable}
 
@@
 In this work, we have calculated the astrophysical false positive
-probability (FPP) for every \kepler\ object of interest (KOI), using
-the publicly available Python module \vespa.  While the assumptions
-behind this calculation are not necessarily valid for every KOI (see
-\sect{results:fpp}), we have identified \nvalnew\ KOIs that have
-reliable FPPs of $< 0.01$, resulting in validation of their planetary
-nature at the 99\% confidence level, more than doubling the number of
-confirmed \kepler\ exoplanets.  Among this set of reliable \vespa\
-calculations are also \nfpnew\ new likely false positive KOIs,
-although we note that there is a chance that some of these large FPPs
-are due to unidentified or miscorrected transit timing variations.
+probability (FPP) for every \kepler\ object of interest (KOI) in the
+Q1-Q17 (DR24) table, using the publicly available Python module
+\vespa, which implements the procedure introduced in
+\citet{Morton:2012}, with improvements in stellar parameter modeling
+and the inclusion of new ``double-period'' false positive scenarios.
+While the assumptions behind this calculation are not necessarily
+valid for every KOI (see \sect{results:fpp}), we have identified
+\nvalnew\ KOIs that have reliable FPPs of $< 0.01$, resulting in
+validation of their planetary nature at the 99\% confidence level,
+more than doubling the number of confirmed \kepler\ exoplanets.  Among
+this set of reliable \vespa\ calculations are also \nfpnew\ new likely
+false positive KOIs, although we note that some of these may be due to
+unidentified or miscorrected transit timing variations.
 
-The reliability of these calculations is dependent largely on the
-results of \citet{Bryson:KSCI}, which quantify the probability that
-the eclipse/transit signal is spatially coincident on the sky with the
+These calculations depend largely on the results of
+\citet{Bryson:KSCI}, which quantify the probability that the
+eclipse/transit signal is spatially coincident on the sky with the
 presumed target star.  Without confirmation that the transit signal is
@@
 there is currently no support within \vespa\ to calculate the FPP for
-a candidate which has a \emph{specifically identified} but hitherto
+a candidate which has a \emph{specifically identified} but previously
 unknown close companion.  Future development plans for the

### 2015-11-24 ms.tex
draft sent to collaborators

@@
 
-\newcommand{\nbadphot}{47} %EmptyPhotometry or MissingKOI
-\newcommand{\nbadphotFP}{34}
-\newcommand{\nbadphotCAND}{13}
+\newcommand{\nbadphot}{28} %EmptyPhotometry or BadPhotometry of MissingKOI or IOError
+%\newcommand{\nbadphotFP}{34}
+%\newcommand{\nbadphotCAND}{13}
 \newcommand{\nbadrowemcmc}{233}
@@
 \newcommand{\nbadsec}{8} %NoWeakSecondary
-\newcommand{\nattempted}{8141}
-\newcommand{\ntryfail}{112}
-\newcommand{\nbadtrapfit}{36}
+%\newcommand{\nattempted}{8141}
+%\newcommand{\ntryfail}{112}
+\newcommand{\nbadtrapfit}{38}
 \newcommand{\nbadroche}{37}
-\newcommand{\nbadother}{2}
-\newcommand{\nbadotherFP}{1}
-\newcommand{\nbadotherCAND}{1}
-\newcommand{\nbadotherCONF}{1}
-
-\newcommand{\nreliable}{3018}
-\newcommand{\nval}{2818}
-\newcommand{\nreliableFP}{424}
+%\newcommand{\nbadother}{2}
+%\newcommand{\nbadotherFP}{1}
+%\newcommand{\nbadotherCAND}{1}
+%\newcommand{\nbadotherCONF}{1}
+
+\newcommand{\nreliable}{2943}
+\newcommand{\nval}{2046}
+\newcommand{\nreliableFP}{419}
 \newcommand{\nvalnew}{1380}
@@
 \newcommand{\vespa}{\texttt{vespa}}
-\newcommand{\pastis}{\verb|PASTIS|}
-\newcommand{\blender}{\verb|BLENDER|}
 \newcommand{\isochrones}{\texttt{isochrones}}
@@
 \affil{Department of Astrophysical Sciences, Princeton University}
+\author{et al.}
 
@@
 \begin{abstract}
-We present transit signal false positive probability calculations for
+We present astrophysical false positive probability calculations for
 every \kepler\ Object of Interest (KOI)---the first large-scale
@@
 systems, such as the prevalence of planets between the size of Earth
-and Neptune, and a population of very compact multiple-planet
-systems. And perhaps most notably, it has enabled for the first time
-estimates of the occurrence rates of small planets ($\gtrsim$1
-$R_\oplus$) out to orbits of about one year.  It is important to
+and Neptune, and a population of very compact multiple-planet systems.
+And perhaps most notably, it has enabled for the first time estimates
+of the occurrence rates of small planets ($\gtrsim$1 $R_\oplus$) out
+to orbits of about one year
+\citep[e.g.][]{Petigura:2013,DFM:2014,Burke:2015}.  It is important to
 remember, however, that these revolutionary discoveries depend
@@
 false positive scenarios---typically stellar eclipsing binaries in
-various configurations.
-
-However, following this model has been largely impossible for \kepler\
-because of the quantity and character of the planet candidates
-(thousands of mostly small-planet candidates around relatively faint
-stars).  There have been a small number of \kepler\ planets with
-masses measured by RVs \citep[e.g.,][]{Marcy:2014}, and significantly
-more that have been confirmed as planets by measurement of transit
-timing variations (TTVs) in multi-planet systems
+various configurations.  However, following this model has been
+largely impossible for \kepler\ because of the quantity and character
+of the planet candidates (thousands of mostly small-planet candidates
+around relatively faint stars).  There have been a small number of
+\kepler\ planets with masses measured by RVs
+\citep[e.g.,][]{Marcy:2014,Santerne:2015}, and significantly more that
+have been confirmed as planets by measurement of transit timing
+variations (TTVs) in multi-planet systems
 \citep[e.g.,][]{Ford:2012,Steffen:2012,Fabrycky:2012,Steffen:2013},
@@
 explanation of a planet transiting the presumed target star.  The
-\blender\ method pioneered this approach and has validated many
+\verb|BLENDER| method pioneered this approach and has validated many
 \kepler\ candidates
 \citep[e.g.,][]{Borucki:2012,Kipping:2014,Torres:2015}.   More
-recently, the \pastis\ analysis suite has been introduced
+recently, the \verb|PASTIS| analysis suite has been introduced
 \citep{Diaz:2014} and used to validate both \kepler\ and
 \textit{CoRoT} candidates \citep[e.g.,][]{Santerne:2014,Moutou:2014}.
+An alternative validation approach for candidates in multiple-planet
+systems has also been applied to a large number of \kepler\ systems
+based on the general argument that it is unlikely to see multiple
+false-positive signals in the same \kepler\ light curve
+\citep{Lissauer:2012}, resulting resulting in validations of over 800
+planets with 99\% confidence \citep{Lissauer:2014,Rowe:2014}. This
+methodology differs from the \verb|BLENDER|/\verb|PASTIS| approach in
+two significant ways: (a) it is applicable only to planets in multi-
+planet systems, and (b) it relies on broad-brush general arguments
+rather than analyzing the details of candidate signals individually.
 
 While they have both proven useful for the purposes of validating
-individual candidates of particular interest, neither \blender\ nor
-\pastis\ is designed for fully automated batch processing of large
-numbers of candidates.  An alternative validation approach for
-candidates in multiple-planet systems has also been applied to a large
-number of \kepler\ systems based on the general argument that it is
-unlikely to see multiple false-positive signals in the same \kepler\
-light curve \citep{Lissauer:2012}, resulting resulting in validations
-of over 800 planets with 99\% confidence
-\citep{Lissauer:2014,Rowe:2014}. However, this methodology differs
-from the \blender/\pastis\ approach in two important ways: (a) it is
-applicable only to planets in multi-planet systems, and (b) it relies on  
-broad-brush general arguments rather than analyzing candidate signals
-individually.
-
-\citet{Morton:2012} describe a planet validation procedure that does
-analyze individual signals, but is computationally simpler than
-\blender\ or \pastis, designed explicitly for batch processing.  Based
-on the idea of describing eclipse light curves as simple trapezoids
-and simulating realistic populations of astrophysical false positives,
-This procedure has also been used in the literature to validate a
-number of \kepler\ planets
+individual candidates of particular interest, neither \verb|BLENDER|
+nor \verb|PASTIS| is designed for fully automated batch processing of
+large numbers of candidates.  \citet{Morton:2012} describes a
+computationally simpler planet validation procedure designed for
+exactly such a purpose, based on the idea of describing eclipse light
+curves as simple trapezoids and simulating realistic populations of
+astrophysical false positives. This procedure has also been used in
+the literature to validate a number of \kepler\ planets
 \citep[e.g.,][]{Muirhead:2012,Dawson:2012,Swift:2013}, and has also
@@
 \kepler\ candidates have been individually analyzed to assess false
-positive probability and the first time that an automated planet
-validation calculation has been applied on such a large scale.  
+positive probability and the first time that a detailed automated
+planet validation calculation has been applied on such a large scale.
 \Sect{methods} describes the methods used, \sect{results} presents and
@@
 estimating the radii of KOI host stars has also been emphasized by
-\citetalias{Bastien:2014}, who find from photometric ``flicker''
+\citet{Bastien:2014}, who find from photometric ``flicker''
 measurements that a significant number of FGK KOI hosts may be
@@
 \begin{enumerate}
-\item Some KOIs did not receive MCMC modeling.  Most of these
+\item \nbadphot\ KOIs did not receive MCMC modeling.  Most of these
   have been are already designated FALSE POSITIVE at the archive.
-\item A number of KOIs (\nbadrowemcmc) did receive MCMC modeling but had unphysical fit
+\item \nbadrowemcmc\ KOIs did receive MCMC modeling but had unphysical fit
   results; e.g., negative $R_p/R_\star$ or best-fit impact parameter
-  greater than $(1 + R_p/R_\star)$.  These KOIs were left out of the \vespa calculations.
+  greater than $(1 + R_p/R_\star)$.  These KOIs were left out of the \vespa\ calculations.
 \item The host stars of \nbadstellar\ KOIs are not included in the
@@
   length.
-\item For \nbadroche\ KOIs, the period of the planet was such that its
-  orbit was implied to be within its host star's Roche limit.  This
+\item For \nbadroche\ KOIs, the orbital period and stellar properties of the 
+  candidate imply the orbit to be within its host star's Roche limit.  This
   usually happens when the host star is estimated to be a giant, and
   these situations are nearly always false positives. 
-\item Finally, \nbadother\ KOIs failed for as-yet undetermined
-  reasons, one of which is a FALSE POSITIVE (371.02) and one is a 
-  candidate (2433.06).
+%\item Finally, a small number of KOIs failed for as-yet-undetermined
+%  reasons.  %, one of which is a FALSE POSITIVE (371.02) and one is a 
+%  candidate (2433.06).
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison with follow-up surveys}
+\section{Comparison with follow-up observational surveys}
 \sectlabel{comparisons}
@@
   \tablabel{santerne}}
-\tablehead{\colhead{nature} & \colhead{mean FPP} & \colhead{median FPP}}
+\tablehead{\colhead{RV-based nature} & \colhead{mean FPP} & \colhead{median FPP}}
 \startdata
-planet & 0.0892 & 0.0002 \\
-BD & 0.0035 & 0.0038 \\
-EB & 0.7764 & 0.9450 \\
-CEB & 0.8326 & 0.9950 \\
-? & 0.2393 & 0.0032
+Planet & 0.0892 & 0.0002 \\
+Brown dwarf & 0.0035 & 0.0038 \\
+Eclipsing binary (EB) & 0.7764 & 0.9450 \\
+Contaminating EB & 0.8326 & 0.9950 \\
+Undetermined & 0.2393 & 0.0032
 \enddata
@@
 While previous \emph{a priori} false positive rate estimates
-\cite{Morton:2011b,Fressin:2013} have made clear that the
-\kepler\ planet candidate catalogs are generally low enough to
-ignore for the purposes of planet occurrence rate calculations, any
-more detailed study of any small subset of individual KOIs should
-understand in more detail the FPPs of those specific candidates.  This
-type of small-sample candidate culling using individually calculated
-FPPs has already been done in the literature
-\citep{MortonSwift:2014,MortonWinn:2015}; the publication of this full
-catalog allows the community to do the same.
+\citep{Morton:2011b,Fressin:2013} have made clear that the \kepler\
+planet candidate catalogs are generally low enough to ignore for the
+purposes of planet occurrence rate calculations, any more detailed
+study of any small subset of individual KOIs should understand in more
+detail the FPPs of those specific candidates.  This type of small-sample 
+candidate culling using individually calculated FPPs has
+already been done in the literature
+\citep{MortonSwift:2014,MortonWinn:2014}; the publication of this full
+catalog allows the community to do the same.  In particular, several
+other studies have shown that specific samples of KOIs tend to have
+large FPPs than the global average, so studies involving giant-planet
+KOIs \citep{Santerne:2015} or evolved stars \citep{Sliski:2014} are in
+even greater need of individual FPP analysis.
 
@@
 \begin{center}
+\includegraphics[width=7in]{figures/fpp_summary_fp.pdf}
+\end{center}
+\caption{Same as \Fig{fppall}, but for KOIs currently dispositioned
+  as FALSE POSITIVE. The vast majority are also identified by \vespa\ as likely
+  false positives.  There are also some that have low FPPs, but this can be
+  explained by the fact that many of the reasons for dispositioning a 
+  KOI as a FALSE POSITIVE also invalidate assumptions made by \vespa; 
+  for example, that the signal is spatially coincident with the target 
+  star (see \Sect{results}). This figure illustrates that \vespa\ is
+  effective (though not 100\% efficient) at recovering known false positives.  
+  \figlabel{fppfps}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
 \includegraphics[width=7in]{figures/fpp_pie.pdf}
@@
   grouped by false positive probability.  \nvalnew\ of these are new
-  planet validations, and \nfpnew\ are new likely false positives.
+  planet validations.%, and \nfpnew\ are new likely false positives.
   \figlabel{fpppie}}

### 2015-12-09 ms.tex
new validation table written

@@
 %\newcommand{\ntryfail}{112}
-\newcommand{\nbadtrapfit}{38}
+\newcommand{\nbadtrapfit}{38} %MCMCError or NoFitError
 \newcommand{\nbadroche}{37}
@@
 
-\newcommand{\nreliable}{2943}
-\newcommand{\nval}{2046}
-\newcommand{\nreliableFP}{419}
-\newcommand{\nvalnew}{1380}
-\newcommand{\nfpnew}{424}
-\newcommand{\ncurval}{1002}
+\newcommand{\nreliable}{2823} %from figure
+\newcommand{\nval}{1994} %from figure
+\newcommand{\nreliableFP}{398} %from figure
+\newcommand{\nvalnew}{1324} %from pie chart
+\newcommand{\nfpnew}{424}  % all candidate with FPP < 0.9
+\newcommand{\ncurval}{984} % from pie chart
 
@@
 
-\shorttitle{False Positive Probabilities for KOIs}
+\shorttitle{False Positive Probabilities for all KOIs}
 \shortauthors{Morton et al.}
@@
 planet validation calculation has been applied on such a large scale.
-\Sect{methods} describes the methods used, \sect{results} presents and
-discusses the results, and \sect{conclusions} contains concluding
+\Sect{methods} describes the methods used, \sect{data} describes the data set,
+\sect{results} presents the results, \sect{comparisons} compares these
+results with observational studies, and \sect{conclusions} contains concluding
 remarks.
@@
 
+\begin{deluxetable}{ccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Mean FPPs of candidate KOIs with reliable \vespa\ calculations
+  \tablabel{meanFPP}}
+\tablehead{\colhead{Selection} & \colhead{Number} & \colhead{mean FPP}}
+\startdata
+all & 2823 & 0.148 \\
+singles & 1665 & 0.196 \\
+multis & 1158 & 0.078 \\
+$R_p > 10\,R_\oplus$ & 347 & 0.704 \\ 
+$4\,R_\oplus < R_p < 10\,R_\oplus$ & 245 & 0.182 \\ 
+$2\,R_\oplus < R_p < 4\,R_\oplus$ & 1150 & 0.057 \\ 
+$R_p < 2\,R_\oplus$ & 1081 & 0.058 
+\enddata
+\end{deluxetable}
+
 To summarize, the results presented in \tab{fpp} are strictly reliable
@@
 is designated a CANDIDATE (or CONFIRMED) and has large enough SNR to
-enable secure positional determination.
-
-To enable interpretation, \tab{fpp} thus contains both the current KOI
-disposition and the results of the positional probability calculations
+enable secure positional determination.  In addition, for greatest
+reliability we also require a signal's multiple-event statistic (MES;
+equivalend to SNR) to be greater than 10, in order to avoid low-SNR
+signals that might be caused by light-curve systematics.
+
+To enable interpretation, \tab{fpp} thus contains the current KOI
+disposition, MES, and the results of the positional probability calculations
 of \citet{Bryson:KSCI}.  \Fig{fppall} shows FPPs for all KOIs passing
@@
 \item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive,
-\item $> 0.99$ probability to be on the target star, according
+\item MES $>$ 10, indicating the signal is unlikely to be caused by 
+      systematic noise in the light curve,
+\item Probability $> 0.99$ to be on the target star, according
   to \citet{Bryson:KSCI}, along with a positional probability
@@
 These selections leave \nreliable\ KOIs for which the \vespa\ results
-can be considered most reliable.  Of these, \nval\ have ${\rm FPP} <
-0.01$, and are thus validated at the 99\% level.  These are not all
+can be considered most reliable;  \Tab{meanFPP} presents the mean FPPs
+for different subsets, showing several notable features.  Single KOIs
+are about 3$\times$ more likely to be false positives than KOIs in
+multiple-KOI systems, in qualitative agreement with
+\citet{Lissauer:2012}---and this is true even without giving any
+``multiplicity boost'' to multi-KOI systems for the increased transit
+probability of subsequent planets once one planet transits in a
+coplanar system.  Also, large candidates typically have high FPPs, in
+agreement with \citet{Santerne:2012} and \citet{Santerne:2015}.  And
+finally, the mean FPPs are very consistent with the \textit{a priori}
+predictions of \citet{Morton:2011b} and with the analysis of
+\citet{Fressin:2013}.
+
+Of these KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
+<0.01$, and are thus validated at the 99\% level.  These are not all
 new validations, however, since a number of these are already
@@
 CANDIDATE KOIs, grouped by FPP.
+
+In addition to the confident validations, we identify \nfpnew\ KOIs
+that currently have CANDIDATE disposition but for which \vespa\
+calculates FPP $>$ 0.9; these KOIs are likely to be false positives.
+We note that these likely false positives are not required to obey the
+same selections that were done in order to ensure a clean sample for
+validation.  This is because even if a signal has characteristics
+such that a low \vespa\ FPP would not be  sufficient to validate it, a
+high \vespa\ FPP is still sufficient to cast doubt on its planetary
+nature.  As a demonstration of the ability of \vespa\ to identify 
+false positives, \Fig{fppfps} shows the FPPs for KOIs that are 
+dispositioned FALSE POSITIVE and have MES $>$ 10 and $L_{\rm tot} > 10^{-3}$.
+The vast majority of these have large FPPs.
 
@@
 rather than an astrophysical false positive, especially in  
-multi-planet systems, which should overall have a very low false
-positive rate \citep{Lissauer:2014,Rowe:2014}.  \Tab{fpp} lists
-whether known TTV were accounted for when constructing the folded
-transit light curve for each KOI.
+multi-planet systems, which should overall have a very low false positive
+rate \citep{Lissauer:2014,Rowe:2014}.  It is thus probable that
+despite multi-KOIs having lower FPPs than singles (\tab{meanFPP}),
+even these relatively low FPPs are inflated by the effect of TTVs.
+\Tab{fpp} lists whether known TTV were accounted for when constructing
+the folded transit light curve for each KOI.
 
@@
 We were not able to successfully run \vespa\ on all of the KOIs. The 
-various reasons for these failures are detailed below.  
+various reasons for these occasional failures are detailed below.  
 \begin{enumerate}
@@
 
+We also briefly discuss another case of individual interest.
+KOI-6705.01, a 0.99\,d signal around a mid M-dwarf star, was
+identified  as a KOI of possible interest by \citet{Gaidos:2015}.
+After significant follow-up observations and detailed full-frame image
+analysis, they concluded that the signal was most likely due to a
+charge-transfer  effect from a 1.99\,d EB located on the same CCD
+column.  For this KOI, \vespa\ calculates an FPP of 1, with
+probabilities of 0.86 to be a BEB, 0.13 to be a BEB with twice the
+period (the true scenario uncovered by the detective work of
+\citet{Gaidos:2015}), and 0.01 to be an HEB.
+
 \begin{deluxetable}{ccc}
@@
 
-These calculations depend largely on the results of
-\citet{Bryson:KSCI}, which quantify the probability that the
-eclipse/transit signal is spatially coincident on the sky with the
+The reliability of these calculations depends significantly on the
+results of \citet{Bryson:KSCI}, which quantify the probability that
+the eclipse/transit signal is spatially coincident on the sky with the
 presumed target star.  Without confirmation that the transit signal is

### 2015-12-09 make_final_fpptable.py

@@ -7,6 +7,7 @@ import os
 from configobj import ConfigObj
 
 from keputils import koiutils as ku
+DATA = ku.DR24
 
 from astropy import constants as const
 RSUN = const.R_sun.cgs.value
@@ -31,24 +32,25 @@ err_table = np.loadtxt('fpp_err.txt', usecols=(0,1), dtype=str)
 
 kois = fpp_table.index
 
-fpp_table['kepid'] = ku.DATA.ix[kois, 'kepid']
-fpp_table['period'] = ku.DATA.ix[kois, 'koi_period']
+fpp_table['kepid'] = DATA.ix[kois, 'kepid']
+fpp_table['period'] = DATA.ix[kois, 'koi_period']
 fpp_table['rp'] = fpp_table.ix[kois, 'rprs'] * star_table.ix[kois, 'radius'] * RSUN/REARTH
-fpp_table['disposition'] = ku.DATA.ix[kois, 'koi_disposition']
+fpp_table['disposition'] = DATA.ix[kois, 'koi_disposition']
 fpp_table['prob_ontarget'] = positional_table.ix[kois, 'pp_host_rel_prob']
 fpp_table['pos_prob_score'] = positional_table.ix[kois, 'pp_host_prob_score']
-fpp_table['not_transitlike'] = ku.DATA.ix[kois, 'koi_fpflag_nt'].astype(bool)
-fpp_table['significant_secondary'] = ku.DATA.ix[kois, 'koi_fpflag_ss'].astype(bool)
-fpp_table['centroid_offset'] = ku.DATA.ix[kois, 'koi_fpflag_co'].astype(bool)
-fpp_table['ephem_match'] = ku.DATA.ix[kois, 'koi_fpflag_ec'].astype(bool)
-fpp_table['MES'] = ku.DATA.ix[kois, 'koi_max_mult_ev']
+fpp_table['not_transitlike'] = DATA.ix[kois, 'koi_fpflag_nt'].astype(bool)
+fpp_table['significant_secondary'] = DATA.ix[kois, 'koi_fpflag_ss'].astype(bool)
+fpp_table['centroid_offset'] = DATA.ix[kois, 'koi_fpflag_co'].astype(bool)
+fpp_table['ephem_match'] = DATA.ix[kois, 'koi_fpflag_ec'].astype(bool)
+fpp_table['MES'] = DATA.ix[kois, 'koi_max_mult_ev']
 
[…]

### 2015-12-18 parse_hammerfile.py
new APP data in

@@ -3,8 +3,10 @@
 import numpy as np
 import pandas as pd
 
+app_hammerfile = 'forTim_kplr20151218020451_appham.txt'
+
 d = {}
-for line in open('app_hammer.txt'):
+for line in open(app_hammerfile):
     line = line.strip().split('|')
     try:
         if line[1] not in d:

### 2015-12-19 ms.tex
edits suggested by JC

@@
 \newcommand{\nbadroche}{37}
-%\newcommand{\nbadother}{2}
-%\newcommand{\nbadotherFP}{1}
-%\newcommand{\nbadotherCAND}{1}
-%\newcommand{\nbadotherCONF}{1}
 
 \newcommand{\nreliable}{2823} %from figure
-\newcommand{\nval}{1994} %from figure
+\newcommand{\nval}{1997} %from figure
 \newcommand{\nreliableFP}{398} %from figure
-\newcommand{\nvalnew}{1324} %from pie chart
+\newcommand{\nvalnew}{1325} %from pie chart
 \newcommand{\nfpnew}{424}  % all candidate with FPP < 0.9
@@
 
-\author{Timothy D. Morton}
-\affil{Department of Astrophysical Sciences, Princeton University}
-\author{et al.}
+%\author{Timothy D. Morton}
+%\affil{Department of Astrophysical Sciences, Princeton University}
+\author{Timothy D.
+Morton\altaffilmark{1}, Stephen T.
+Bryson\altaffilmark{2}, Jeffrey L.
+Coughlin\altaffilmark{2,3}, Jason F.
+Rowe\altaffilmark{4},Michael R.
+Haas\altaffilmark{2}, and Natalie M.
+Batalha\altaffilmark{2}}
+
+%\journalinfo{} and \submitted{}
+%\journalinfo{Accepted for Publication in the Astronomical Journal - Feb. 21, 2014}
+%\submitted{}
+
+\altaffiltext{1}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA, tdm@astro.princeton.edu}
+\altaffiltext{2}{NASA Ames Research Center, M/S 244-30, Moffett Field, CA 94035, USA}
+\altaffiltext{3}{SETI Institute, 189 Bernardo Ave, Mountain View, CA 94043, USA}
+\altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
 
@@
 variations (TTVs) in multi-planet systems
-\citep[e.g.,][]{Ford:2012,Steffen:2012,Fabrycky:2012,Steffen:2013},
-but this still leaves the vast majority of candidates unaccessible to
+\citep[e.g.,][]{Ford:2012,Steffen:2012,Fabrycky:2012,Steffen:2013,Jontof:2015},
+but this still leaves the vast majority of candidates inaccessible to
 dynamical confirmation.
@@
 possibility that if an eclipsing binary has similar primary and
-secondar eclipse depths, then it might be mischaracterized as a
+secondary eclipse depths, then it might be mischaracterized as a
 primary-only transiting planet signal at twice the orbital period
@@
 POSITIVE.  As such, we begin with a list of \ntotal\ KOIs from the
-Q1-Q17 (DR24) table at the NASA Exoplanet Science Institute (NExScI)
+Q1-Q17 DR24 table at the NASA Exoplanet Science Institute (NExScI)
 Exoplanet Archive (the most recent available uniform catalog).  We
@@
   \citet{Rowe:2015} and \citet{Coughlin:KSCI}, and the values of these
-  metrics for the \kepler\ Data Release 24 (DR24) will soon be
-  published (Coughlin et al.~2015, in prep).  The maximum secondary
+  metrics for the Q1-Q17 DR24 release will soon be
+  published (Coughlin et al.~2015, submitted).  The maximum secondary
   depth we use is
@@
 
-Of the \ntotal\ KOIs in the cumulative table at the NExScI Exoplanet
+Of the \ntotal\ KOIs in the Q1-Q17 DR24 table at the NExScI Exoplanet
 Archive, \vespa\ successfully calculates the FPP for \ncalc.  These
@@
 However, because of the generally permissive philosophy of the
-\kepler\ dispositioning, not all CANDIDATE KOIs receive the same level
-of vetting.  That is, something is not identified as a FALSE POSITIVE
+\kepler\ dispositioning, not all CANDIDATE KOIs have the same level of 
+reliability in their disposition, due an ``innocent 
+until proven guilty'' philosophy.
+That is, something is not identified as a FALSE POSITIVE
 \emph{unless there is positive confirmation of false positive status}.
@@
 Of these KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
-<0.01$, and are thus validated at the 99\% level.  These are not all
-new validations, however, since a number of these are already
-CONFIRMED.  \Fig{fpppie} shows a different kind of summary, grouping
-KOIs by disposition and splitting up the CANDIDATES according to the
-\vespa\ results, showing that \nvalnew\ KOIs are newly validated at
-the 99\% level. \Fig{rpcand} shows the radii and periods of the
-CANDIDATE KOIs, grouped by FPP.
+<0.01$, and are thus validated at the 99\% level.  These KOIs are
+marked as labeled as such in \tab{fpp}.  These are not all new
+validations, however, since a number of them are already CONFIRMED.
+\Fig{fpppie} shows a different kind of summary, grouping KOIs by
+disposition and splitting up the CANDIDATES according to the \vespa\
+results, showing that \nvalnew\ KOIs are newly validated at the 99\%
+level. \Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
+grouped by FPP.
 
@@
 calculates FPP $>$ 0.9; these KOIs are likely to be false positives.
-We note that these likely false positives are not required to obey the
-same selections that were done in order to ensure a clean sample for
-validation.  This is because even if a signal has characteristics
-such that a low \vespa\ FPP would not be  sufficient to validate it, a
-high \vespa\ FPP is still sufficient to cast doubt on its planetary
-nature.  As a demonstration of the ability of \vespa\ to identify 
-false positives, \Fig{fppfps} shows the FPPs for KOIs that are 
-dispositioned FALSE POSITIVE and have MES $>$ 10 and $L_{\rm tot} > 10^{-3}$.
-The vast majority of these have large FPPs.
+As \Fig{rpcand} shows, many of these newly identified false positives
+have large radii---this is again because of the dispositioning
+philosophy adopted by the \kepler\ team, which does not use any cut in
+transit depth or inferred ``planet'' size to identify FALSE POSITIVES.
+To identify these likely false positives from the \vespa\
+calculations, we do not require CANDIDATES to obey the same selections
+we used to ensure a clean sample for validation.  This is because even
+if a signal has characteristics such that a low \vespa\ FPP would not
+be sufficient to validate it, a high \vespa\ FPP is still sufficient
+to cast doubt on its planetary nature. As a demonstration of the
+ability of \vespa\ to identify false positives, \Fig{fppfps} shows the
+FPPs for KOIs that are dispositioned FALSE POSITIVE and have MES $>$
+10 and $L_{\rm tot} > 10^{-3}$. The vast majority of these have large
+FPPs.
 
@@
 
+\subsection{Unidentified Ephemeris Matches?}
+\sectlabel{PEMs}
+
+One potential concern for the reliability of the validations presented
+here might be the possibility of unidentified ephemeris matches, or
+``period-epoch matches'' (PEMs).  \citet{Coughlin:2014} identified a
+number of false positives among KOIs using this method, by comparing
+the periods and epochs of KOIs both to each other and to known
+catalogs of eclipsing binaries in order to see if any have identical
+ephemerides, an indication of contamination, sometimes from far away 
+on the \kepler\ CCD.
+
+In the Q1-Q17 DR24 KOI table used as the basis for this work, 980
+KOIs were identified as PEMs.  Of these, 187 were not identified by
+any other method.  Only 18 of these 187 survived all the quality cuts
+described in \sect{results:fpp}. And of these 18, only 4 have FPP 
+$< 0.01$.
+
+Thus, we expect only about 0.4\% (4/980) of unidentified PEMs to end
+up as validated according to \vespa. As the total rate of PEMs is
+estimated to be something around 35\% \citep{Coughlin:2014}, there
+remains a small ($\sim$0.1\%  chance) that any of the validated
+planets may turn out to be due to  as-yet unidentified contamination
+from one of the false positive  sources that cause PEMs.  In other
+words, among our validated sample of planets, there may well be one or
+two that turn out to be false positives due to distant contamination
+(such as via the ``column anomaly'' effect), but not substantially
+more.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   results; e.g., negative $R_p/R_\star$ or best-fit impact parameter
-  greater than $(1 + R_p/R_\star)$.  These KOIs were left out of the \vespa\ calculations.
+  greater than $(1 + R_p/R_\star)$.  These KOIs were left out of the 
+  \vespa\ calculations.
 \item The host stars of \nbadstellar\ KOIs are not included in the
@@
   these situations are nearly always false positives. 
-%\item Finally, a small number of KOIs failed for as-yet-undetermined
-%  reasons.  %, one of which is a FALSE POSITIVE (371.02) and one is a 
-%  candidate (2433.06).
 \end{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison with follow-up observational surveys}
+\section{Comparison with follow-up observational studies}
 \sectlabel{comparisons}
@@
 
+\subsection{\textit{Spitzer} photometry}
+
 The first of these datasets is from \citet{Desert:2015}, who observe
-the transits of 50 \kepler\ candidates with the Spitzer Space
+the transits of 50 \kepler\ candidates with the \textit{Spitzer} Space
 Telescope in order to observationally constrain the FP rate.  The idea
@@
 
+\subsection{Radial-velocity monitoring of large candidates}
+
 A much more independent and powerful test data set has recently become
@@
 giant-planet candidates, possibly near 50\%, which sounds potentially
-concerning.  However, when we look at our results on this sample, we
-see very good agreement between the \vespa\ predictions and the RV-
+concerning, although we reiterate that KOIs are not ruled FALSE 
+POSITIVES based on their transit depth or inferred size alone.
+Additionally, when we look at the \vespa\ results on this sample, we
+see very good agreement between our results and the RV-
 detected ``ground truth'' (\Tab{santerne}).  Notably, confirmed
@@
 
+\subsection{The enigmatic case of KOI-6705.01}
+
 We also briefly discuss another case of individual interest.
@@
 period (the true scenario uncovered by the detective work of
-\citet{Gaidos:2015}), and 0.01 to be an HEB.
+\citet{Gaidos:2015}), and 0.01 to be an HEB.  This is an excellent
+example of what was discussed in \sect{PEMs}: that even effects like
+column anomalies that were not identified by the \kepler\ team as
+ephemeris matches will typically be identified as false positives by 
+\vespa.
 
@@
 probability (FPP) for every \kepler\ object of interest (KOI) in the
-Q1-Q17 (DR24) table, using the publicly available Python module
+Q1-Q17 DR24 table, using the publicly available Python module
 \vespa, which implements the procedure introduced in
@@
 also be broken if the source of the eclipse were significantly
-displaced.
+displaced.  We estimate that perhaps 0.1\% of the planets we validate
+could be signals coming from significantly displaced sources, similar 
+to those identified as period-epoch matches by \citet{Coughlin:2014}
+but unidentified by that analysis.
 
@@
 KOIs \citep{Santerne:2015} or evolved stars \citep{Sliski:2014} are in
-even greater need of individual FPP analysis.
+even greater need of the individual FPP analysis here presented.
 
@@
 \acknowledgments
-It is a pleasure to thank
-\ldots\
+TDM acknowledges support from the \kepler\ Participating Scientist
+Program (NNX14AE11G). \ldots
 

### 2016-01-05 ms.tex
updated HZ table, added acknowledgments, blended planet discussion

@@
 \newcommand{\ncurval}{984} % from pie chart
+\newcommand{\nhz}{10}
 
@@
 \newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
+
+%from Natalie
+\newcommand{\teff}{\ensuremath{T_{\rm eff}}}
+\newcommand{\logg}{\ensuremath{\log{g}}}
+\newcommand{\vsini}{\ensuremath{v \sin{i}}}
+\newcommand{\feh}{[Fe/H]}
+\newcommand{\logl}{\ensuremath{\log{L}}}
+
+\newcommand{\rsun}{\ensuremath{R_\sun}}
+\newcommand{\msun}{\ensuremath{M_\sun}}
+\newcommand{\lsun}{\ensuremath{L_\sun}}
+
+\newcommand{\rstar}{\ensuremath{R_\star}}
+\newcommand{\mstar}{\ensuremath{M_\star}}
+\newcommand{\loggstar}{\ensuremath{\logg_\star}}
+\newcommand{\lstar}{\ensuremath{L_\star}}
+\newcommand{\astar}{\ensuremath{a_\star}}
+\newcommand{\dstar}{\ensuremath{d_\star}}
+\newcommand{\loglstar}{\ensuremath{\log{L_\star}}}
+\newcommand{\rhostar}{\ensuremath{\rho_\star}}
+
+\newcommand{\rpl}{\ensuremath{R_{\rm P}}}
+\newcommand{\mpl}{\ensuremath{M_{\rm P}}}
+\newcommand{\lpl}{\ensuremath{L_{\rm P}}}
+\newcommand{\rhopl}{\ensuremath{\rho_{\rm P}}}
+\newcommand{\loggpl}{\ensuremath{\logg_{\rm P}}}
+\newcommand{\teq}{\ensuremath{T_{\rm eq}}}
+
+\newcommand{\rjup}{\ensuremath{R_{\rm J}}}
+\newcommand{\mjup}{\ensuremath{M_{\rm J}}}
+\newcommand{\rhojup}{\ensuremath{\rho_{\rm J}}}
+\newcommand{\rearth}{\ensuremath{R_{\earth}}}
+\newcommand{\mearth}{\ensuremath{M_{\earth}}}
+
+\newcommand{\msini}{\ensuremath{m \sin{i}}}
+\newcommand{\mplsini}{\ensuremath{\mpl\sin{i}}}
 
@@
 \vespa\ are the following: unblended eclipsing binary (EB),
-hierarchical- triple eclipsing binary (HEB), chance-aligned
+hierarchical-triple eclipsing binary (HEB), chance-aligned
 background/foreground eclipsing binary (BEB), and transiting planet
-(Pl).  In this work, we also implement ``double-period'' versions of
+(Pl).\footnote{We note that we do not consider ``blended transiting planet''
+false positive scenarios, either due to physically associated or 
+chance-aligned companions.  See \sect{btp} for more discussion.} 
+In this work, we also implement ``double-period'' versions of
 each of the stellar false positive scenarios, acknowledging the
@@
 of sight by the TRIdimensional modeL of thE GALaxy (TRILEGAL) Galactic
-stellar popultion synthesis tool, but constrained to agree with some
+stellar population synthesis tool, but constrained to agree with some
 observed color(s) of the star (e.g. $J-K$), to within some specified
@@
 
-Of these KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
-<0.01$, and are thus validated at the 99\% level.  These KOIs are
-marked as labeled as such in \tab{fpp}.  These are not all new
-validations, however, since a number of them are already CONFIRMED.
-\Fig{fpppie} shows a different kind of summary, grouping KOIs by
-disposition and splitting up the CANDIDATES according to the \vespa\
-results, showing that \nvalnew\ KOIs are newly validated at the 99\%
-level. \Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
+\subsection{Validation of \nvalnew\ new planets}
+
+While the FPP below which to claim planet validation is clearly
+an arbitrary choice, there is precedent to using ${\rm FPP} <0.01$ as 
+the threshold---\citet{Rowe:2014} validated over 800 multi-planet KOIs
+using this number.  Adopting this same threshold, we find that 
+of the KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
+<0.01$, and are thus validated at the 99\% level.  
+These KOIs are labeled as such in \tab{fpp}.  These are not all new validations,
+however, since a number of them are already CONFIRMED. \Fig{fpppie}
+shows a different kind of summary, grouping KOIs by disposition and
+splitting up the CANDIDATES according to the \vespa\ results, showing
+that \nvalnew\ KOIs are newly validated at the 99\% level.
+\Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
 grouped by FPP.
+
+%HZ table
+\input{table_hz}
+
+As there is significant interest in identifying potentially habitable
+planets, \tab{hz} lists the properties of \nhz\ CANDIDATE KOIs newly
+validated by this work that \textit{may} fall within the optimistic
+habitable zones of their host stars \citep{Kopparapu:2013}, 
+according to the stellar
+properties reported by the DR24 table at the NExScI Archive.  We note
+that while more detailed follow-up observations (imaging and
+spectroscopy) have been taken for each of these targets, we make no
+attempt here to characterize these systems in detail.  Analysis of
+high-resolution spectroscopy in particular will solidify the
+properties of these host stars, which will affect the habitable zone
+boundaries.  We thus emphasize that this list is neither complete nor
+final, serving only to draw attention to new validations of 
+interest rather than to be a definitive statement on potential 
+habitability.  We also note that based solely on the properties in the 
+DR24 table, KOI-5475.01 (listed as having a 448-day orbital period) 
+should also be included in this list of potentially habitable-zone
+planets.  However, as explained in \citet[][Section 5.5.4]{Coughlin:2015},
+this particular KOI actually has a 224-day period, making its insolation
+to high to be within the habitable zone; we have thus excluded it 
+from \tab{hz}.
+
+\subsection{Likely False Positives}
 
@@
 even these relatively low FPPs are inflated by the effect of TTVs.
-\Tab{fpp} lists whether known TTV were accounted for when constructing
+\Tab{fpp} lists whether known TTVs were accounted for when constructing
 the folded transit light curve for each KOI.
@@
 (such as via the ``column anomaly'' effect), but not substantially
-more.
+more.  (See \sect{gaidos} for an example of a KOI caused by a 
+column anomaly that went unidentified by the \kepler\ pipeline but
+which \vespa\ assigned a high FPP.)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Blended Transiting Planets?}
+\sectlabel{btp}
+
+In this work, the only false positive scenarios we consider are 
+eclisping binary stars (EB, HEB, BEB, and the double-period versions
+thereof).  Previous work studying \kepler\ false positive rates
+\citep[e.g.][]{Fressin:2013} has also considered the  ``blended transiting
+planet'' to be a false positive---i.e.,  a fainter companion
+star hosting a transiting planet larger than what would be inferred if
+it were transiting the target star.  Because we do not consider such
+a scenario to be a false positive, the \vespa\ analysis presented here 
+does not quantify its probability.  As a result, we are \textit{not}
+able to unambiguously determine the radii of the planets we validate---
+all the planet radii listed in \tab{fpp} are based on the assumption
+that the planet transits the target star and that the target star is 
+unblended.  If the target star is actually a member of an unresolved
+binary system (as a significant fraction of KOIs undoubtedly are),
+then the true planet radius will be larger (significantly larger 
+if transiting a fainter companion).  This was indeed the motivation
+for \citet{Fressin:2013} to consider the ``blended transiting planet''
+as a false positive; part of the goal of that work was to 
+compute the planet occurrence rates in different radius bins.  
+However, trying to distinguish between single and binary target
+star configurations is beyond the scope of this work; we thus follow
+the precedent of \citet[][especially Section 5]{Lissauer:2014} by 
+acknowledging the potential for substantial radius
+uncertainties among the validated planet sample while nevertheless 
+defending the validations themselves as robust.
 
@@
 \subsection{The enigmatic case of KOI-6705.01}
+\sectlabel{gaidos}
 
@@
 other studies have shown that specific samples of KOIs tend to have
-large FPPs than the global average, so studies involving giant-planet
+larger FPPs than the global average, so studies involving giant-planet
 KOIs \citep{Santerne:2015} or evolved stars \citep{Sliski:2014} are in
@@
 
-\acknowledgments
-TDM acknowledges support from the \kepler\ Participating Scientist
-Program (NNX14AE11G). \ldots
+\acknowledgments TDM acknowledges support from the \kepler\
+Participating Scientist Program (NNX14AE11G). This paper includes data
+collected by the \kepler\ mission. Funding for the \kepler\ mission
+is provided by the NASA Science Mission directorate. The authors
+acknowledge the efforts of the \kepler\ Mission team for obtaining
+the light curve products used in
+this publication, which were generated by the \kepler\ Mission
+science pipeline through the efforts of the \kepler\ Science
+Operations Center and Science Office. The \kepler\ Mission is led by
+the project office at NASA Ames Research Center. Ball Aerospace built
+the \kepler\ photometer and spacecraft which is operated by the
+mission operations center at LASP. These data products are archived at
+the NASA Exoplanet Science Institute, which is operated by the
+California Institute of Technology, under contract with the National
+Aeronautics and Space Administration under the Exoplanet Exploration
+Program. This research has made use of NASA's Astrophysics Data
+System.
 
@@
   are most likely to be false positives, and blue plusses have
-  intermediate FPPs.  Grey dots are KOIs for which the
+  intermediate FPPs.  Grey dots are KOIs not identified as likely 
+  false positives for which the
   \vespa\ calculation is considered less reliable.  

### 2016-03-04 document/ms.tex
reorganization; readme updates

--- 2016-01-05 ms.tex
@@
 
-\slugcomment{}
+\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}
 
@@
 this particular KOI actually has a 224-day period, making its insolation
-to high to be within the habitable zone; we have thus excluded it 
+too high to be within the habitable zone; we have thus excluded it 
 from \tab{hz}.

### 2016-03-04 make_final_fpptable.py

@@ -4,8 +4,6 @@ import pandas as pd
 import numpy as np
 import os
 
-from configobj import ConfigObj
-
 from keputils import koiutils as ku
 DATA = ku.DR24
 
@@ -13,9 +11,11 @@ from astropy import constants as const
 RSUN = const.R_sun.cgs.value
 REARTH = const.R_earth.cgs.value
 
-fpp_file = 'fpp_all.txt'
-positional_file = 'positional_probability.csv'
-starprop_file = 'starprops_all.txt'
+folder = 'data'
+
+fpp_file = os.path.join(folder, 'fpp_all.txt')
+positional_file = os.path.join(folder, 'positional_probability.csv')
+starprop_file = os.path.join(folder, 'starprops_all.txt')
 
 fpp_table = pd.read_table(fpp_file, delim_whitespace=True)
 fpp_table.index = fpp_table['koi']
@@ -25,9 +25,11 @@ positional_table = pd.read_csv(positional_file, index_col=0)
 star_table = pd.read_table(starprop_file, delim_whitespace=True)
 star_table.index = star_table['koi']
 
-ttv_table = pd.read_table('ttvdata.txt', index_col=0, delim_whitespace=True) 
+ttv_file = os.path.join(folder, 'ttvdata.txt')
+ttv_table = pd.read_table(ttv_file, index_col=0, delim_whitespace=True) 
 
-err_table = np.loadtxt('fpp_err.txt', usecols=(0,1), dtype=str)
+err_file = os.path.join(folder, 'fpp_err.txt')
+err_table = np.loadtxt(err_file, usecols=(0,1), dtype=str)
 
 
 kois = fpp_table.index

### 2016-03-05 old_scripts/organize_positional_probtable.py
more reorganization

@@ -1,0 +1,26 @@
+
+import numpy as np
+import pandas as pd
+
+d = {}
+
+for line in open('probability_table_hammer.txt'):
+    line = line.split('|')
+    try:
+        line[3] = line[3].strip()
+        if line[1] not in d:
+            d[line[1]] = {}
+        if line[3]=='NULL':
+            val = np.nan
+        else:
+            try:
+                val = float(line[3])
+            except ValueError:
+                val = line[3]
+        d[line[1]][line[2]] = val
+    except:
+        print('error with {}'.format(line))
+        
+df = pd.DataFrame.from_dict(d, orient='index')
+
+df.to_csv('positional_probability.csv')

### 2016-03-05 document/table_meanfpp.tex
table

\begin{deluxetable}{cccc}
\tabletypesize{\scriptsize}
\tablecaption{Mean FPPs of candidate KOIs with reliable \vespa\ calculations
\tablabel{meanFPP} }
\tablehead{\colhead{Selection} & \colhead{Number} & \colhead{Mean FPP}}
\startdata
all & 2775 & 0.131 \\
singles & 1623 & 0.170 \\
multis & 1152 & 0.076 \\
$R_p > 15\,R_\oplus$ & 208 & 0.746 \\
$10\,R_\oplus < R_p < 15\,R_\oplus$ & 75 & 0.245 \\
$4\,R_\oplus < R_p < 10\,R_\oplus$ & 222 & 0.221 \\
$2\,R_\oplus < R_p < 4\,R_\oplus$ & 935 & 0.075 \\
$R_p < 2\,R_\oplus$ & 1335 & 0.053 
\enddata
\end{deluxetable}

### 2016-03-07 document/ms.tex
tables updated

@@
 
-\begin{deluxetable}{ccc}
-\tabletypesize{\scriptsize}
-\tablecaption{\vespa--calculated FPPs of the \\Santerne (2015) RV sample
-  \tablabel{santerne}}
-\tablehead{\colhead{RV-based nature} & \colhead{mean FPP} & \colhead{median FPP}}
-\startdata
-Planet & 0.0892 & 0.0002 \\
-Brown dwarf & 0.0035 & 0.0038 \\
-Eclipsing binary (EB) & 0.7764 & 0.9450 \\
-Contaminating EB & 0.8326 & 0.9950 \\
-Undetermined & 0.2393 & 0.0032
-\enddata
-\end{deluxetable}
+\input{table_santerne}
 

### 2016-03-15 make_final_fpptable.py
nb and figure work

@@ -54,6 +54,25 @@ fpp_table['has_ttv'] = ttv_table.ix[kois,'has_ttv']
 fpp_table['MES'] = DATA.ix[kois, 'koi_max_mult_ev']
 fpp_table['n_cands'] = DATA.ix[kois, 'koi_count']
 
+
+# Replace with mean values
+
+fpp_mean = pd.read_csv('data/fpp_bootstrap_mean.csv')
+fpp_mean.rename(columns={'Unnamed: 0':'koi'}, inplace=True)
+fpp_mean.index = fpp_mean['koi']
+
+fpp_max = pd.read_csv('data/fpp_bootstrap_max.csv')
+fpp_max.rename(columns={'Unnamed: 0':'koi'}, inplace=True)
+fpp_max.index = fpp_max['koi']
+
+for m in ['heb', 'eb', 'beb', 'heb', 'eb_Px2', 'beb_Px2', 'heb_Px2', 'long', 'boxy', 'pl']:
+    for col in ['lhood_{}'.format(m), 'pr_{}'.format(m)]:
+        fpp_table[col] = fpp_mean.ix[fpp_table.index, col]
+        
+fpp_table['FPP'] = fpp_mean.ix[fpp_table.index, 'FPP']
+fpp_table['FPP_max'] = fpp_max.ix[fpp_table.index, 'FPP']
+
+
 fpp_table.to_csv('fpp_final_table.csv')
 
     

### 2016-03-16 document/ms.tex
table spacing adjusted
new validations up, some paper edits

@@
 %\usepackage{acronym}
+
+\setlength{\tabcolsep}{2pt}
 
@@
 Coughlin\altaffilmark{2,3}, Jason F.
-Rowe\altaffilmark{4},Michael R.
-Haas\altaffilmark{2}, and Natalie M.
-Batalha\altaffilmark{2}}
+Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A.
+Petigura\altaffilmark{6},
+Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}
 
@@
 \altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
+\altaffiltext{5}{Columbia University}
+\altaffiltext{6}{California Institute of Technology}
 
@@
 The basic idea of \vespa\ is to assign probabilities to different
-astrophysical hypotheses that might describe a transiting planet
+hypotheses that might describe a transiting planet
 candidate signal.  If $\{H_i\}$ is the set of all considered
@@
 
+We note that a built-in weakness of model selection is that it assumes that
+the set of models being considered is comprehensive.  This could
+in principle lead to a situation where one model is strongly preferred
+over all other models, but even that model is a poor explanation of
+the data---in this work, this could lead to improperly validated planets.  
+There are two general strategies to try to address this issue.  The first 
+is to somehow quantify the absolute goodness-of-fit of the models, and 
+require that a validated planet pass some threshold test.  The other 
+strategy, that we adopt here, is to expand the set of models to be more 
+comprehensive.  In order to do this, we introduce two artificial models:
+``boxy'' and ``long.''  The ``boxy'' likelihood function is a step function
+at some minimum value of $T/\tau$ (zero below this threshold, and constant
+above), and constant throughout the space of the other trapezoidal parameters.
+Similarly, the likelihood of the ``long'' model is a step function at some
+minimum threshold value of duration $T$.  These thresholds  
+are set relative to the simulated trapezoidal shapes of the planet model:
+the $T/\tau$ threshold is the maximum value from the simulated planet population,
+and the $T$ threshold is the 99\% percentile of simulated planet
+population values.  We also choose the model priors for these artificial
+models to be low, reflecting that we expect only a small number of signals
+to be unexplained by any of the astrophysical scenarios: the number that we
+choose for each of these models is $5 \times 10^{-5}$, corresponding to an expectation
+that there may be $\sim$10 such signals among the $\sim$200,000 \kepler\ targets.
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 understand the range of applicability of the \vespa\ calculation.
-First of all, this method selects between different \emph{eclipse
-  configuration} explanations for the transit-like signal, and cannot
+First of all, this method selects between different specific explanations 
+for the transit-like signal, and cannot
 comment on whether the signal might be caused by stellar variability
@@
 signal-to-noise ratio (SNR) candidates that are not clearly
-transit-like must be viewed with caution.
+transit-like must be viewed with caution.  This being said, the reason 
+for including the artificial 
+``boxy'' and ``long'' models in the model selection calculation
+ (\sect{mothods:fpp}) is to flag signals that do not 
+fit well with any of the astrophysical eclipse models---and despite their
+contrived nature, they do seem to
 
@@
 \begin{center}
-\includegraphics[width=7in]{figures/RP_cand.pdf}
+\includegraphics[width=7in]{figures/fppalpha.pdf}
 \end{center}
-\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
-  by FPP value.  Green circles are most likely to be planets, red X's
-  are most likely to be false positives, and blue plusses have
-  intermediate FPPs.  Grey dots are KOIs not identified as likely 
-  false positives for which the
-  \vespa\ calculation is considered less reliable.  
+\caption{Periods and radii of KOIs with CANDIDATE and CONFIRMED disposition.  
+  Blue circles have previously been identified as CONFIRMED.  Candidates are orange circles, 
+  shaded by false positive probability, with 
+  a transparent circle representing a high FPP. 
   \figlabel{rpcand}}

### 2016-03-16 make_final_fpptable.py

@@ -65,12 +65,18 @@ fpp_max = pd.read_csv('data/fpp_bootstrap_max.csv')
 fpp_max.rename(columns={'Unnamed: 0':'koi'}, inplace=True)
 fpp_max.index = fpp_max['koi']
 
+fpp_std = pd.read_csv('data/fpp_bootstrap_std.csv')
+fpp_std.rename(columns={'Unnamed: 0':'koi'}, inplace=True)
+fpp_std.index = fpp_std['koi']
+
+
 for m in ['heb', 'eb', 'beb', 'heb', 'eb_Px2', 'beb_Px2', 'heb_Px2', 'long', 'boxy', 'pl']:
     for col in ['lhood_{}'.format(m), 'pr_{}'.format(m)]:
         fpp_table[col] = fpp_mean.ix[fpp_table.index, col]
         
 fpp_table['FPP'] = fpp_mean.ix[fpp_table.index, 'FPP']
 fpp_table['FPP_max'] = fpp_max.ix[fpp_table.index, 'FPP']
+fpp_table['FPP_std'] = fpp_std.ix[fpp_table.index, 'FPP']
 
 
 fpp_table.to_csv('fpp_final_table.csv')

### 2016-03-16 document/ms.tex
text edits

@@
 \newcommand{\nbadroche}{37}
+
+\newcommand{\nlongfp}{530}
 
@@
 ``boxy'' and ``long'' models in the model selection calculation
- (\sect{mothods:fpp}) is to flag signals that do not 
-fit well with any of the astrophysical eclipse models---and despite their
-contrived nature, they do seem to
-
-However, while the FPP value does only give the \emph{relative}
-probability between the false positive and planet scenarios, there is
-a way to get a sense of whether \emph{all} of the models might be bad
-fits to the data (and thus get a hint that perhaps the signal is due
-to stellar variability or a false alarm).  Recall that FPP is
-calculated as
-\begin{equation}
-\eqlabel{fpp}
-{\rm FPP} = \frac{\displaystyle\sum_{i \neq {\rm Pl}}
-  L_i}{\displaystyle \sum_i L_i}
-\end{equation}
-where $L_i$ = $\mathcal L_i \pi_i$ and $i$ runs over all the models,
-with ``Pl'' representing the planet scenario.  If, for example, the
-shape of the transit is such that \emph{none} of the models gives any
-kind of decent fit to its trapezoidal shape, then $L_{\rm tot} =
-\sum_i L_i$ will be very small.  It appears that a value of $10^{-3}$
-is a reasonable threshold below which to consider a particular
-calculation unreliable.  To set this threshold we inspected the
-handful of systems that have low FPPs and $L_{\rm tot} < 10^{-3}$
-(some go as low as $10^{-10}$ or lower), and find that these very
-often have unrealistically long durations for a transit signal.  Such
-a case could easily give the planet hypothesis the \emph{largest}
-likelihood (resulting in a low FPP), not because it is intrinsically
-likely, but because all the other scenarios are even less likely.
-
-Another important constraint used in the FPP calculation is the
+ (\sect{methods:fpp}) is to flag signals that do not 
+fit well with any of the astrophysical eclipse models---in fact, the ``long''
+model is preferred by \nlongfp\ KOIs that are already dispositioned
+as FALSE POSITIVE.
+
+Additionally, an important constraint used in the FPP calculation is the
 allowed sky area inside which a blended false positive may live.  As
@@
 
-\begin{deluxetable}{ccc}
-\tabletypesize{\scriptsize}
-\tablecaption{Mean FPPs of candidate KOIs with reliable \vespa\ calculations
-  \tablabel{meanFPP}}
-\tablehead{\colhead{Selection} & \colhead{Number} & \colhead{mean FPP}}
-\startdata
-all & 2823 & 0.148 \\
-singles & 1665 & 0.196 \\
-multis & 1158 & 0.078 \\
-$R_p > 10\,R_\oplus$ & 347 & 0.704 \\ 
-$4\,R_\oplus < R_p < 10\,R_\oplus$ & 245 & 0.182 \\ 
-$2\,R_\oplus < R_p < 4\,R_\oplus$ & 1150 & 0.057 \\ 
-$R_p < 2\,R_\oplus$ & 1081 & 0.058 
-\enddata
-\end{deluxetable}
+\input{table_meanfpp}
 
@@
 detected ``ground truth'' (\Tab{santerne}).  Notably, confirmed
-planets show a mean FPP of about 9\% and a median of only 0.02\%,
-while confirmed EBs (CEBs) show a mean FPP of 78\% (83\%) and a median
-of 95\% (99.5\%).  The three brown dwarfs also show low FPPs, which is
+planets show a mean FPP of about 10\% and a median of much less than 1\%,
+while confirmed EBs (CEBs) show a mean FPP of 75\% (78\%) and a median
+of 97\% (99\%).  The three brown dwarfs also show low FPPs, which is
 understandable because \vespa\ doesn't pretend to predict anything
@@
 as giant planets.  It is also instructive to investigate the four
-cases where \vespa\ computes high FPPs ($>$0.3) for confirmed planets.
+cases where \vespa\ computes high FPPs ($>$0.5) for confirmed planets.
 Three of these (KOI-377.01, KOI-1426.02 and KOI-1474.01) have
@@
 charge-transfer  effect from a 1.99\,d EB located on the same CCD
-column.  For this KOI, \vespa\ calculates an FPP of 1, with
+column.  For this KOI, \vespa\ calculates an FPP of 1, with the 
+``long'' model preferred by far.
+
 probabilities of 0.86 to be a BEB, 0.13 to be a BEB with twice the

### 2016-03-24 document/ms.tex
some updated figures, text, etc.

@@
 \newcommand{\ntotal}{7470}
-\newcommand{\nfail}{422}
-\newcommand{\ncalc}{7048}
-
-\newcommand{\nfp}{424}
+\newcommand{\nfail}{427}
+\newcommand{\ncalc}{7056}
 
@@
 \newcommand{\nbadtrapfit}{38} %MCMCError or NoFitError
-\newcommand{\nbadroche}{37}
-
-\newcommand{\nlongfp}{530}
-
-\newcommand{\nreliable}{2823} %from figure
-\newcommand{\nval}{1997} %from figure
-\newcommand{\nreliableFP}{398} %from figure
-\newcommand{\nvalnew}{1325} %from pie chart
-\newcommand{\nfpnew}{424}  % all candidate with FPP < 0.9
+\newcommand{\nbadroche}{39}
+
+\newcommand{\nlongfp}{526}
+
+\newcommand{\nreliable}{2857} %from figure
+\newcommand{\nval}{1948} %from figure
+\newcommand{\nreliableFP}{419} %from figure
+\newcommand{\nvalnew}{1284} %from pie chart
+\newcommand{\nfpnew}{428}  % all candidate with FPP < 0.9
 \newcommand{\ncurval}{984} % from pie chart
@@
 fit well with any of the astrophysical eclipse models---in fact, the ``long''
-model is preferred by \nlongfp\ KOIs that are already dispositioned
+model is preferred ($>50\5$) by \nlongfp\ KOIs that are already dispositioned
 as FALSE POSITIVE.
@@
 \item MES $>$ 10, indicating the signal is unlikely to be caused by 
-      systematic noise in the light curve,
+      systematic noise in the light curve, and
 \item Probability $> 0.99$ to be on the target star, according
   to \citet{Bryson:KSCI}, along with a positional probability
-  ``score'' $> \posprobthresh$ (indicating a reliable result), and   
-\item $L_{\rm tot} > 10^{-3}$, indicating that not all the hypotheses are
-  poor fits to the transit signal.
+  ``score'' $> \posprobthresh$ (indicating a reliable result).  
 \end{itemize}
@@
 for different subsets, showing several notable features.  Single KOIs
-are about 3$\times$ more likely to be false positives than KOIs in
+are about 2.5$\times$ more likely to be false positives than KOIs in
 multiple-KOI systems, in qualitative agreement with
@@
 
+\subsection{Unidentified Ephemeris Matches?}
+\sectlabel{PEMs}
+
+One potential concern worth addressing in some detail, before deciding
+which planets to validate based on the \vespa\ calculations, is the 
+possibility of false positives caused by distant contamination
+but not identified through the ``period-epoch match'' (PEM) technique
+used by \citet{Coughlin:2014}, due to the fact that not all stars in the 
+\kepler\ field were monitored by the mission.  We thus estimate here
+the probability that a CANDIDATE KOI to which \vespa\ assigns a low FPP
+might still be caused by such a scenario.
+
+In the Q1-Q17 DR24 KOI table used as the basis for this work, 980
+KOIs were identified as PEMs.  Of these, 187 were not identified 
+as false positives by any other method.  Only 15 of these 187 survived 
+all the quality cuts described in \sect{results:fpp}. And of these 15, 
+only 3 have FPP $< 0.01$  (See \sect{gaidos} for an example of a KOI caused by a 
+``column anomaly'' effect that went unidentified by the \kepler\ pipeline but
+to which \vespa\ assigned a high FPP.).  Thus, we expect only about 0.3\% (3/980) of 
+as-yet unidentified distant-contamination FPs to end
+up with FPP $< 0.01$ according to \vespa. As the fraction of false positives
+from pixel contamination but unidentified as PEMs among the entire KOI sample is
+estimated to be something around 23\% \citep{Coughlin:2014}, we estimate
+that there remains a small ($\sim$0.06\%) residual FPP for all KOIs, even 
+when the \vespa\-calculated FPP is negligibly tiny.
+
 \subsection{Validation of \nvalnew\ new planets}
@@
 the threshold---\citet{Rowe:2014} validated over 800 multi-planet KOIs
-using this number.  Adopting this same threshold, we find that 
+using this number.  Adopting this same threshold, and incorporating
+the 0.06\% residual FPP estimated in \sect{PEMs}, we find that 
 of the KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
-<0.01$, and are thus validated at the 99\% level.  
+<0.0094$, and are thus validated at the 99\% level.  
 These KOIs are labeled as such in \tab{fpp}.  These are not all new validations,
@@
 that \nvalnew\ KOIs are newly validated at the 99\% level.
-\Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
-grouped by FPP.
+\Fig{rpcand} shows the radii and periods of the CONFIRMED and 
+CANDIDATE KOIs, with the transparency of the points representing
+the \vespa-calculated FPP.
 
@@
 spectroscopy) have been taken for each of these targets, we make no
-attempt here to characterize these systems in detail.  Analysis of
-high-resolution spectroscopy in particular will solidify the
-properties of these host stars, which will affect the habitable zone
+attempt here to characterize these systems in detail.  However, 
+we do note that high-resolution imaging of KOI-2418 and KOI-3010 reveal
+that these two host stars have close companions that may or may not
+change the habitable nature of the planets (e.g., if the planets happen
+to transit the secondary star instead of the primary).  Additionally, analysis of
+high-resolution spectroscopy will solidify the
+properties of all these host stars, affecting the habitable zone
 boundaries.  We thus emphasize that this list is neither complete nor
@@
 the folded transit light curve for each KOI.
-
-\subsection{Unidentified Ephemeris Matches?}
-\sectlabel{PEMs}
-
-One potential concern for the reliability of the validations presented
-here might be the possibility of unidentified ephemeris matches, or
-``period-epoch matches'' (PEMs).  \citet{Coughlin:2014} identified a
-number of false positives among KOIs using this method, by comparing
-the periods and epochs of KOIs both to each other and to known
-catalogs of eclipsing binaries in order to see if any have identical
-ephemerides, an indication of contamination, sometimes from far away 
-on the \kepler\ CCD.
-
-In the Q1-Q17 DR24 KOI table used as the basis for this work, 980
-KOIs were identified as PEMs.  Of these, 187 were not identified by
-any other method.  Only 18 of these 187 survived all the quality cuts
-described in \sect{results:fpp}. And of these 18, only 4 have FPP 
-$< 0.01$.
-
-Thus, we expect only about 0.4\% (4/980) of unidentified PEMs to end
-up as validated according to \vespa. As the total rate of PEMs is
-estimated to be something around 35\% \citep{Coughlin:2014}, there
-remains a small ($\sim$0.1\%  chance) that any of the validated
-planets may turn out to be due to  as-yet unidentified contamination
-from one of the false positive  sources that cause PEMs.  In other
-words, among our validated sample of planets, there may well be one or
-two that turn out to be false positives due to distant contamination
-(such as via the ``column anomaly'' effect), but not substantially
-more.  (See \sect{gaidos} for an example of a KOI caused by a 
-column anomaly that went unidentified by the \kepler\ pipeline but
-which \vespa\ assigned a high FPP.)
 
@@
 column.  For this KOI, \vespa\ calculates an FPP of 1, with the 
-``long'' model preferred by far.
-
-probabilities of 0.86 to be a BEB, 0.13 to be a BEB with twice the
-period (the true scenario uncovered by the detective work of
-\citet{Gaidos:2015}), and 0.01 to be an HEB.  This is an excellent
+``long'' model preferred by far (of the astrophysical models, the 
+double-period BEB---the true scenario---is preferred). This is an excellent
 example of what was discussed in \sect{PEMs}: that even effects like

### 2016-03-26 document/ms.tex
new hz table

@@
 \newcommand{\ntotal}{7470}
-\newcommand{\nfail}{427}
+\newcommand{\nfail}{414}
 \newcommand{\ncalc}{7056}
@@
 \newcommand{\nreliable}{2857} %from figure
-\newcommand{\nval}{1948} %from figure
+\newcommand{\nval}{1935} %from figure
 \newcommand{\nreliableFP}{419} %from figure
@@
 \newcommand{\ncurval}{984} % from pie chart
-\newcommand{\nhz}{10}
+\newcommand{\nhz}{9}
 
@@
 
+To quantify uncertainty due to the Monte Carlo nature of this procedure, 
+\vespa\ is also able to repeat these calculations any desired number of times 
+by bootstrap resampling (with replacement) of the simulated populations, 
+and recalculating the likelihoods based on the resampled populations.  
+This mitigates the chances for rare outliers in a simulation to significantly 
+affect the calculated FPP.
+
 We note that a built-in weakness of model selection is that it assumes that
@@
 Of the \ntotal\ KOIs in the Q1-Q17 DR24 table at the NExScI Exoplanet
-Archive, \vespa\ successfully calculates the FPP for \ncalc.  These
-results are listed in \tab{fpp};  \sect{failures} contains detailed
-explanations of the failure reasons for the other \nfail\ KOIs.
+Archive, \vespa\ successfully calculates the FPP for \ncalc.  
+\Sect{failures} contains detailed explanations of the failure reasons for 
+the \nfail\ KOIs for which we do not present \vespa\ results.  
+FPPs and their uncertainties are determined as the mean and standard 
+deviations of 10 bootstrap 
+recalculations of the initially simulated populations for each KOI (as described in 
+\sect{methods:fpp}).  These results are listed in \tab{fpp}.  
+The median fractional FPP uncertainty 
+for KOIs with 0.001 $<$ FPP $<$ 0.1 (within an order of magnitude of the 
+validation threshold) is about 12\%, and this distribution 
+is shown in \fig{sigmafpp}.
 
@@
 fit well with any of the astrophysical eclipse models---in fact, the ``long''
-model is preferred ($>50\5$) by \nlongfp\ KOIs that are already dispositioned
+model is preferred ($>50\%$) by \nlongfp\ KOIs that are already dispositioned
 as FALSE POSITIVE.
@@
 all the quality cuts described in \sect{results:fpp}. And of these 15, 
-only 3 have FPP $< 0.01$  (See \sect{gaidos} for an example of a KOI caused by a 
+only 3 have FPP $< 0.01$.  (See \sect{gaidos} for an example of a KOI caused by a 
 ``column anomaly'' effect that went unidentified by the \kepler\ pipeline but
-to which \vespa\ assigned a high FPP.).  Thus, we expect only about 0.3\% (3/980) of 
+to which \vespa\ assigned a high FPP.)  Thus, we expect only about 0.3\% (3/980) of 
 as-yet unidentified distant-contamination FPs to end
@@
 that there remains a small ($\sim$0.06\%) residual FPP for all KOIs, even 
-when the \vespa\-calculated FPP is negligibly tiny.
+when the \vespa-calculated FPP is negligibly tiny.
 
@@
 the threshold---\citet{Rowe:2014} validated over 800 multi-planet KOIs
-using this number.  Adopting this same threshold, and incorporating
-the 0.06\% residual FPP estimated in \sect{PEMs}, we find that 
+using this number, and \citet{Montet:2015} used it to validate a sample
+of K2-Campaign 1 planets.  Adopting this same threshold and adding
+the 0.06\% residual FPP estimated in \sect{PEMs} to the \vespa-calculated
+value, we find that 
 of the KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
-<0.0094$, and are thus validated at the 99\% level.  
+<0.01$, and are thus validated at the 99\% level.  
 These KOIs are labeled as such in \tab{fpp}.  These are not all new validations,
@@
 CANDIDATE KOIs, with the transparency of the points representing
-the \vespa-calculated FPP.
+the \vespa-calculated FPP.  \Fig{validatedcompare} compares the temperature
+and radii of the stars hosting these planets between the \citetalias{Huber:2014}
+and \isochrones\ analysis.
 
@@
 FPPs for KOIs that are dispositioned FALSE POSITIVE and have MES $>$
-10 and $L_{\rm tot} > 10^{-3}$. The vast majority of these have large
-FPPs.
+10. The vast majority of these have large FPPs.
 
@@
 
-In this work, the only false positive scenarios we consider are 
+In this work, the only astrophysical false positive scenarios we consider are 
 eclisping binary stars (EB, HEB, BEB, and the double-period versions
@@
 \citet{Morton:2012}, with improvements in stellar parameter modeling
-and the inclusion of new ``double-period'' false positive scenarios.
+and the inclusion of new ``double-period'' false positive scenarios 
+and artificial models to identify KOIs that are not well explained
+by any of the astrophysical models.  We have also for the first time
+estimated uncertainties in the \vespa\ calculation, through a bootstrap
+resampling procedure.
+
 While the assumptions behind this calculation are not necessarily
@@
 more than doubling the number of confirmed \kepler\ exoplanets.  Among
-this set of reliable \vespa\ calculations are also \nfpnew\ new likely
+this set of newly validated planets are \nhz\ that are consistent with being
+in the habitable zones of their host stars.  We also identify \nfpnew\ new likely
 false positive KOIs, although we note that some of these may be due to
@@
 also be broken if the source of the eclipse were significantly
-displaced.  We estimate that perhaps 0.1\% of the planets we validate
+displaced.  We estimate that perhaps 0.06\% of the planets we validate
 could be signals coming from significantly displaced sources, similar 
@@
 \acknowledgments TDM acknowledges support from the \kepler\
-Participating Scientist Program (NNX14AE11G). This paper includes data
-collected by the \kepler\ mission. Funding for the \kepler\ mission
+Participating Scientist Program (NNX14AE11G). We thank the anonymous
+referee, Daniel Huber, Jack Lissauer, Juna Kollmeier, and David Hogg 
+for providing helpful suggestions that improved both the analysis and 
+presentation herein.
+This paper includes data collected by the \kepler\ mission. Funding for the \kepler\ mission
 is provided by the NASA Science Mission directorate. The authors
@@
 \begin{center}
+\includegraphics[width=7in]{figures/sigmafpp.pdf}
+\end{center}
+\caption{Fractional uncertainties for KOIs with FPPs between
+  0.001 and 0.1; that is, within an order of magnitude of the 
+  validation threshold.  FPP values and uncertainties 
+  are determined by the mean and standard deviations 
+  of \vespa\ calculations based on 
+  10 bootstrap resamplings (see \sect{methods:fpp}) of 
+  a single set of simulated populations for each KOI.
+  \figlabel{sigmafpp}}
+\end{figure*}
+
+\begin{figure*}[p]
+\begin{center}
 \includegraphics[width=7in]{figures/fpp_summary_all.pdf}
@@
   0.99$, with ``score'' $> \posprobthresh$) according to pixel-level analysis
-  \citep{Bryson:KSCI}, and have $L_{\rm tot} > 10^{-3}$, indicating
-  that the hypotheses tested by \vespa\ are not all poor explanations
-  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
+  \citep{Bryson:KSCI}, and have MES $>10$.  Of these \nreliable\ KOIs,
   \nval\ have FPPs less than 1\% (\nvalnew\ of which have not yet been
@@
   estimates of the overall \kepler\ candidate false positive rate.
+  Red circles correspond to median FPP values in equal-sized bins. 
   \figlabel{fppall}}
@@
   categorize according to their reliability.  The ``no reliable
-  calculation'' category means that either the \vespa\ calculation was
-  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
+  calculation'' category means that the \vespa\ calculation was
+  not successful.  ``On-target
   probability uncertain'' indicates that the positional probability
@@
 
+\begin{figure*}[p]
+\begin{center}
+\includegraphics[width=7in]{figures/validated_compare.pdf}
+\end{center}
+\caption{Comparison between temperatures and radii estimated from the
+  \isochrones\ analysis in this work and those from the
+  \kepler\ stellar parameters catalog \citepalias{Huber:2014}, for the 
+  sample of stars hosting planets validated in this study.  As 
+  seen in previous figures, the \isochrones\ analysis tends to 
+  over-predict the stellar radii compared to \citetalias{Huber:2014} 
+  for the coolest stars.  A small number of stars are also estimated by 
+  the photometric analysis of \citetalias{Huber:2014} to be evolved, 
+  but not by \isochrones.
+  \figlabel{validatedcompare}}
+\end{figure*}
+
 %\capstartfalse

### 2016-04-20 document/ms.tex
re-submitted to apj
something

--- 2016-03-16 document/ms.tex
@@
 %\usepackage{acronym}
-
-\setlength{\tabcolsep}{2pt}
 
@@
 
-\newcommand{\nlongfp}{530}
-
 \newcommand{\nreliable}{2823} %from figure
@@
 Coughlin\altaffilmark{2,3}, Jason F.
-Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A.
-Petigura\altaffilmark{6},
-Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}
+Rowe\altaffilmark{4},Michael R.
+Haas\altaffilmark{2}, and Natalie M.
+Batalha\altaffilmark{2}}
 
@@
 \altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
-\altaffiltext{5}{Columbia University}
-\altaffiltext{6}{California Institute of Technology}
 
@@
 The basic idea of \vespa\ is to assign probabilities to different
-hypotheses that might describe a transiting planet
+astrophysical hypotheses that might describe a transiting planet
 candidate signal.  If $\{H_i\}$ is the set of all considered
@@
 
-We note that a built-in weakness of model selection is that it assumes that
-the set of models being considered is comprehensive.  This could
-in principle lead to a situation where one model is strongly preferred
-over all other models, but even that model is a poor explanation of
-the data---in this work, this could lead to improperly validated planets.  
-There are two general strategies to try to address this issue.  The first 
-is to somehow quantify the absolute goodness-of-fit of the models, and 
-require that a validated planet pass some threshold test.  The other 
-strategy, that we adopt here, is to expand the set of models to be more 
-comprehensive.  In order to do this, we introduce two artificial models:
-``boxy'' and ``long.''  The ``boxy'' likelihood function is a step function
-at some minimum value of $T/\tau$ (zero below this threshold, and constant
-above), and constant throughout the space of the other trapezoidal parameters.
-Similarly, the likelihood of the ``long'' model is a step function at some
-minimum threshold value of duration $T$.  These thresholds  
-are set relative to the simulated trapezoidal shapes of the planet model:
-the $T/\tau$ threshold is the maximum value from the simulated planet population,
-and the $T$ threshold is the 99\% percentile of simulated planet
-population values.  We also choose the model priors for these artificial
-models to be low, reflecting that we expect only a small number of signals
-to be unexplained by any of the astrophysical scenarios: the number that we
-choose for each of these models is $5 \times 10^{-5}$, corresponding to an expectation
-that there may be $\sim$10 such signals among the $\sim$200,000 \kepler\ targets.
-
 %%%%%%%%%%%%%%%%%%%%%%
@@
 understand the range of applicability of the \vespa\ calculation.
-First of all, this method selects between different specific explanations 
-for the transit-like signal, and cannot
+First of all, this method selects between different \emph{eclipse
+  configuration} explanations for the transit-like signal, and cannot
 comment on whether the signal might be caused by stellar variability
@@
 signal-to-noise ratio (SNR) candidates that are not clearly
-transit-like must be viewed with caution.  This being said, the reason 
-for including the artificial 
-``boxy'' and ``long'' models in the model selection calculation
- (\sect{methods:fpp}) is to flag signals that do not 
-fit well with any of the astrophysical eclipse models---in fact, the ``long''
-model is preferred by \nlongfp\ KOIs that are already dispositioned
-as FALSE POSITIVE.
-
-Additionally, an important constraint used in the FPP calculation is the
+transit-like must be viewed with caution.
+
+However, while the FPP value does only give the \emph{relative}
+probability between the false positive and planet scenarios, there is
+a way to get a sense of whether \emph{all} of the models might be bad
+fits to the data (and thus get a hint that perhaps the signal is due
+to stellar variability or a false alarm).  Recall that FPP is
+calculated as
+\begin{equation}
+\eqlabel{fpp}
+{\rm FPP} = \frac{\displaystyle\sum_{i \neq {\rm Pl}}
+  L_i}{\displaystyle \sum_i L_i}
+\end{equation}
+where $L_i$ = $\mathcal L_i \pi_i$ and $i$ runs over all the models,
+with ``Pl'' representing the planet scenario.  If, for example, the
+shape of the transit is such that \emph{none} of the models gives any
+kind of decent fit to its trapezoidal shape, then $L_{\rm tot} =
+\sum_i L_i$ will be very small.  It appears that a value of $10^{-3}$
+is a reasonable threshold below which to consider a particular
+calculation unreliable.  To set this threshold we inspected the
+handful of systems that have low FPPs and $L_{\rm tot} < 10^{-3}$
+(some go as low as $10^{-10}$ or lower), and find that these very
+often have unrealistically long durations for a transit signal.  Such
+a case could easily give the planet hypothesis the \emph{largest}
+likelihood (resulting in a low FPP), not because it is intrinsically
+likely, but because all the other scenarios are even less likely.
+
+Another important constraint used in the FPP calculation is the
 allowed sky area inside which a blended false positive may live.  As
@@
 detected ``ground truth'' (\Tab{santerne}).  Notably, confirmed
-planets show a mean FPP of about 10\% and a median of much less than 1\%,
-while confirmed EBs (CEBs) show a mean FPP of 75\% (78\%) and a median
-of 97\% (99\%).  The three brown dwarfs also show low FPPs, which is
+planets show a mean FPP of about 9\% and a median of only 0.02\%,
+while confirmed EBs (CEBs) show a mean FPP of 78\% (83\%) and a median
+of 95\% (99.5\%).  The three brown dwarfs also show low FPPs, which is
 understandable because \vespa\ doesn't pretend to predict anything
@@
 as giant planets.  It is also instructive to investigate the four
-cases where \vespa\ computes high FPPs ($>$0.5) for confirmed planets.
+cases where \vespa\ computes high FPPs ($>$0.3) for confirmed planets.
 Three of these (KOI-377.01, KOI-1426.02 and KOI-1474.01) have
@@
 charge-transfer  effect from a 1.99\,d EB located on the same CCD
-column.  For this KOI, \vespa\ calculates an FPP of 1, with the 
-``long'' model preferred by far.
-
+column.  For this KOI, \vespa\ calculates an FPP of 1, with
 probabilities of 0.86 to be a BEB, 0.13 to be a BEB with twice the
@@
 \begin{center}
-\includegraphics[width=7in]{figures/fppalpha.pdf}
+\includegraphics[width=7in]{figures/RP_cand.pdf}
 \end{center}
-\caption{Periods and radii of KOIs with CANDIDATE and CONFIRMED disposition.  
-  Blue circles have previously been identified as CONFIRMED.  Candidates are orange circles, 
-  shaded by false positive probability, with 
-  a transparent circle representing a high FPP. 
+\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
+  by FPP value.  Green circles are most likely to be planets, red X's
+  are most likely to be false positives, and blue plusses have
+  intermediate FPPs.  Grey dots are KOIs not identified as likely 
+  false positives for which the
+  \vespa\ calculation is considered less reliable.  
   \figlabel{rpcand}}

### 2016-05-10 document/ms.tex
added github comment to paper; submitted to arxiv

--- 2016-03-26 document/ms.tex
@@
 
-\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}
+%\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}
 
@@
 Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A.
-Petigura\altaffilmark{6},
+Petigura\altaffilmark{6,7},
 Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}
@@
 \altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
-\altaffiltext{5}{Columbia University}
-\altaffiltext{6}{California Institute of Technology}
+\altaffiltext{5}{Department of Computer Science, Columbia University, 1214 Amsterdam Ave, New York, NY 10027}
+\altaffiltext{6}{California Institute of Technology, Pasadena, CA 91125, USA}
+\altaffiltext{7}{Hubble Fellow}
 
@@
 
+\vspace{1.5\baselineskip}
+Instructions for reproducing all the calculations presented 
+herein can be found at \url{https://github.com/timothydmorton/koi-fpp}.
+Summary figures produced by \vespa\ for all KOIs can be accessed
+at \url{http://kepler-fpp.space}.
+
 \acknowledgments TDM acknowledges support from the \kepler\
